# R Coding Basics

Okay so what is R?

## Operators

### Arithmetic Operators

R is a programming language used for statistical modeling, data analysis, and visualization. At it's most basic, it's a calculator which uses **operators** to perform arithmetic operations:

- `+`  -- Addition
- `-`  -- Subtraction
- `*`  -- Multiplication
- `/`  -- Division
- `^`  -- Exponentiate (raise to the power of)
- `%%` -- Modulus (find the remainder of *X* divided by *Y*)


```{r simple arithmetic, strip.white=TRUE}
2 + 2

6 / 2

3^2

10 %% 4

3^2/2*5/2
```

*comparison* operators return `TRUE` or `FALSE` values (aka booleans):

- `<` less than, `>` greater than
- `<=` less than or equal to, `>=` greater than or equal to
- `==` exactly equal to

> Look at some simple test expressions to see how they evaluate:

```{r comparison examples}
6 > 4

(2+4) < (8+8)

2.5 <= 2.5
```


*logical* operators also return `TRUE` or `FALSE` values (aka booleans):

- `&` and
- `|` or
- `!` not
- `%in%` Checks whether an element is in an object

> Look at some more simple test expressions to see how they evaluate:

```{r logical tests}
TRUE & FALSE

TRUE | FALSE

!FALSE
```

`TRUE` also = 1, and `FALSE` also = 0.

```{r logical arithmatic}
TRUE < FALSE

TRUE + TRUE

TRUE + FALSE 
```

**Note: You must use ALL CAPS (when you spell the logical's name)**


## Variable Assignment

In R, you assign a value to a variable with an assignment operator: `=` or `<-`. e.g.,:

`x = 4`

`x <- 4`

Think of `=` and `<-` to mean "gets".

To reference or access the information stored in a variable, you "call" (type in the code) the variable's name:

```{r objects}
x <- 4
x

x+2

x + x

y <- x + 4
y

z <- "Hello world"
z
```

R is very specific and finicky.

```{r eval=F}
myVar = 4
myvar
```

## Variable/Data modes (types)

R classifies all the data it works with into different *types* or storage *modes*, which can be organized into different categories:

A. Continuous

1. Numeric -- Whole numbers or decimals
  + Integers (**int**) - whole numbers
  + Double-precision (**dbl**) - real numbers (floating point numerical values)

B. Discrete

1. Character (**chr**) - a string of characters/text (can use " or ')
2. Logical (**lgl**) - a logical `TRUE` or `FALSE`
3. Factor (**fct**) - factors, which R uses to represent categorical variables with fixed possible values of discrete data.

You can check the type of some data by using the `typeof()` function (more about functions later!).

> use `typeof()` to check the types of `y` and `z`

```{r}
y

typeof(z)

z


```

		
## Global environment		

Global environment contains all saved objects. 
`ls()` to print what's in your global environment.

```{r}
ls()
```

You can remove objects from your environment with the `rm()` command. 

> remove `x` with `rm()` and then check your work space with `ls()`

```{r}
rm(x)
ls()

```

`rm(list=ls())` to clear entire workspace

## Data Objects

### Vectors

**Vectors** are a series of elements. Each item in a vector is an element.

You initiate a vector with `c()`

> Create a vector with 4 different numbers and save it to the variable `myVector`. Then print out `myVector`

```{r}

myVector <- c(2, 4, 6, 8)
myVector


```

Arithmetic and logical operations can be performed on a vector:

```{r} 
myVector * 2

myVector > 4
```

Observe the output here. What do you notice?

```{r}
c(1, "hello")
c(5, "HELLO")
```


#### Indexing Vectors

indexing, with brackets, lets you target/pull specific elements out of an object.

> Index the 2nd element of `myVector`

```{r}
myVector[2]
```

### Dataframes

You can think of a data frame like an excel spreadsheet: a series of equal length vectors, where each vector is treated as a column and elements of those vectors are the rows.

```{r dataframes}
data.frame()

# Column name in quotes, values as vectors
data.frame("Exam" = c(1:4), 
           "Score" = c(88,90,77,98)) 

# When only one value is specified, it will be repeated. 
data.frame("Exam" = c(1:4), 
           "Score" = c(88,90,77,98), 
           "Student" = c("Dave")) 

# If two, it will cycle between the two.
data.frame("Exam" = c(1:4), 
           "Score" = c(88,90,77,98), 
           "Student" = c("Dave", "Ally")) 
```

#### Indexing dfs

```{r indexing DF}
df <- data.frame("Exam" = c(1:4), 
                "Score" = c(88,90,77,98), 
                "Student" = c("Dave", "Ally", "Tyreek", "Kassi"))
df

  # Below are a few ways to index different parts of a df. 

# [column] (single value only selects columns)
# Select the second row of our df
df[2]

# [row,column] to select a single element using numbers 
# Select the value in the second row of the first column 
df[2, 1]

# Leave one value blank to select all
# Select the value of the first row of all columns
df[1,]
# Select the value of the first column of all rows
df[,1]
```

Use `$` to index column by name:

> Use the `$` to index the `Exam` column from `df`

```{r}
df$Exam

```

Note the difference between these two.

Check with `typeof()`

```{r}
df[2]
typeof(df[2])

mean(df[2])

df$Score
typeof(df$Score)

mean(df$Score)
```

You can further index the output from when you index with the `$`

> first use the `$` to index the `Student` column, then use brackets to index the name of the 2nd student.

```{r}
df$Student[2]
```

Instead of using the `$` to index by name, you can also use double brackets

```{r}
df[["Student"]][2]
```

This may be familiar if you have knowledge of other coding languages, but is a little more verbose.
