---
title: "R Notebook"
output: html_notebook
---


Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*. 

#Loading Packages

```{r}
install.packages("tidyverse")
install.packages("haven")
install.packages("readr")
install.packages("readxl")
install.packages("openxlsx")
library(tidyverse)
library(haven)
library(readr)
library(readxl)
library(openxlsx)
```


#Loading the File in

```{r}
#hint: use read.csv() to load in the file


#additional hint: customfilename = read.csv('filepath')


```


#view the file
```{r}
#hint: use view() 

```


#Q1: Correlation between age and ASD diagnosis. 4-11 year olds
```{r}
#Data manipulation

#make it so that Class.ASD in the dataframe is not binary ("YES/NO"), but numeric (1/0). There are many ways which this can be done. ifelse() is one way. 



#try to find more ways on how to convert binary to numeric






# Fit the logistic regression model 
my_model = glm(outcome ~ predictor1 + predictor2, family = binomial, data = customfilename)

# View the model summary 
summary(my_model)


```

*Interpret Model Summary:*


#Make Graph for Q1
```{r}
#Make a graph.
#https://psyc193l.github.io/index.html <-- Ch 7 will help you figure out  

#make a box plot 


#see if any other graphs would be a good fit to represent the data




```




#Q2: Correlation between Jaundice diagnosis and ASD diagnosis. 4-11 year olds
```{r}
# Try your best! This one is less handholdy

#chi square test 
#https://www.datacamp.com/tutorial/chi-square-test-r




```

*Interpret Model Summary:*


#Make Graph for Q2
```{r}
#Make a graph.
#https://psyc193l.github.io/index.html <-- Ch 7 will help you figure out  





```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.
