---
title: ""
author: ""
date: ""
output: html_document
---

```{r}
library(tidyverse)
# Modify the file path in the code below to properly load the "NFLScores2021.RData" file
load("NFLScores2021.RData")
```

You realized after playing around a bit with your football analytics hat that maybe being a pokemon researcher was not the most lucrative opportunity for you to be implementing your R skills... After impressing with all your work so far, you were able to land a job doing some real NFL analytics! You have been given the data from the entire 2021 NFL season in the `NFL` df. 

`NFL` contains the following variables:

* `game_id` - an arbitrary ID for the game
* `week` - what week of the season the game was played
* `day` - what day of the week the game was played
* `home_team` - who the home team was
* `away_team` - who the away team was
* `home_score` - the score of the home team
* `away_score` - the score of the away team
* `season_type` - whether this was the regular season or playoffs
* `roof` - what type of stadium the game was played in
* `surface` - the surface type the stadium had
* `start_time` - what time the game started
* `div_game` - whether this was a game with two teams from the same division

Your job is to use this data to try and learn all you can to give your new team the edge in the upcoming season, and have been given a stack of tasks to complete to help with this. For each question, you must find the answers numerically AND create a graph to visualize it.

*NOTE:* 
> You may sometimes have to compute new variables or modify existing ones to answer these questions!
> There may be more than one way to answer a question. Part of this exercise is thinking about what kind of evidence you can look for with the data you have, and what would help make a compelling answer.

### Part 1:

1. Does the playing surface impact points scored by the away team?

  A. What are some reasons why this might be true?

    - 
  
  B. What are some reasons this might not be true?

    - 

  C. What is your prediction?

    -
    
  D. Investigate

  
```{r}


```
  
  E. Summarize

    - 
    
  F. Overall conclusion and rationale

    -     


2. Is there a home field advantage?

  A. What are some reasons why there might be?

    - 
  
  B. What are some reasons why there might not be?

    - 

  C. What is your prediction?

    -
    
  D. Investigate

  
```{r}


```
  
  E. Summarize

    - 
    
  F. Overall conclusion and rationale

    - 

3. How does the number of points scored per game compare from the first half of the **REGULAR SEASON** to the second half of the **REGULAR SEASON**?

  A. What is your prediction?

    - 
  
  B. What are some reasons why this might be true?

    - 

  C. What are some reasons this might not be true?

    -
    
  D. Investigate

  
```{r}


```
  
  E. Summarize

    - 

  F. Conclusion

    - 
    
  G. Now, instead of comparing the first half of the **REGULAR SEASON** to the second half, compare across the entire **REGULAR SEASON** week by week.

  
```{r}


```

  H. Is the pattern/relationship consistent with the one above? If not, in what way is it different?

    - 
    
  I. Overall conclusion and rationale

    - 


4. Does the average difference between the winning score and the losing score (the score differential) increase or decrease as you get farther into the season? 
  (*hint:* you may find the `abs()` function useful here)

  A. What are some reasons why this might be true?

    - 
  
  B. What are some reasons this might not be true?

    - 

  C. What is your prediction?

    -
    
  D. Investigate

  
```{r}


```
  
  E. Summarize

    - 
    
  F. Now, use an alternative type of visualization to investigate

  
```{r}

```

  G. Is the pattern/relationship the same as above? If not, in what way is it different?

    - 
    
  H. Overall conclusion and rationale

    - 

5. Come up with your own question you are interested in exploring with this data.

  A. What is the question?

    - 

  B. What is your prediction?

    - 
  
  C. What are some reasons why this might be true?

    - 

  D. What are some reasons this might not be true?

    -
    
  E. Investigate

  
```{r}

```
  
  F. Summarize

    - 
    
  G. Overall conclusion and rationale

    - 

6. Come up with another question you are interested in exploring with this data.

  A. What is the question?

    - 

  B. What is your prediction?

    - 
  
  C. What are some reasons why this might be true?

    - 

  D. What are some reasons this might not be true?

    -
    
  E. Investigate

  
```{r}

```
  
  F. Summarize

    - 
    
  G. Overall conclusion and rationale

    - 
    
### Part 2:

Answer the following without using visualizations:

1. How many games did each team win?

```{r}

```

2. Did home or away teams win more?

```{r}

```

    - Answer here

3. Which team scored the most points on average at home? Away?

```{r}

```

    - Answer here

4. Which team had the highest average *winning* point differential (the difference between the winning score and the losing score)?

```{r}

```

    - Answer here

5. Did the day the game was played impact the total points scored?

```{r}

```

    - Answer here



# Feedback

Please save the appropriate number to the variables below:

1. Approximately how long (in minutes) do you think it took you to complete this assignment?

```{r}
timeEstimate = 
```

2. How difficult or challenging did you find this assignment?

Extremely easy -------------------------------------- Extremely challenging 
                                                     (impossible to complete)
    1                                                           10
    
```{r}
challenge = 
```
    
    
3. How engaging or fun did you find this assignment?
  
Extremely Boring and Dry -------------------------------------- Extremely Engaging and Fun 
          1                                                                   10

```{r}
engagement = 
```

4. If you have any other feedback about this assignment, please provide it below.






