# Control Flow

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(palmerpenguins)
```

## If/Else statements

### Traditional

`if` statements work as such: 

**if** some test/condition evaluates to `TRUE`, execute some specific code. 

`if` statement syntax:

```{r eval=FALSE}
if(some test/condition to evaluate) {
  code for what to do if that test/condition evaluates to true
}
```

For example:

```{r}
x = 4

if(3 < x) {
  print("The condition evaluated TRUE")
}
```

> Fill in the blanks below to create an `if` statement that prints "hello world" if x is greater than 1

```{r}
if(x > 1) {
  print("hello world")
}
```

It is always good practice to set up an alternative for when the test evaluates to `FALSE`. That is where `else` statements come in.

> Run the code below a few times and observe the output.

```{r}
x = sample(c(1:6), 1) # From the values 1 to 6, sample 1 value

if(3 < x) {
  print("The condition evaluated TRUE")
} else {
  print("the condition evaluated FALSE")
}
x
```

Instead of using `else`, you use `else if()` and specify another test. 

> Run the code below a few times and observe the output.

```{r}
x = sample(c(1:6), 1)

if(4 < x) {
  print("The first condition evaluated TRUE")
} else if (2 < x & x < 5) { 
  print("The second condition evaluated TRUE")
} else {
  print("Neither the first or second condition evaluated TRUE.")
}

x
```

Writing `if` statements like this is most useful when the code you want to run executes a function

There are two alternative ways to write `if...else` statements. 

### ifelse()

`ifelse()` statements take the form:

`ifelse(test, the value to return if the test evaluates *TRUE*, the value to return if the test evaluates *FALSE*)`

```{r}
x = sample(c(1:6), 1)

ifelse(3 < x, 
       "The test evaluated to TRUE", 
       "The test evaluated to FALSE")

x
```

Multiple `ifelse()` statements can be chained together, akin to an `else if`.

```{r}
x = sample(c(1:6), 1)

ifelse(4 < x, 
       "The first condition evaluated true.",
       ifelse(2 < x & x < 5, 
              "The second condition evaluated true.", 
              "Neither the first or second condition evaluated true."))

x
```

### case_when()

`case_when()` is just a different way to formulate `ifelse()` strings.

```{r}
x = sample(c(1:6), 1)

case_when(
  x < 4 ~ "The first condition evaluated true.",
  2 < x & x < 5 ~ "The second condition evaluated true.",
  TRUE ~ "Neither the first or second condition evaluated true."
)

x
```

**In sum:**

- Traditional `if...else` for executing some code.
- `ifelse()` and `case_when()` for returning specific values.

## Loops

Loops are used to repeat certain code iteratively.

```{r eval=FALSE}
for (val in sequence) 
  {code to be executed}
```

The `for` initiates for for loop, `val` is completely arbitrary and can be replaced with anything.

> Execute the code below and compare the values of x before and after the for loop code

```{r}
x = c(1:10) # Exam scores

x

for (i in 1:length(x)) {
  x[i]= x[i] + 1 # Set the ith X to be equal to itself + 1
  # This will be iterated through each value in x
}

x # Look at output to verify changes
```

`for` loops are often combined with `if` statements to apply conditional code iteratively through your data. 

E.g., grant bonus credit for SONA participation:

```{r}
y = data.frame("Exam" = c(1:4), 
               "Score" = c(88,90,77,98), 
               "Student" = c("Dave", "Ally", 
                             "Tyreek", "Jeanie"), 
               "Sona" = c(0,1,1,0))

y

for (i in 1:nrow(y)) { 
    # Use nrow for a dataframe
  if(y$Sona[i] == 1){ 
    # $ to index -- You want the y dataframe, 
    # the Student column, and the ith row. 
    y$Score[i] = y$Score[i] + 5 
          # For every row in the Score column of 
          # the y dataframe, if the condition y$Sona[i] == 1 
          # evaluates to TRUE, that value is going to be 
          # equal to what is currently there + 5.
  }
}
```

The same task can be accomplished using `ifelse()`, since the goal here is to return values:

```{r}
y = data.frame("Exam" = c(1:4), 
               "Score" = c(88,90,77,98), 
               "Student" = c("Dave", "Ally", 
                             "Tyreek", "Jeanie"), 
               "Sona" = c(0,1,1,0))

for (i in 1:nrow(y)) {
  y$Score[i] = ifelse(y$Sona[i] == 1, # Test
                      y$Score[i]+5, # What to do if TRUE
                      y$Score[i]) # What to do if FALSE
}

y
```

Only Ally and Tyreek's scores have changed.

