---
title: ""
author: ""
date: ""
output: html_document
---

```{r}
library(tidyverse)
```


1. 
  A. define a variable `z` that will randomly sample a single value from `1:100`. Copy/paste this code to the top of the code chunks for #1B:1D.

```{r}
z <- sample(c(1:100), 1)
z
```


  B. Write an `if` statement that will `print()` "My first R if" if `z` is less than 20. Run all the code in the cell.

```{r}
z <- sample(c(1:100), 1)
z
if(z < 20) {
  print("My first R if")
}
```


C. Add an `else` condition to your `if` statement that will print, "Still my first R if, but z is not less than 20." Run all the code in the cell.

```{r}
z <- sample(c(1:100), 1)
z
if(z < 20) {
  print("My first R if")
} else {
  print("Still my first R if, but z is not less than 20.")
}
```


D. Between your `if` and `else` conditions, add an `else if` that will print "The else if evaluated TRUE!" when z is greater than 40 but less than 80. Run all the code in the cell.

```{r}
z <- sample(c(1:100), 1)
z
if(z < 20) {
  print("My first R if")
} else if (40 < z & z < 80) {
  print("The else if evaluated TRUE!")
} else {
  print("Still my first R if, but z is not less than 20.")
}
```


E. Try running all the code in the cell for #1D multiple times and see how often each string gets printed.


2. Reformat your code from #1D to use the `ifelse()`

```{r}
z <- sample(c(1:100), 1)
z
ifelse(z < 20,
       "My first R if",
       ifelse(40 < z & z < 80,
              "The else if evaluated TRUE!",
              "Still my first R if, but z is not less than 20."))
```

3. Reformat your code from #1D to use the `case_when()`

```{r}
z <- sample(c(1:100), 1)
z
case_when(z < 20 ~ "My first R if",
          40 < z & z < 80 ~ "The else if evaluated TRUE!",
          TRUE ~ "Still my first R if, but z is not less than 20.")
```

4. Use a `for` loop to to subtract 2 from all values in vector `v`.

```{r}
v = c(19, 22, 30, 23, 15, 22, 24, 19, 30, 23)

for (i in 1:length(v)) {
  v[i]= v[i] - 2}

v
```

5.
A. Use a `for` loop to give a 1.5x bonus only to the employees in dataframe `work_df` who worked overtime.

```{r}
work_df <- data.frame("Name" = c("Jim", "Jo", "Jack", "Jana"),
                     "Pay" = c(80, 120, 100, 150),
                     "Overtime" = c(0,1,0,1))


for (i in 1:nrow(work_df)) { 
  if(work_df$Overtime[i] == 1){ 
    work_df$Pay[i] = work_df$Pay[i]*1.5 
  }
}
```


B. Rewrite your code using `ifelse()` syntax to accomplish the same goal.

```{r}
for (i in 1:nrow(work_df)) {
  work_df$Pay[i] = ifelse(work_df$Overtime[i] == 1,
                      work_df$Pay[i]*1.5,
                      work_df$Pay[i])
}
```

# Feedback 

Please save the appropriate number to the variables below:

1. Approximately how long (in minutes) do you think it took you to complete this assignment?

```{r}
timeEstimate = 
```

2. How difficult or challenging did you find this assignment?

Extremely easy -------------------------------------- Extremely challenging 
                                                     (impossible to complete)
    1                                                           10
    
```{r}
challenge = 
```
    
    
3. How engaging or fun did you find this assignment?
  
Extremely Boring and Dry -------------------------------------- Extremely Engaging and Fun 
          1                                                                   10

```{r}
engagement = 
```

4. If you have any other feedback about this assignment, please provide it below.







