---
title: ""
author: ""
date: ""
output: html_document
---

# Set up

```{r}
library(tidyverse)
msleep2 = msleep %>%
  select(-conservation)
```

1. Write some code to find the number of instances of each unique value of `vore`.

```{r}
msleep2 %>%
  pull(vore) %>%
  table()
```

2. 
   A. Modify your code from exercise 1 to show the proportions

```{r}
msleep2 %>%
  pull(vore) %>%
  table() %>%
  prop.table()
```

   B. verify that they sum to 1.

```{r}
msleep2 %>%
  pull(vore) %>%
  table() %>%
  prop.table() %>%
  sum()
```

3. Use `summarize()` to find the average number of hours each animal spends awake and the average brain weight. If there are any issues with missing values, modify your code to account for this.

```{r}
msleep2 %>%
  drop_na() %>%
  summarize(awake_avg = mean(awake),
            brainwt_avg = mean(brainwt))
```

4. Modify your code from exercise 3 to show averages for each level of `vore`.

```{r}
msleep2 %>%
  drop_na() %>%
  group_by(vore) %>%
  summarise(awake_avg = mean(awake),
            brainwt_avg = mean(brainwt))
```

5. 
   A. Find the average of all variables that start with "sleep" for every level of `vore`.
   
```{r}
msleep2 %>%
  group_by(vore) %>%
  summarize(across(starts_with("sleep"),
                   mean, na.rm = TRUE))
```
   
   B. Find the average and sd for all variables that end in "wt" for every level of `vore`.
   
```{r}
msleep2 %>%
  group_by(vore) %>%
  summarize(across(ends_with("wt"),
                   list(mean = mean, sd = sd), na.rm = TRUE))
```
   
   C. Find the number of unique values for each variable that is a *character*.

```{r}
msleep2 %>%
  drop_na() %>%
  summarize(across(where(is.character), n_distinct))

```


# Feedback 

Please save the appropriate number to the variables below:

1. Approximately how long (in minutes) do you think it took you to complete this assignment?

```{r}
timeEstimate = 
```

2. How difficult or challenging did you find this assignment?

Extremely easy -------------------------------------- Extremely challenging 
                                                     (impossible to complete)
    1                                                           10
    
```{r}
challenge = 
```
    
    
3. How engaging or fun did you find this assignment?
  
Extremely Boring and Dry -------------------------------------- Extremely Engaging and Fun 
          1                                                                   10

```{r}
engagement = 
```

4. If you have any other feedback about this assignment, please provide it below.




