---
title: ""
author: ""
date: ""
output: html_document
---

```{r}
library(tidyverse)
# Modify the file path in the code below to properly load the file
load("~/Desktop/GitHub/R Bootcamp/Summarizing and Transforming Data - 4/Transformations_data/penguins_sep.RData")
# Modify the file path in the code below to properly load the file
load("~/Desktop/GitHub/R Bootcamp/Summarizing and Transforming Data - 4/Transformations_data/join_practice.RData")

penguins_set1 = slice_sample(penguins1, n = 20)
penguins_set2 = slice_sample(penguins1, n = 20)
```

1. Use `pivot_longer()` to transform the data found in `table4a`. The code should result in a df that has 3 total columns (country, year, and population count) and 6 total rows.

```{r}
table4a %>%
  pivot_longer(cols = c(`1999`, `2000`),
               names_to = "year",
               values_to = "population_count")
```

2. Use `pivot_wider()` to transform the data found in `table2` (specifically, the `type` column). The code should result in a df that has 4 total columns (country, year, cases, population) and 6 total rows.

```{r}
table2 %>%
  pivot_wider(names_from = type, 
              values_from = count)

```

3. 
  A. Look at the dfs `penguins1`, `penguins2`, and `penguins3` individually. Then, use `bind_rows()` to combine the `penguins1` and `penguins2` dfs.

```{r}
bind_rows(penguins1, penguins2)
```

  B. Pipe your result from 3A to combine with `penguins3`.

```{r}
bind_rows(penguins1, penguins2) %>%
  bind_rows(penguins3)
```

4. Using dfs `x` and `y`, write some code that will return a new df that contains only the observations common in both.

```{r}
inner_join(x, y)
```

5. Using dfs `x` and `y`, write some code that will return a new df that contains all variables across both dfs, but only from observations in `x`.

```{r}
left_join(x, y)
```

6. Using dfs `x` and `y`, write some code that will return a new df that contains all variables across both dfs, but only from observations in `y`.

```{r}
right_join(x, y)
```

7. Using dfs `x` and `y`, write some code that will return a new df that contains all variables and observations from both dfs.
  
```{r}
full_join(x, y)
```

8. Using dfs `penguins_set1` and `penguins_set2`, write some code that will return a new df that contains all unique observations from both samples.

```{r}
union(penguins_set1, penguins_set2)
```

9. Using dfs `penguins_set1` and `penguins_set2`, write some code that will return a new df that contains only the observations that appeared in both samples.

```{r}
intersect(penguins_set1, penguins_set2)
```

10. Using dfs `penguins_set1` and `penguins_set2`, write some code that will return a new df that contains only the unique observations in `penguins_set1`.

```{r}
setdiff(penguins_set1, penguins_set2)
```



# Feedback 

Please save the appropriate number to the variables below:

1. Approximately how long (in minutes) do you think it took you to complete this assignment?

```{r}
timeEstimate = 
```

2. How difficult or challenging did you find this assignment?

Extremely easy -------------------------------------- Extremely challenging 
                                                     (impossible to complete)
    1                                                           10
    
```{r}
challenge = 
```
    
    
3. How engaging or fun did you find this assignment?
  
Extremely Boring and Dry -------------------------------------- Extremely Engaging and Fun 
          1                                                                   10

```{r}
engagement = 
```

4. If you have any other feedback about this assignment, please provide it below.







