# Summarizing Data

```{r}
library(tidyverse) # Load tidyverse packages
library(palmerpenguins) # Load penguins data
load(url("https://github.com/Psyc193L/Psyc193L.github.io/blob/main/data/penguins_example.RData?raw=true")) # Load example data
```

## Table and Count

To get the *number of instances* of each unique value, use `table()` (for a table output) or `count()` (for a df/tibble output).

> Complete the code below to get the number of instances of each `species` using both `table()` and `count()`

```{r}
penguins %>%
  pull(X) %>%
  X()

X %>%
  count(X)
```

### Proportions

For tables, you add `prop.table()`

> Take your code for `table()` above and then pipe it to `prop.table()`

```{r}


```

For dfs, you have to manually compute the proportions and add them as a new variable.

```{r}
penguins %>%
  count(species) %>%
  mutate(proportion = n / length(penguins$species))
```

Always check that your proportions sum to 1

> Take your code from above and use `sum()` to make sure they both sum to 1.

```{r}


```

## Summary

`summary()` gives a quick quantitative summary of each variable.

> Use `summary()` on `penguins`

```{r}

```

## Summarize

`summarize()` gives specific summaries of your data.
- has a similar format to `mutate()`
- define new variables and how their values are computed

```{r}
penguins_example
```

> Complete the code below to create 3 summary variables: 1. "flipper_m" that has the mean of `flp_mm`, 2. "mass_m" which has the mean of `mass`, 3. "ratio" which has the mean ratio of `mass` to `flp_mm`.

```{r}
penguins_example %>%
  summarize(X = mean(X),
            mass_m = X,
            ratio = mean(X))
```

summary is designed to work with summary functions -- those that output a single value.

To verify the above is true:

```{r}
firstCol = c(181, 186, 192, 196, 211, 230)
mean(firstCol)
secondCol = c(3750, 3800, 3500, 3900, 4500, 5700)
mean(secondCol)
thirdCol = c(3750/181, 3800/186, 3500/192, 3900/196,
             4500/211, 5700/230)
mean(thirdCol)
```

## Grouping Data

`group_by()` organizes your data into subgroups based on shared values. 

> Compare the output of the following:

```{r}
penguins %>%
  glimpse()

penguins %>%
  class()
```

```{r}
penguins %>%
  group_by(species) %>%
  glimpse()

penguins %>%
  group_by(species) %>%
  class()
```

> Note the differences you observe:







## Grouped Summaries

`group_by()` allows you to perform operations group-wise, analyzes data separately according to the different levels of some grouping variable.

> Using the `penguins_example` df, use summarize to find the mean `flp_mm`, but first use `group_by()` to group the data by `species`.

```{r eval=FALSE}
penguins_example %>%
  group_by(species) %>%
  summarize(m = mean(flp_mm))
```


Some functions designed for `summarize()`

- `n()` -- gives the number of values.

> Complete the code below to find the number of values of observations on each `island` and each `species` within an island

```{r}
penguins %>%
  group_by(X, X) %>%
  summarize(n = X)
```

### Using `across()` with `summarize()`


> First, complete the code below to get the mean of `bill_length_mm` and `bill_depth_mm` for each `species`.

```{r}
penguins %>%
  drop_na() %>%

```

Use `across()` within a `summarize()` call to make use of helper functions.

> Instead of specifying each variable, as done above, use `across()` and a helper function to get the relevant variables.

```{r}
X
  X
  X
  summarize(X(X,
                   mean))
```


You can perform multiple summary functions at the same time by passing them as a list rather than just the function name.

> Take your code from above and replace `mean` with `list(mean = mean, sd = sd)`

```{r}

```

As another example, say you wanted to find the number of unique levels for the different factors in your data. This could be done on the entire dataset:

> Complete the code below and use `n_distinct` to find the number of unique levels for the different factor variables in the data

```{r}
penguins %>%
  drop_na() %>%
  
```

> Do the same as above but this time find the levels of those variables *for each* `species`

```{r}
penguins %>% 
  drop_na() %>%

```

## Extra Resources

* dplyr documentation for [row-wise](https://dplyr.tidyverse.org/articles/rowwise.html) and [column-wise](https://dplyr.tidyverse.org/articles/colwise.html) operations
* [across](https://dplyr.tidyverse.org/reference/across.html) documentation
* [data wrangling cheatsheet](https://rstudio.com/wp-content/uploads/2015/02/data-wrangling-cheatsheet.pdf)