---
title: ""
author: ""
date: ""
output: html_document
---

# Part 1:

```{r}
var1 = 9
var2 = 6
```


 1. Arithmetic Operators

 A. Find the sum of 8 and 8
```{r}
8+8
```

 B. Find the product of 2 and 7
```{r}
2*7
```

 C. Exponentiate 3 to the power of 3
```{r}
3^3
```

 D. Find the difference of 89 and 16
```{r}
89-16
```

 E. Find the quotient of 9 and 2

```{r}
9/2
```

 2. Comparison Operators

 A. Write a test to evaluate whether `var1` is less than `var2`
```{r}
var1<var2
```

 B. Write a test to evaluate whether `var1` is equal to `var2`
```{r}
var1 == var2
```

 C. Write a test to evaluate whether the sum of `var1` and `var2` is greater than or equal to the product of `var1` and `var2`
```{r}
var1 + var2 >= var1*var2
```

 D. Write a test to evaluate whether `var2` squared is not equal to `var1` cubed.
```{r}
var2^2 != var1^3
```

 E. Write a test to evaluate whether the remained of `var1` squared divided by `var2` is greater than 0.

```{r}
var1^2/var2 > 0
```

 F. Write a test to evaluate whether `var2` squared is less than or equal to 50

```{r}
var2^2 <= 50
```

 3. Logical Operators

 A. Use `&` to evaluate 2A. and 2C.
```{r}
8+8 & 3^3
```

 B. Use `!` to evaluate 2D.
```{r}
!var2^2 != var1^3
```

 C. Use `|` to evaluate 2E. and 2B.
```{r}
var1^2/var2 > 0 | var1 == var2
```

 D. Now, use each operator (`&`, `!`, and `|`) combined with at least one other operator (logical or comparison operators).

`&`

```{r}
TRUE & FALSE >= FALSE
```

`!`

```{r}
!TRUE > FALSE
```

`|`

```{r}
TRUE | FALSE != FALSE
```

 4. Define one variable that contains the number 3, another containing "Hi!", and another containing `FALSE`. Use `typeof()` to verify the type of each of these variables.

```{r exercise 4}
x <- 3
y <- "Hi!"
z <- FALSE

typeof(x)
typeof(y)
typeof(z)

```


 5. Create 3 vectors that each contain a different type of data (number, character, and logical). See which operations can be applied to each vector.

```{r exercise 5}
Vector1 <- c(1, 3, 5, 7)
Vector2 <- c("Hi!","Hello")
Vector3 <- c(TRUE, FALSE)

Vector1*3
typeof(Vector2)
!Vector3
```

 6. Index and save the first element from your first vector to a variable called `first_first`, and the last element from your last vector to one called `last_last`.

```{r exercise 6}
first_first <- Vector1[1]
first_first
last_last <- Vector3[2]
last_last
```

 7. Complete the code below to create a dataframe called `my_df` that has information about you.

```{r exercise 7}
my_df <- data.frame("Name" = c("Mira","Julianne","Mateo"),
               "Course" = c("PSYC193L"),
               "Term" = c("Fall"))

my_df
```

 8. 
 
 A. Index the first row of your dataframe and save it to a variable called `df_first_row`. Index the course name (1st value of 2nd row) and save it to a variable called `course_name`. 
 
```{r exercise 8a}
df_first_row <- my_df[1,]
df_first_row
course_name <- my_df[1,2]
course_name
```
 
 B. Now index the course name in a different way and save it to a variable called `course_name_alt`. Write a test to valuate whether `course_name` and `course_name_alt` are equivalent.

```{r exercise 8b}
course_name_alt <- my_df["Course"]
  course_name_alt
  
  course_name == course_name_alt
```


# Part 2:

 1. Install the packages listed below:

- tidyverse
- patchwork
- magrittr
- viridis
- RColorBrewer
- DT
- ggExtra
- gridExtra
- reprex
- knitr
- markdown
- palmerpenguins
- janitor
- ggridges

```{r, eval = FALSE}
install.packages("tidyverse",
                 "patchwork",
                 "magrittr",
                 "viridis",
                 "RColorBrewer",
                 "DT",
                 "ggExtra",
                 "gridExtra",
                 "reprex",
                 "knitr",
                 "markdown",
                 "palmerpenguins",
                 "janitor",
                 "ggridges")

```


 2. Create a new code chunk below. Name the code chunk "exercise 2".

```{r exercise 2}


```

 3. Clean up all the code below so that it follows the proper formatting guidelines listed above.

```{r exercise 3, eval = FALSE}
df[, 4]
df[, 2]
df[, 0]

mean(df$col, na.rm = TRUE)
mean(df$col, na.rm = TRUE)

3 + 4 + 5
- 2 * 8 ^ 2

#compute persons height
height <- feet * 12 + inches
T + 1 < 2
! F | F + 1

long_computation('little', bunny = 1, foo*2, hopping, through = 'forest')

```

 4. Rewrite the following code as properly formatted pipe chains.

```{r exercise 4, eval = FALSE}

laces %>%
  pull() %>%
  swoop() %>%
  loop()


me %>%
  wake_up() %>%
  get_out_of_bed() %>%
  get_dressed() %>%
  leave_house()
```

 5. Download the files for today's class that came with the assignment. Import both the .csv and .RData files. Make sure you save them to variables! Copy/paste their file path in the cell below.

```{r exercise 6, eval = FALSE}

```

 6. Export your `my_df` dataframe as a .csv file called "my_dataframe.csv". Export your dataframe and all the variables you saved to an .RData file called "my_data.RData".

```{r exercise 7, eval = FALSE}

```


# Feedback 

Please save the appropriate number to the variables below:

1. Approximately how long (in minutes) do you think it took you to complete this assignment?

```{r}
timeEstimate = 60
```

2. How difficult or challenging did you find this assignment?

Extremely easy -------------------------------------- Extremely challenging 
                                                     (impossible to complete)
    1                                                           10
    
```{r}
challenge = 4
```
    
    
3. How engaging or fun did you find this assignment?
  
Extremely Boring and Dry -------------------------------------- Extremely Engaging and Fun 
          1                                                                   10

```{r}
engagement = 7
```

4. If you have any other feedback about this assignment, please provide it below.




