---
title: ""
author: ""
date: ""
output: html_document
---


1. Use each of the following operators in a new expression:

"+"

```{r}
5 + 5
```

"-"

```{r}
7 - 3
```

"*"

```{r}
6 * 8
```

"/"

```{r}
21 / 3
```

"^"

```{r}
7 ^ 4 
```

"%%"

```{r}
18 %% 2
```


2. Use each of the following operators in a new expression:

"<"

```{r}
5 < 8
```

">"

```{r}
6 > 20

```

"<="

```{r}
1 <= 1
```

">="

```{r}
203 >= 405
```

"=="

```{r}
6 == 6
```

"!="

```{r}
5 != 8
```

3. 
  A. Use each of the operators below in a new expression. 

"&"

```{r}
TRUE & FALSE
```

"|"

```{r}
TRUE | FALSE
```

"!"

```{r}
!TRUE
```

B. Use *each* operator (`&`, `!`, and `|`) combined with at least one operator from exercise 1 or 2 as well.

```{r}
!FALSE == !TRUE
TRUE & TRUE <= FALSE
TRUE | FALSE == !FALSE
```


C. Now, use *each* operator (`&`, `!`, and `|`) combined with at least one *other* operator (logical or comparison operators).

```{r}
TRUE & FALSE < FALSE
!FALSE + !TRUE
FALSE | TRUE == TRUE | FALSE
```


4. Define variables of each of the following types and use `typeof()` to verify their type.

A. number

```{r}
x <- 8
typeof(x)
```

B. character

```{r}
y <- "Salamat"
typeof(y)
```


C. logical

```{r}
z <- TRUE
typeof(z)
```

5. Create 3 vectors that each contain a different type of data (number, character, and logical). See which operations can be applied to each vector.

  A. number

```{r}
Vector1 <- c(1, 4, 6) 
Vector2 <- c("Hi", "Hola", "Bonjour")
Vector3 <- c(TRUE, FALSE)

Vector1 * 3
Vector1 / 2
```

  B. character

```{r}
Vector2[2]

```

  C. logical

```{r exercise 5}
!Vector3
```

6.

  A. Index the 1st and 2nd element from the vector in 5A

```{r}
Vector1[1]
Vector1[2]
```

  B. Index the 2nd and 3rd element from the vector in 5B.
  
```{r}
Vector2[2]
Vector2[3]
```
  
  C. Save the first element from your first vector to a variable called `first_first`.
  
```{r}
first_first <- Vector1[1]
first_first
```

  D. Save the last element from your last vector to one called `last_last`.
  
```{r}
last_last <- Vector3[2]
last_last
```
  

7. Create a dataframe called `my_df` that has information about your top 3 favorite animals. It should contain 3 columns: 1. One that has the words, "first", "second", and "third". 2. Another that has the animals names. 3. A third having a rating, on a scale of 1-10, of how likely you think it is you could beat that animal in a fight to the death.

```{r exercise 7}
my_df <- data.frame("Rank" = c("first", "second", "third"),
                    "Name" = c("Dog", "Wolf", "Cat"),
                    "Rating" = c(5, 1, 7))
my_df
```

8. Index the second row of your dataframe and save it to a variable called `df_second_row`. Index the name of your second favorite animal and save it to a variable called `second_fave`. Index the battle likelihood rating for your third favorite animal and save it to a variable called `third_rating`.

```{r exercise 8}
df_second_row <- my_df[2, ]
second_fave <- my_df[2, 2]
third_rating <- my_df[3, 3]
df_second_row
second_fave
third_rating
```

9. Rewrite the following code as properly formatted pipe chains.

```{r, eval = FALSE}
park(drive(start_car(find("keys")), to = "campus"))
find %>%
  keys %>%
  start_car %>%
  drive to campus %>%
  park

brush(tooth_paste(running_water(tooth_brush)), teeth)

toothbrush %>%
  running water %>%
  toothpaste on teeth %>%
  brush
```


# Feedback 

Please save the appropriate number to the variables below:

1. Approximately how long (in minutes) do you think it took you to complete this assignment?

```{r}
timeEstimate = 15
```

2. How difficult or challenging did you find this assignment?

Extremely easy -------------------------------------- Extremely challenging 
                                                     (impossible to complete)
    1                                                           10
    
```{r}
challenge = 4
```
    
    
3. How engaging or fun did you find this assignment?
  
Extremely Boring and Dry -------------------------------------- Extremely Engaging and Fun 
          1                                                                   10

```{r}
engagement = 7
```

4. If you have any other feedback about this assignment, please provide it below.




