# Color Theory

Load Packages:
```{r}
library(patchwork)
library(RColorBrewer)
library(colorspace) 
library(viridis) 
library(tidyverse)
library(palmerpenguins) 
```

Set Theme:
```{r}
theme_set(theme_classic() + 
            theme(plot.title = element_text(size = 18,
                                face = "bold",
                                hjust = 0.5),
      plot.subtitle = element_text(size = 10, 
                                   color = "grey50",
                                   face = "bold",
                                   hjust = 0.5,
                                   margin = margin(b = 0.2, 
                                                   unit = "inch")),
      plot.tag = element_text(face = "bold"),
      plot.caption = element_text(hjust = 0,
                                  face = 'italic'),
      axis.title.x = element_text(size = 16,
                                  face = "bold",
                                  margin = margin(t = 0.2, 
                                                  unit = "inch")),
      axis.title.y = element_text(size = 16,
                                  face = "bold",
                                  margin = margin(r = 0.2, 
                                                  unit = "inch")),
      axis.text = element_text(face = "bold",
                               color = "black",
                               size = 12)))
```

Color and design principles are often overlooked when considering how to make an effective visualization because they are subtle, but are very important!

The following graphs will serve as examples used throughout:

```{r}
plot_bar = penguins %>%
  ggplot(aes(y = body_mass_g, x = island,
             fill = island)) +
  stat_summary(fun = "mean", geom = "bar") +
  scale_y_continuous(expand = c(0,0))

plot_bar
plot_jitter = penguins %>%
  ggplot(aes(y = body_mass_g, x = island)) +
  geom_jitter(height = 0, width = 0.2, 
              size = 2, alpha = 0.5,
              aes(color = island)) +
    stat_summary(fun.data = "mean_se",
               geom = "pointrange",
               size = 0.5)

plot_jitter
plot_line = penguins %>%
  ggplot(aes(y = body_mass_g, x = bill_depth_mm, color = bill_depth_mm)) +
  stat_summary(fun = "mean", geom = "point", size = 2) +
  stat_summary(fun = "mean", geom = "line", size = 1)

plot_line
plot_hex = penguins %>%
  ggplot(aes(y = body_mass_g,
             x = bill_depth_mm,
             z = flipper_length_mm)) +
  stat_summary_hex() +
  labs(fill = "Flipper Length")

plot_hex
```

*Note: these are not great visualizations, but will be useful to illustrate some different concepts.*

Color choices should be made intentionally and purposefully.

## HCL and Color Theory

You can think of "color" as being composed of 3 parts.

### Hue

e.g., "Blue", "Red", "Yellow"
- organized along a color wheel and defined by their angle
- No inherent order

### Chrominance (Chroma)

Chroma = degree of purity or intensity of a color
- range from a muted/grey to the fully vivid color
- perceived to be ordered

### Luminance

Luminance = brightness of a color. 
- ranges black to white. 
- perceived to be ordered

### Why Does This Matter?

Color mappings should accurately and meaningfully characterize the data it is representing. Beyond *numerical* accuracy, you want differences to be maintained in a viewer's *perception* of those different colors.

Perception of luminance is based on *relative* rather than *absolute* judgments.

HCL color space itself is not even perceptually uniform!

Color values that are *numerically* uniform may not be *perceptually* uniform.

## Categorical 

Color goal with categorical data:
- Distinguish groups *without* an inherent order.

Use a *qualitative* color scale
- Perceptually distinct but equivalently different colors.

To change the color scale and/or palette used in your visualization, you will use another `scale_*_*()` command.

1st `*` - the aesthetic you have mapped, `fill` or `color`. 
2nd `*` - the type of scale you want to use or modify. 

For example, to manually set the HCL parameters of a color space, you would use `scale_*_hue()`. This function has 3 main arguments:

* `h` = range of hues to use 
  + (ranged from 0 - 360 -- default = (c(0,360) + 15))
  + ex. `scale_*_hue(h = c(0,60))`
* `l` = luminance 
  + (lightness; 0-100 -- default = 65)
  + ex. `scale_*_hue(l = 80)`
* `c` = chroma 
  + (intensity of color -- maximum value varies depending on combination of hue and luminance).
  + ex. `scale_*_hue(c = 200)`

`scale_*_manual()` to set colors yourself. The main argument here is `values`, which expects a vector of color names/codes to use.

> Replace the X's below with a color you think would fit:

```{r}
plot_bar +
  scale_fill_manual(values = c("cyan", "lightgreen", "coral"))

plot_jitter +
  scale_color_manual(values = c("magenta", "yellow", 
                                "lightskyblue"))
```

You can also specify which level of the mapped variable is associated with each specific color:

> Replace the X's below to map the colors from above to specific levels, so the colors are in an order you think makes most sense.

```{r}
plot_bar +
  scale_fill_manual(values = c("Torgersen" = "30",
                               "Biscoe" = "60",
                               "Dream" = "90"))
plot_jitter +
  scale_color_manual(values = c("Torgersen" = "25",
                               "Biscoe" = "50",
                               "Dream" = "75"))
```

Choose colors that will be intrinsically informative and intuitive.

## Continuous 

### Sequential

Color goal with continuous data:

- represent the *actual* data values. 
- there **is** an ordering to the values. 

Use a *sequential* color scale (or color *gradient*)
- contains a sequence of colors which convey size and relative distance. 

Use `scale_*_gradient()` - main arguments are a `low` and `high` value over which to define the gradient. 

A sequential scale can be defined over a single hue: 

> Run the first line of code to see the default gradient created with a single hue. Replace the X's below for the second to create a unique gradient over a single hue -- green. (hint: it can be useful to pick a single color and use words like "light", "dark", "medium", "pale" in front, or related colors like olive in this case)

```{r}
plot_line +
  scale_color_gradient()

plot_hex +
  scale_fill_gradient(low = "lightgreen", high = "darkgreen")
```

or multiple hues:

> Replace the X's below to create gradients using brown and red

```{r}
plot_line +
  scale_color_gradient(low = "tan", high = "chocolate")

plot_hex +
  scale_fill_gradient(low = "pink", high = "red")
```

A sequential color gradient should create the perception that values have a meaningful sequential order.

`scale_*_gradientn()` to create a gradient over several colors. The argument `colors` takes a vector of colors over which to linearly create a gradient.

```{r}
plot_line +
  scale_color_gradientn(colors = c("red", "orange", "yellow", 
                                   "green", "blue"))
plot_hex +
  scale_fill_gradientn(colors = c("red", "brown", "yellow"))
```


### Divergent

If you have data with a neutral point or true zero, you would use a *divergent* scale. 
- Essentially two sequential scales appended to a single common point (0, the mean, etc.). 

`scale_*_gradient2()` creates a divergent gradient. Specify a `mid` color in addition to `low` and `high`. 

> Replace the X's below to create a red and yellow gradient with a grey middle.

```{r}
plot_hex +
  scale_fill_gradient2(low = "red", mid = "grey90", high = "yellow",
                       midpoint = mean(penguins$flipper_length_mm, na.rm = TRUE))
```

## Pre-defined Color Scales

R has a number of pre-defined color scales that can be used.

### Built-in

Base R comes with built in color scales.

Each color scale can be used as a function that takes an argument `n` for the number of colors to sample from that color scale, and return those colors' hexcodes.

> Uncomment one row at a time and replace n with different numbers.

```{r}
rainbow(10)
heat.colors(4)
terrain.colors(9)
topo.colors(6)
cm.colors(1)
```

> Pass some base R color samples in as the value for the arguments below:

```{r}
plot_hex +
    scale_fill_gradientn(colors = rainbow(3))
plot_jitter +
  scale_color_manual(values = cm.colors(4))
```

### Brewer

RColorBrewer contains great pre-defined color scales and palettes. All info contained in `brewer.pal.info`

```{r}
brewer.pal.info
```

Palettes are grouped into 3 distinct categories:

1. Qualitative
2. Sequential
3. Divergent

Quickly visualize all the palettes with `display.brewer.all()`

```{r}
display.brewer.all(colorblindFriendly = TRUE, type = "qual") 
```

```{r}
display.brewer.all(colorblindFriendly = TRUE, type = "seq")
```

```{r}
display.brewer.all(colorblindFriendly = TRUE, type = "div")
```

You can see the exact colors used for a given palette and number of colors using `display.brewer.pal()`.

> Replace the X's below to examine a palette that has 3 "Blues", and then 6 "Blues"

```{r}
display.brewer.pal(n = 3, name = 'Blues')
display.brewer.pal(n = 6, name = 'Blues')
```

The specific values of those colors can be identified with `brewer.pal()`.

> Take your code from above and use `brewer.pal()` instead of `display.brewer.pal()`

```{r}
brewer.pal(n = 3, name = 'Blues')
brewer.pal(n = 6, name = 'Blues')
```

`scale_*_brewer()` for categorical data and `scale_*_distiller()` for continuous. Just pass in the name of the specific `palette`.

> Run the code below and examine the different graphs

```{r}
plot_hex +
    scale_fill_distiller(palette = "GnBu")

plot_line +
  scale_color_distiller(palette = "RdPu")

plot_jitter +
  scale_color_brewer(palette = "Dark2")

plot_bar +
  scale_fill_brewer(palette = "Set2")
```

Since `brewer.pal()` gives a vector of color values from a specific palette, that can be used to set colors "manually".

> Replace the X's below with a number of colors and name of a palette respectively.

```{r}
plot_hex +
    scale_fill_gradientn(colors = brewer.pal(n = 3, name = 'YlOrRd'))
plot_jitter +
  scale_color_manual(values = brewer.pal(n = 4, name = 'PuBu'))
```

### Grey scale

`scale_*_grey()` is used for categorical data. The scale can be selected automatically, or you can specify the `start` and `end` values which range from 0 (dark) to 1 (light).

> Run the code below to see the default values:

```{r eval=FALSE}
plot_jitter + 
  scale_color_grey()

plot_bar + 
  scale_fill_grey()
```

> Replace the X's below to try different ranges:

```{r}
plot_bar + 
  scale_fill_grey(start = 0, end = 1)

plot_bar + 
  scale_fill_grey(start = 0.4, end = 0.7)
```

### Viridis

`viridis` -- palettes interpretable under a variety of color vision types.

`scale_*_viridis()` -- specific palette is set with the `option` argument, and can be applied to categorical data by using the `discrete` argument

> In the code below, add `discrete = TRUE` where needed.

```{r}
plot_bar + 
  scale_fill_viridis(discrete = TRUE)

plot_jitter + 
  scale_color_viridis(discrete = TRUE, option = "plasma")

plot_line + 
  scale_color_viridis(option = "inferno")

plot_hex + 
  scale_fill_viridis()
```

You can also generate specific color codes from these palettes

```{r}
viridis(4)
magma(9)
inferno(2)
plasma(7)
```

### colorspace

Info on all the palettes can be accessed with `hcl_palettes()`.

```{r}
hcl_palettes()
```

You can also `plot` them to actually see the palettes themselves.

```{r}
hcl_palettes(type = "Qualitative", plot = TRUE)
hcl_palettes(type = "Sequential (single-hue)", plot = TRUE)
hcl_palettes(type = "Sequential (multi-hue)", plot = TRUE)
hcl_palettes(type = "Diverging", plot = TRUE)
```

You use these palettes similarly to `brewer.pal()`. Each scale has its own function, where you specify the `palette` and `n`umber of colors from it. That vector of colors can then be used in your ggplot code.

> Replace the X's below with a number and one of the 3 palettes listed

```{r}
qualitative_hcl(n = 3, palette = "Harmonic")
sequential_hcl(n = 3, palette = "SunsetDark")
diverging_hcl(n = 3, palette = "Lisbon")

plot_hex +
    scale_fill_gradientn(colors = sequential_hcl(n = 5, 
                                                 palette = "Hawaii"))
```

Many colorspace palettes attempt to be identical to RColorBrewer or viridis ones.

The code below compares a color palette from brewer and viridis to their colorspace counterpart:

```{r}
(plot_bar +
    scale_fill_manual(values = brewer.pal(n = 3, name = 'BuGn')) +
 ggtitle("brewer")) + (plot_bar +
    scale_fill_manual(values = sequential_hcl(n = 3, palette = "BuGn")) +
      ggtitle("colorspace"))
(plot_hex +
    scale_fill_viridis(option = "viridis") +
    ggtitle("viridis")) + (plot_hex +
    scale_fill_gradientn(colors = sequential_hcl(n = 12, 
                                                 palette = "viridis")) +
      ggtitle("colorspace"))
```

Whenever there is a similar palette available from another package, probably go with that one.

`demoplot()` -- Makes quick demo plot to test palette

> Replace the X's below to test different palettes with different numbers of colors

```{r}
demoplot(sequential_hcl(n = 3, palette = "Emrld"), "bar")
demoplot(sequential_hcl(n = 6, palette = "Mint"), "scatter")
demoplot(sequential_hcl(n = 9, palette = "Lajolla"), "lines")
```

Since it just needs a vector of colors, you can use `demoplot()` with colors generated from other packages (e.g., `viridis(n)`, `brewer.pal()`, etc.)

> Use functions covered earlier to create color values that can by used by demoplot. Use at least one from Base R, viridis, and brewer.

```{r}
demoplot(terrain.colors(6), "lines")
demoplot(viridis(5), "bar")
demoplot(brewer.pal(6, "Dark2"), "scatter")
```


## References

Stauffer, R., Mayr, G. J., Dabernig, M., & Zeileis, A. (2015). Somewhere over the rainbow: How to make effective use of colors in meteorological visualizations. *Bulletin of the American Meteorological Society, 96*(2), 203-216.