---
title: ""
author: ""
date: ""
output: html_document
---

```{r}
library(palmerpenguins)
library(RColorBrewer)
library(colorspace)
library(viridis)
library(tidyverse)
```

For these questions, you will use template graphs *similar* to those used in the Color Theory lecture. Fill in the blanks below to complete the code and create your template graphs. These should **NOT** be *IDENTICAL* to any graphs from the lecture. Make any other additional tweaks you want.

```{r}
plot_bar = penguins %>%
  ggplot(aes(y = , x = ,
             fill = )) +
  stat_summary(fun = "mean", geom = "bar") +
  scale_y_continuous(expand = c(0,0))

plot_jitter = penguins %>%
  ggplot(aes(y = , x = )) +
  geom_jitter(height = 0, width = 0.2, 
              size = 2, alpha = 0.5,
              aes(color = )) +
    stat_summary(fun.data = "mean_se",
               geom = "pointrange",
               size = 0.5)

plot_line = penguins %>%
  ggplot(aes(y = , x = , color = )) +
  stat_summary(fun = "mean", geom = "point", size = 2) +
  stat_summary(fun = "mean", geom = "line", size = 1)

plot_hex = penguins %>%
  ggplot(aes(y = ,
             x = ,
             z = )) +
  stat_summary_hex()
```

1. Change the colors in `plot_bar` and `plot_jitter` to manually set values. Find a combination of colors you think work well together and are perceptually uniform.

```{r}

```

2. Using `plot_line` and/or `plot_hex`...

A. Create 2 *single hue* gradients that you think seem perceptually uniform using...

A light and dark purple:

```{r}

```

A light and dark green:

```{r}

```


B. Create 2 *multiple hue* gradients (using either function to do so) that you think seem perceptually uniform using...

purple and yellow:

```{r}

```

pink and green:

```{r}

```


3. Create 2 visualizations using *divergent* scales that you think are equally uniform in both directions from the midpoint. Use `mean(penguins$X, na.rm = TRUE)` for the midpoint, replacing `x` with the appropriate variable from your graph.

red and blue:

```{r}

```

orange and yellow:

```{r}

```

4. Modify each of your template visualizations to use a different palette from RColorBrewer (hint: make sure you use the appropriate type of color scale given the type of data!).

`plot_bar` using "Set3"

```{r}

```

`plot_jitter` using "Pastel2"

```{r}

```

`plot_line` using "YlGn"

```{r}

```

`plot_hex` using "GnBu"

```{r}

```


5. Take your code from Exercise 4 and replace the color palettes from RColorBrewer with ones from viridis.

`plot_bar` using "cividis"

```{r}

```

`plot_jitter` using "plasma"

```{r}

```

`plot_line` using "inferno"

```{r}

```

`plot_hex` using "viridis"

```{r}

```


# Feedback 

Please save the appropriate number to the variables below:

1. Approximately how long (in minutes) do you think it took you to complete this assignment?

```{r}
timeEstimate = 
```

2. How difficult or challenging did you find this assignment?

Extremely easy -------------------------------------- Extremely challenging 
                                                     (impossible to complete)
    1                                                           10
    
```{r}
challenge = 
```
    
    
3. How engaging or fun did you find this assignment?
  
Extremely Boring and Dry -------------------------------------- Extremely Engaging and Fun 
          1                                                                   10

```{r}
engagement = 
```

4. If you have any other feedback about this assignment, please provide it below.




