---
title: ""
author: ""
date: ""
output: html_document
---

```{r}
library(palmerpenguins)
library(RColorBrewer)
library(colorspace)
library(viridis)
library(tidyverse)
```

For these questions, you will use template graphs *similar* to those used in the Color Theory lecture. Fill in the blanks below to complete the code and create your template graphs. These should **NOT** be *IDENTICAL* to any graphs from the lecture. Make any other additional tweaks you want.

```{r}
plot_bar = penguins %>%
  ggplot(aes(y = bill_depth_mm, x = body_mass_g,
             fill = island)) +
  stat_summary(fun = "mean", geom = "bar") +
  scale_y_continuous(expand = c(0,0))
plot_bar

plot_jitter = penguins %>%
  ggplot(aes(y = flipper_length_mm, x = bill_length_mm)) +
  geom_jitter(height = 0, width = 0.2, 
              size = 2, alpha = 0.5,
              aes(color = island)) +
    stat_summary(fun.data = "mean_se",
               geom = "pointrange",
               size = 0.3)
plot_jitter

plot_line = penguins %>%
  ggplot(aes(y = bill_depth_mm, 
             x = flipper_length_mm,
             color = flipper_length_mm)) +
  stat_summary(fun = "mean", geom = "point", size = 2) +
  stat_summary(fun = "mean", geom = "line", size = 1)
plot_line

plot_hex2 = penguins %>%
  ggplot(aes(y = flipper_length_mm,
             x = bill_length_mm,
             z = bill_depth_mm)) +
  stat_summary_hex()
plot_hex2
```

1. Change the colors in `plot_bar` and `plot_jitter` to manually set values. Find a combination of colors you think work well together and are perceptually uniform.

```{r}
plot_bar + 
  scale_fill_manual(values = c("#FA003F", "#FFFF81", "skyblue"))

plot_jitter + 
  scale_color_manual(values = c("pink", "coral", "lightgreen"))
```

2. Using `plot_line` and/or `plot_hex`...

A. Create 2 *single hue* gradients that you think seem perceptually uniform using...

A light and dark purple:

```{r}
plot_hex2 + 
  scale_fill_gradient(low = "lavender", high = "purple")
```

A light and dark green:

```{r}
plot_line + 
  scale_color_gradient(low = "lightgreen", high = "darkgreen")
```


B. Create 2 *multiple hue* gradients (using either function to do so) that you think seem perceptually uniform using...

purple and yellow:

```{r}
plot_hex2 + 
  scale_fill_gradientn(colors = c("purple", "yellow"))
```

pink and green:

```{r}
plot_line + 
  scale_color_gradientn(colors = c("pink", "green"))
```


3. Create 2 visualizations using *divergent* scales that you think are equally uniform in both directions from the midpoint. Use `mean(penguins$X, na.rm = TRUE)` for the midpoint, replacing `x` with the appropriate variable from your graph.

red and blue:

```{r}
plot_line + 
  scale_color_gradient2(low = "red", mid = "green", high = "lightblue",
                       midpoint = mean(penguins$flipper_length_mm, na.rm = TRUE))
```

orange and yellow:

```{r}
plot_hex2 + 
  scale_fill_gradient2(low = "orange", mid = "grey90", high = "yellow",
                       midpoint = mean(penguins$flipper_length_mm, na.rm = TRUE))
```

4. Modify each of your template visualizations to use a different palette from RColorBrewer (hint: make sure you use the appropriate type of color scale given the type of data!).

`plot_bar` using "Set3"

```{r}
plot_bar + 
  scale_fill_brewer(palette = "Set3")
```

`plot_jitter` using "Pastel2"

```{r}
plot_jitter + 
  scale_color_brewer(palette = "Pastel2")
```

`plot_line` using "YlGn"

```{r}
plot_line + 
  scale_color_distiller(palette = "YlGn")
```

`plot_hex` using "GnBu"

```{r}
plot_hex + 
  scale_fill_distiller(palette = "GnBu")
```


5. Take your code from Exercise 4 and replace the color palettes from RColorBrewer with ones from viridis.

`plot_bar` using "cividis"

```{r}
plot_bar + 
  scale_fill_viridis(discrete = TRUE, option = "cividis")
```

`plot_jitter` using "plasma"

```{r}
plot_jitter + 
  scale_color_viridis(discrete = TRUE, option = "plasma")
```

`plot_line` using "inferno"

```{r}
plot_line + 
  scale_color_viridis(option = "inferno")
```

`plot_hex` using "viridis"

```{r}
plot_hex + 
  scale_fill_viridis(option = "viridis")
```


# Feedback 

Please save the appropriate number to the variables below:

1. Approximately how long (in minutes) do you think it took you to complete this assignment?

```{r}
timeEstimate = 
```

2. How difficult or challenging did you find this assignment?

Extremely easy -------------------------------------- Extremely challenging 
                                                     (impossible to complete)
    1                                                           10
    
```{r}
challenge = 
```
    
    
3. How engaging or fun did you find this assignment?
  
Extremely Boring and Dry -------------------------------------- Extremely Engaging and Fun 
          1                                                                   10

```{r}
engagement = 
```

4. If you have any other feedback about this assignment, please provide it below.




