---
title: ""
author: ""
date: ""
output: html_document
---

```{r}
library(tidyverse)
library(palmerpenguins)
```


1. Create your own graph using the `penguins` data and pick 2 of the following to put on your x and y axes: `bill_length_mm`, `bill_depth_mm`, `flipper_length_mm`, or `body_mass_g` (Note: This should *NOT* be code directly from the lecture or notes).

```{r}

```


2. Update your graph above by telling ggplot you want it to render a point for each observation in the penguins dataset. Describe the pattern/relationship you see under the code chunk.

```{r}

```

*Summary here*


3. Think about what patterns you notice in the visualization you created, and test whether `sex` or `species` might explain those patterns. Write a prediction before the code chunk, test that prediction, and then describe what you see.

*Prediction here*

```{r}

```

*Summary here*

4. Add in the line of best fit with `geom_smooth()`, making sure that your code produces a single line that is fit to ***all*** your data.

```{r}

```

5. Use R code to create or recreate the graphs below

A. Make a visualization to investigate the relationship between bill length (on the y-axis) and bill depth (on the x-axis)

```{r}

```

B. https://drive.google.com/uc?export=view&id=11Ig5Xq3z8CZwn0ElYmw4GNX0MK09Ja5E

```{r}

```

C. Make a visualization to investigate the relationship between body mass and flipper length. In doing so, make the geometric figure rendering the observations appear in blue. 
```{r}

```

D. https://drive.google.com/uc?export=view&id=1hcgTg902GsvRNS2SnZxiv-rtFXRpCiAR

```{r}

```

E. https://drive.google.com/uc?export=view&id=1RIuM6lRIoMdriUrtBySONizo22L9R_Xm

```{r}

```

6. 
Part 1: Take the code you produced for Exercise 4 and... 

1. Change the shape to be solid color squares with color mapped to the `species` variable. 

```{r}

```

2. Change the shape to be hollow squares with color mapped to the `species` variable. 

```{r}

```

3. Change the shape to be filled squares with color mapped to the `species` variable and fill set with a color of your choosing.

```{r}

```

Part 2: Use R code to recreate the graphs below

A. https://drive.google.com/uc?export=view&id=18OVNxbNI2MhaNTVO7W5FN_Yn-2hkxKgG

```{r}

```

B. https://drive.google.com/uc?export=view&id=1giVWU7yzuD5XND7LE_Ub88tKohtswbtk

```{r}

```

C. https://drive.google.com/uc?export=view&id=1QpR3ph7oCJiLJXRE_hio_agWOQwgNWNd

```{r}

```

*Bonus Challenge (ungraded):* See if you can think of a way to use what we demonstrated above to take your code from the Exercise 6, part 2, question 3, and give each observation a thicker outside border. The result should look like the graph below:

https://drive.google.com/uc?export=view&id=1N_9zRcePm8j1ffGGoZgJzUP6XbqisHIR

```{r}

```

7. Update the main graph you have been working with throughout the exercises to make the observations more translucent. First try doing so by mapping it to `island`. Then, create another graph where you set the alpha yourself. Try to pick the value you think makes the graph most legible and effective.

```{r}

```

Feedback 

Please save the appropriate number to the variables below:

1. Approximately how long (in minutes) do you think it took you to complete this assignment?

```{r}
timeEstimate = 
```

2. How difficult or challenging did you find this assignment?

Extremely easy -------------------------------------- Extremely challenging 
                                                     (impossible to complete)
    1                                                           10
    
```{r}
challenge = 
```
    
    
3. How engaging or fun did you find this assignment?
  
Extremely Boring and Dry -------------------------------------- Extremely Engaging and Fun 
          1                                                                   10

```{r}
engagement = 
```

4. If you have any other feedback about this assignment, please provide it below.




