# Intro to ggplot2

```{r}
library(tidyverse) # Load tidyverse
```

> "The greatest value of a picture is when it forces us to notice what we never expected to see."— John Tukey

>"There is no single statistical tool that is as powerful as a well‐chosen graph." (Chambers et al. 1983)

*Why Do We Care About Visualizing Our Data?*

The summary statistics of some variables and their linear relationships inherently overlook some aspects of the data. Visualizing your data is critically important.

The point of a visualization, just like a summary statistic, is to understand a relationship or pattern in your data. 

## When Visualizing Go Wrong

A bad visualization is often times worse than no visualization at all. 

It is not enough to just make *some* visualization, it is important to also consider the principles that make a ***GOOD*** visualization.

## ggplot2

`ggplot2` will be used to create visualizations. Graphs are constructed by mapping data to geometric objects (lines, bars, points, etc.) according to some aesthetic attributes (color, shape, size, etc.).

### Meet the Penguins

The `palmerpenguins` dataset will be used to create examples throughout. Contains measurements of things like bill length and depth, sex, etc., for penguins.

There are 3 different species of penguins in this dataset, collected from 3 islands in the Palmer Archipelago, Antarctica.

> Use `library()` to load in the `palmerpenguins` dataset

```{r}
install.packages("palmerpenguins")
library(tidyverse)
library(palmerpenguins)
```

## A Basic Graph

All ggplot graphs are build using the `ggplot()` call. The first thing it needs is some data.

> pipe in the `penguins` dataframe to `ggplot()`

```{r}
ggplot(penguins)
```

> ""

ggplot needs to be told what variables from your data should be *map*ped to the *aes*thetics you want to render on your graph. You will do that with `aes()`.

> Fill in the code below to examine how a penguin's `bill_length_mm` is related to its `flipper_length_mm`. 

```{r}
penguins %>%
  ggplot(mapping = aes(y = bill_length_mm,
                       x = flipper_length_mm))
```

> ""

You want ggplot to use those mappings to construct some **geom**etric object, and the way you do that is by adding a *geom*. 

Geoms have the general syntax of `geom_X()`, where X usually refers to the specific geometric object you want to render. Here, you want a point on the graph for each penguin, so `geom_point()` will be used.

> Replace the X in the code below to to put a point for each observation on the graph

```{r}
penguins %>%
  ggplot(mapping = aes(y = flipper_length_mm,
                       x = bill_length_mm)) +
  geom_point()
```

> ""

There are two important things to note here:

1. The `+` was used instead of `%>%` to add on a new function. The ggplot system is additive/layered, `geom_point()` was being added to the code.

2. The following showed up in the console: 

**Warning message: Removed 2 rows containing missing values (geom_point).**

Looking at your warnings and errors is always important, but especially so when creating visualizations! This says that it removed 2 rows of data.

For every visualization you create, make a verbal description of the pattern seen underneath.


# Aesthetics

## Color

One way the penguins seem to be grouped is with a cluster at the top and another at the bottom. Maybe this corresponds to the `sex` variable?

To explore this idea: visually indicate which observations were from which sex.

Prior to running code -- declare formal predictions by stating two mutually exclusive alternatives that you *could* observe:

--
prediction here
There will be no correlation between penguin sex and penguin physical features.
There will be a correlation between penguin sex and penguin physical features.
--

> Replace the X's in the code below to have map `color` to `sex`

```{r}
penguins %>%
  ggplot(mapping = aes(y = flipper_length_mm,
                       x = bill_length_mm),
                color = sex) +
  geom_point()

penguins %>%
  ggplot(mapping = aes(y = flipper_length_mm,
                       x = bill_length_mm,
                       color = sex)) +
  geom_point()
#this code is correct because color = sex is included in the yellow parentheses of the aes() function!
```

> ""

It actually kind of looks like there are 3 distinct clusters, not 2. Maybe this corresponds to the `species` variable?

Predictions:

--
prediction here
There is no correlation between penguin species and penguin physical features.
There is a correlation between penguin species and penguin physical features.
--

> Replace the X's in the code below to have map `color` to `species`

```{r}
penguins %>%
  ggplot(mapping = aes(y = flipper_length_mm,
                       x = bill_length_mm,
                       color = species)) +
  geom_point()
```

> ""

Summary:

--
Summary here
There appears to be a correlation between penguin species and penguin physical features according to the current data. This correlation is observable in the way that the data points, when distinguished by species type, creates three distinct colored clusters on the scatter plot.
--


Visualizing your data in ways like this allow you to quickly get insights into different questions you may want to use your data to answer.

### Global vs Local Aesthetics

It can be helpful to add the line of best fit to see linear relationships using `geom_smooth()`.

> Replace the X's in the code below to show the line of best fit

```{r}
penguins %>%
  ggplot(mapping = aes(y = flipper_length_mm,
                       x = bill_length_mm,
                       color = species)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```

>""

**global** aesthetic -- put in the `ggplot()` call and applies to ALL parts of your graph 
**local** aesthetic -- put in individual geoms and applies ONLY to those individual ones

> Correct the code above so that only the points are mapped to `species`.

```{r}
penguins %>%
  ggplot(aes(y = flipper_length_mm,
             x = bill_length_mm)) +
  geom_point(aes(color = species)) +
  geom_smooth(method = "lm", se = FALSE)
```

### Setting vs Mapping Aesthetics

What if you just want to set the value of something yourself? 

Look at the example below that changes all the points to orange (so they have a good contrast with the line).

```{r}
penguins %>%
  ggplot(aes(y = flipper_length_mm,
             x = bill_length_mm)) +
  geom_point(color = orange) +
  geom_smooth(method = "lm", se = FALSE)
```

By writing `orange` like this, R thinks it is a variable in the `penguins` dataset that was piped in to ggplot! Instead just use quotes.

> Replace the X in the code below to color all the points with the color "orange"

```{r}
penguins %>%
  ggplot(aes(y = flipper_length_mm,
             x = bill_length_mm)) +
  geom_point(color = "orange") +
  geom_smooth(method = "lm", se = FALSE)
```

This can be done for any geom.

> Modify the code below to change the color of the smoothing line:

```{r}
penguins %>%
  ggplot(aes(y = flipper_length_mm,
             x = bill_length_mm)) +
  geom_point(color = "orange") +
  geom_smooth(method = "lm", se = FALSE, color = "pink")
```

**Note: Aesthetic settings can only be set locally, not globally. Aesthetic mappings can be local OR global.**

```{r}
penguins %>%
  ggplot(aes(y = flipper_length_mm,
             x = bill_length_mm,
         color = "orange")) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```

### Setting Colors

When setting a color, this can be done by name, as was done above, or by hexcode:

```{r}
penguins %>%
  ggplot(aes(y = flipper_length_mm,
             x = bill_length_mm)) +
  geom_point(color = "#9FE2BF") +
  geom_smooth(method = "lm", se = FALSE, color = "#FFBF00")
```

Can also set your colors based on some logical operation:

```{r}
penguins %>%
  ggplot(aes(y = flipper_length_mm,
             x = bill_length_mm)) +
  geom_point(aes(color = flipper_length_mm > 200)) +
  geom_smooth(method = "lm", se = FALSE, color = "#FFBF00")
```

## Shape

### Mapping

Shape is another aesthetic that can be changed.

> Replace the X's below to map the point shape to `species` in addition to point color

```{r}
penguins %>%
  ggplot(aes(y = flipper_length_mm,
             x = bill_length_mm)) +
  geom_point(aes(color = species,
                 shape = species)) +
  geom_smooth(method = "lm", se = FALSE)
```

>""

> Replace the X's below to map shape to `island` instead:

```{r}
penguins %>%
  ggplot(aes(y = flipper_length_mm,
             x = bill_length_mm)) +
  geom_point(aes(color = species,
                 shape = island)) +
  geom_smooth(method = "lm", se = FALSE)
```

Mapping variables to different aesthetics visualizes even more data and patterns, but can quickly become overwhelming and difficult to interpret.

### Setting

Can select shapes by number or by name.

There appears to be 3 different kinds of triangles. Compare their differences below:

* 17 or 'triangle'

> Replace the X's below to map shape to the triangle 17 using number or name
    
```{r}
penguins %>%
  ggplot(aes(y = flipper_length_mm,
             x = bill_length_mm)) +
  geom_point(aes(color = species),
             shape = 17) +
  geom_smooth(method = "lm", se = FALSE)

```


* 2 or 'triangle open'

> Replace the X's below to map shape to the triangle 2 using number or name
    
```{r}
penguins %>%
  ggplot(aes(y = flipper_length_mm,
             x = bill_length_mm)) +
  geom_point(aes(color = species),
             shape = 2) +
  geom_smooth(method = "lm", se = FALSE)
```


* 24 or 'triangle filled'

> Replace the X's below to map shape to the triangle 24 using number or name
    
```{r}
penguins %>%
  ggplot(aes(y = flipper_length_mm,
             x = bill_length_mm)) +
  geom_point(aes(color = species),
             shape = 24,
             fill = "darkgrey") +
  geom_smooth(method = "lm", se = FALSE)
```

```{r}

```

Some geoms have a 'color' argument, some have a 'fill' argument, some have both:

'color' = outline/outside
'fill' = the fill / inside

## Size

### Mapping

Size is another aesthetic that can be set.

> Replace the X's below to map `species` to `color`, `shape`, and `size`.

```{r}
penguins %>%
  ggplot(aes(y = flipper_length_mm,
             x = bill_length_mm)) +
  geom_point(aes(color = species,
                 shape = species,
                 size = species)) +
  geom_smooth(method = "lm", se = FALSE)
```

>""

This does is demonstrate what is meant by saying, **"ggplot is additive/layered"**. The last geom added is added *on top* of the graph rendered by the previous code.

> Try adding the geoms in a different order and see what happens

```{r}
penguins %>%
  ggplot(aes(y = flipper_length_mm,
             x = bill_length_mm)) +
  geom_smooth(method = "lm", se = FALSE) +
  geom_point(aes(color = species,
                 shape = species,
                 size = species))
#notice that the shapes are now above the best fit line. order is important!
```

This concept is very important to keep in mind when creating your visualizations. **Order matters!**

### Setting

Instead of mapping to a variable, can be set manually:

For example, you could take one of the graphs from above and make the shapes a little bit larger.

> Modify the code below to make the points size 4

```{r}
penguins %>%
  ggplot(aes(y = flipper_length_mm,
             x = bill_length_mm)) +
  geom_point(aes(color = species),
             shape = 24,
             fill = 'darkgrey',
             size = 4) +
  geom_smooth(method = "lm", se = FALSE)
```


## Alpha

### Mapping

The alpha aesthetic changes how translucent vs opaque something is.

> Replace the X's below to map `alpha` to `species`

```{r}
penguins %>%
  ggplot(aes(y = flipper_length_mm,
             x = bill_length_mm)) +
  geom_point(aes(color = species,
                 shape = species,
                 size = species,
                 alpha = species)) +
  geom_smooth(method = "lm", se = FALSE)
```

>""

### Setting

Alpha values range from 0-1, with 0 being completely transparent and 1 being completely opaque.

> In the graphs below, compare a high and low alpha value:

```{r}
penguins %>%
  ggplot(aes(y = flipper_length_mm,
             x = bill_length_mm)) +
  geom_point(aes(color = species,
                 shape = species),
             size = 3,
             alpha = 1) +
  geom_smooth(method = "lm", se = FALSE)
```


```{r}
penguins %>%
  ggplot(aes(y = flipper_length_mm,
             x = bill_length_mm)) +
  geom_point(aes(color = species,
                 shape = species),
             size = 3,
             alpha = 0.3) +
  geom_smooth(method = "lm", se = FALSE)
```

Even with a very low alpha, you can see just how many observations are overlapping.

## References:

Good color guides:

* http://sape.inf.usi.ch/quick-reference/ggplot2/colour

* http://www.cookbook-r.com/Graphs/Colors_(ggplot2)/#hexadecimal-color-code-chart
