---
title: "Customization Practice Problem Set"
author: ""
date: ""
output: html_document
---

```{r}
library(tidyverse)
library(patchwork)
# Modify the file path in the code below to properly load the "diamonds_sample.RData" file
load("/Users/miramateo/Desktop/GitHub/R Bootcamp/ggplot expanded - 2/Color Theory") 
```

You are going to continue working with the `diamonds_sample` dataset.

`diamonds_sample` contains the following variables: 

* `price` - price in USD
* `carat` - weight of the diamond
* `cut` - quality of the cut
* `color` - diamond color
* `clarity` - a measurement of how clear the diamond is
* `x` - length in mm
* `y` - width in mm
* `z` - depth in mm
* `depth` - total depth percentage
* `table` - width of top of diamond relative to widest point


1. Use the `diamonds_sample` dataframe and create your own `base_graph`. Make sure to have a continuous variable on the y-axis and a categorical variable on the x-axis.

```{r}
base_graph <- diamonds %>%
  ggplot(aes(y = price, x = carat)) + 
  geom_point()

base_graph
```

2. Take your code from #1 and add on code that will modify your `base_graph` so the scale is more appropriate and represents the full range.

```{r}
base_graph + 
  scale_y_continuous(breaks = seq(from = 0, to = 30000, by = 5000),
                     labels = seq(from = 0, to = 30000, by = 5000)) + 
  coord_cartesian(ylim = c(0, 20000))
```

3. Take your code from #2 and add on code that will modify your `base_graph` so the padding is gone.

```{r}
base_graph + 
  scale_y_continuous(breaks = seq(from = 0, to = 30000, by = 5000),
                     labels = seq(from = 0, to = 30000, by = 5000),
                     expand = c(0, 0)) + 
  coord_cartesian(ylim = c(0, 20000))
```

4. Take your code from #3 and add on code that will modify your `base_graph` so that it has more appropriate titles for the y- and x-axis. Additionally, add an appropriate title, subtitle (if needed), figure tag, and caption.

```{r}
base_graph + 
  scale_y_continuous(breaks = seq(from = 0, to = 30000, by = 5000),
                     labels = seq(from = 0, to = 30000, by = 5000),
                     expand = c(0, 0)) + 
  coord_cartesian(ylim = c(0, 20000)) + 
  labs(title = "How Does Carat Amount Affect Diamond Price?",
       subtitle = "Quality Assessed by Master Geologist",
       y = "Carat Number",
       x = "Diamond Price in USD",
       tag = "A",
       caption = "Note: This is a single sample of diamonds. Price may vary by store.")
```

5. Create a new variable called `modified_graph` that takes your `base_graph` and saves all modifications you've added in questions 2:4. Then, try applying some different themes to your `modified_graph`.

```{r}
modified_graph <- base_graph + 
  scale_y_continuous(breaks = seq(from = 0, to = 30000, by = 5000),
                     labels = seq(from = 0, to = 30000, by = 5000),
                     expand = c(0, 0)) + 
  coord_cartesian(ylim = c(0, 20000)) + 
  labs(title = "How Does Carat Amount Affect Diamond Price?",
       subtitle = "Quality Assessed by Master Geologist",
       y = "Carat Number",
       x = "Diamond Price in USD",
       tag = "A",
       caption = "Note: This is a single sample of diamonds. Price may vary by store.")

#modified_graph + theme_classic()
#modified_graph + theme_bw()
modified_graph + theme_minimal()
```

6. Add some code to `modified_graph` to modify your visualization's titles and increase their legibility.

```{r}
modified_graph + 
  theme(plot.title = element_text(size = 20,
                                  face = "bold",
                                  hjust = 0.5),
        plot.subtitle = element_text(size = 15,
                                     face = "italic",
                                     color = "dimgray",
                                     hjust = 0.5),
        axis.title = element_text(size = 12),
        plot.tag = element_text(face = "bold"),
        plot.caption = element_text(face = "italic"))
```

7. Take your code from #6 and add on code that will modify your visualization's caption and increase its legibility.

```{r}
modified_graph + 
  theme(plot.title = element_text(size = 20,
                                  face = "bold",
                                  hjust = 0.5),
        plot.subtitle = element_text(size = 15,
                                     face = "italic",
                                     color = "dimgray",
                                     hjust = 0.5),
        axis.title = element_text(size = 12),
        plot.tag = element_text(face = "bold"),
        plot.caption = element_text(face = "italic",
                                    size = 10))
```

8. Take your code from #7 and add on code that will modify your visualization's axes titles and increase their legibility.

```{r}
modified_graph + 
  theme(plot.title = element_text(size = 20,
                                  face = "bold",
                                  hjust = 0.5),
        plot.subtitle = element_text(size = 15,
                                     face = "italic",
                                     color = "dimgray",
                                     hjust = 0.5),
        axis.title = element_text(size = 12,
                                  face = "bold"),
        plot.tag = element_text(face = "bold"),
        plot.caption = element_text(face = "italic",
                                    size = 10))
```

9. Take your code from #8 and add on code that will modify your visualization's axes values and increase their legibility.

```{r}
modified_graph + 
  theme(plot.title = element_text(size = 20,
                                  face = "bold",
                                  hjust = 0.5),
        plot.subtitle = element_text(size = 15,
                                     face = "italic",
                                     color = "dimgray",
                                     hjust = 0.5),
        axis.title = element_text(size = 12,
                                  face = "bold"),
        axis.text = element_text(color = "dimgray"),
        plot.tag = element_text(face = "bold"),
        plot.caption = element_text(face = "italic",
                                    size = 10))
```

10. Create a new variable called `a` that takes your `modified_graph` and saves all the new modifications you've added in questions 6:9.

```{r}
a <- modified_graph + 
  theme(plot.title = element_text(size = 20,
                                  face = "bold",
                                  hjust = 0.5),
        plot.subtitle = element_text(size = 15,
                                     face = "italic",
                                     color = "dimgray",
                                     hjust = 0.5),
        axis.title = element_text(size = 12,
                                  face = "bold"),
        axis.text = element_text(color = "dimgray"),
        plot.tag = element_text(face = "bold"),
        plot.caption = element_text(face = "italic",
                                    size = 10))

a
```


11. Take the code from questions 3, 11, 21, and 23, on your "geoms_practice" assignment, change any instances of `price` to `log10(price)`, and make any other aesthetic modifications that you think help improve the legibility or effectiveness of the graph. 

Then, repeat steps similar to those for 1:9 above to customize these visualizations. Save these new visualizations to `b`, `c`, `d`, and `e`, and call each variable to create/print the new graphs.

  B. 
  
```{r}
b <- diamonds %>%
  ggplot(aes(x = log10(price))) + 
  geom_histogram(color = "white",
           fill = "skyblue") + 
  theme_classic() +
  labs(title = "How Do Diamond Prices Compare?",
       subtitle = "Graphed By An Aspiring Data Scientist",
       y = "Number of Diamonds",
       x = "Log10 Price in USD",
       tag = "B") + 
  theme(plot.title = element_text(size = 15,
                                  face = "bold"),
        plot.subtitle = element_text(size = 12,
                                     face = "italic",
                                     color = "dimgray"))

b
```

  C.
  
```{r}
c <- diamonds %>%
  ggplot(aes(y = depth, x = clarity)) + 
  geom_boxplot(color = "salmon", 
               fill = "sienna") + 
  theme_bw() + 
  labs(title = "How Does Diamond Clarity Affect Diamond Depth?",
       subtitle = "Graphed By An Aspiring Data Scientist",
       y = "Depth",
       x = "Clarity",
       tag = "C") + 
  theme(plot.title = element_text(size = 15,
                                  face = "bold",
                                  hjust = 0.5),
        plot.subtitle = element_text(size = 12,
                                     face = "italic",
                                     color = "dimgray",
                                     hjust = 0.5),
        axis.title = element_text(face = "bold"))

c
```

  D.

```{r}
d <- diamonds %>%
  ggplot(aes(x = cut,
             y = clarity,
             z = price)) +
  stat_summary_2d(fun = "mean", geom = "tile") + 
  theme_minimal() + 
  labs(title = "How Does Diamond Cut Affect Clarity?",
       subtitle = "An In-depth Analysis",
       y = "Clarity",
       x = "Cut") + 
  theme(plot.title = element_text(size = 20,
                                  face = "bold",
                                  hjust = 0.5),
        plot.subtitle = element_text(size = 12,
                                     face = "italic",
                                     color = "dimgrey",
                                     hjust = 0.5),
        axis.title = element_text(color = "dimgray",
                                  face = "bold"),
        axis.line = element_line(color = "black"),
        axis.ticks = element_line(color = "black",
                                  size = 0.6))

d
```

  E.

```{r}
e <- diamonds %>%
  ggplot(aes(x = table,
             y = carat,
             z = log10(price))) +
  geom_raster() + 
  stat_summary_2d(fun = "mean", geom = "tile", color = "white") + 
  theme_bw() + 
  labs(title = "How Does Diamond Table Affect Carat and Price?",
       subtitle = "A Comprehensive Study",
       y = "Carat Number",
       x = "Table Measurement") + 
  theme(plot.title = element_text(size = 18,
                                  hjust = 0.5,
                                  face = "bold"),
        plot.subtitle = element_text(size = 12,
                                     hjust = 0.5,
                                     face = "italic",
                                     color = "blue"),
        axis.title = element_text(color = "darkblue",
                                  face = "bold"),
        axis.line = element_line(color = "black"),
        axis.ticks = element_line(color = "black",
                                  size = 0.4),
        legend.title = element_text(size = 11, 
                                    face = "bold"),
        legend.key = element_rect(fill = "white", colour = "black"))

e
```


12. Use `patchwork` to create plots with the following layouts:


  A. 
  
|----|
| d  |
|----|
| c  |
|----|

```{r}
d / c
```

  B. 

|----|----|
| b  |  e |
|----|----|


```{r}
b | e
```


  C. 

|----|----|
| a  |  b |
|----|----|
| c  |  d |
|----|----|

```{r}
(a | b) / (c | d)
```

  D. 

|----|----|
|    e    |
|----|----|
| c  |  d |
|----|----|

```{r}
e / (c | d)
```

  E.
  
|----|----|
| a  |    |
|----|  c |
| b  |    |
|----|----|

```{r}
(a / b) | c
```

  F. 
  
|----|----|
| e  |  a |
|----|----|
|    b    |
|----|----|

```{r}
(e | a) / b
```

  G.

|----|----|
|    |  e |
| d  |----|
|    |  b |
|----|----|

```{r}
d | (e / b)
```


# Feedback

Please save the appropriate number to the variables below:

1. Approximately how long (in minutes) do you think it took you to complete this assignment?

```{r}
timeEstimate = 
```

2. How difficult or challenging did you find this assignment?

Extremely easy -------------------------------------- Extremely challenging 
                                                     (impossible to complete)
    1                                                           10
    
```{r}
challenge = 
```
    
    
3. How engaging or fun did you find this assignment?
  
Extremely Boring and Dry -------------------------------------- Extremely Engaging and Fun 
          1                                                                   10

```{r}
engagement = 
```

4. If you have any other feedback about this assignment, please provide it below.




