---
title: "Customization Practice Problem Set"
author: ""
date: ""
output: html_document
---

```{r}
library(tidyverse)
library(patchwork)
# Modify the file path in the code below to properly load the "diamonds_sample.RData" file
load("diamonds_sample.RData") 
```

You are going to continue working with the `diamonds_sample` dataset.

`diamonds_sample` contains the following variables: 

* `price` - price in USD
* `carat` - weight of the diamond
* `cut` - quality of the cut
* `color` - diamond color
* `clarity` - a measurement of how clear the diamond is
* `x` - length in mm
* `y` - width in mm
* `z` - depth in mm
* `depth` - total depth percentage
* `table` - width of top of diamond relative to widest point


1. Use the `diamonds_sample` dataframe and create your own `base_graph`. Make sure to have a continuous variable on the y-axis and a categorical variable on the x-axis.

```{r}

```

2. Take your code from #1 and add on code that will modify your `base_graph` so the scale is more appropriate and represents the full range.

```{r}

```

3. Take your code from #2 and add on code that will modify your `base_graph` so the padding is gone.

```{r}

```

4. Take your code from #3 and add on code that will modify your `base_graph` so that it has more appropriate titles for the y- and x-axis. Additionally, add an appropriate title, subtitle (if needed), figure tag, and caption.

```{r}

```

5. Create a new variable called `modified_graph` that takes your `base_graph` and saves all modifications you've added in questions 2:4. Then, try applying some different themes to your `modified_graph`.

```{r}

```

6. Add some code to `modified_graph` to modify your visualization's titles and increase their legibility.

```{r}

```

7. Take your code from #6 and add on code that will modify your visualization's caption and increase its legibility.

```{r}

```

8. Take your code from #7 and add on code that will modify your visualization's axes titles and increase their legibility.

```{r}

```

9. Take your code from #8 and add on code that will modify your visualization's axes values and increase their legibility.

```{r}

```

10. Create a new variable called `a` that takes your `modified_graph` and saves all the new modifications you've added in questions 6:9.

```{r}

```


11. Take the code from questions 3, 11, 21, and 23, on your "geoms_practice" assignment, change any instances of `price` to `log10(price)`, and make any other aesthetic modifications that you think help improve the legibility or effectiveness of the graph. 

Then, repeat steps similar to those for 1:9 above to customize these visualizations. Save these new visualizations to `b`, `c`, `d`, and `e`, and call each variable to create/print the new graphs.

  B. 
  
```{r}

```

  C.
  
```{r}

```

  D.

```{r}

```

  E.

```{r}

```


12. Use `patchwork` to create plots with the following layouts:


  A. 
  
|----|
| d  |
|----|
| c  |
|----|

```{r}

```

  B. 

|----|----|
| b  |  e |
|----|----|


```{r}

```


  C. 

|----|----|
| a  |  b |
|----|----|
| c  |  d |
|----|----|

```{r}

```

  D. 

|----|----|
|    e    |
|----|----|
| c  |  d |
|----|----|

```{r}

```

  E.
  
|----|----|
| a  |    |
|----|  c |
| b  |    |
|----|----|

```{r}

```

  F. 
  
|----|----|
| e  |  a |
|----|----|
|    b    |
|----|----|

```{r}

```

  G.

|----|----|
|    |  e |
| d  |----|
|    |  b |
|----|----|

```{r}

```


# Feedback

Please save the appropriate number to the variables below:

1. Approximately how long (in minutes) do you think it took you to complete this assignment?

```{r}
timeEstimate = 
```

2. How difficult or challenging did you find this assignment?

Extremely easy -------------------------------------- Extremely challenging 
                                                     (impossible to complete)
    1                                                           10
    
```{r}
challenge = 
```
    
    
3. How engaging or fun did you find this assignment?
  
Extremely Boring and Dry -------------------------------------- Extremely Engaging and Fun 
          1                                                                   10

```{r}
engagement = 
```

4. If you have any other feedback about this assignment, please provide it below.




