# Customization

```{r}
library(tidyverse)
library(palmerpenguins) 
```

The following will serve as a base plot to customize:

```{r}
base_plot <- penguins %>%
  ggplot(aes(y = body_mass_g, x = island)) +
  geom_jitter(height = 0, width = 0.1, 
              size = 2, alpha = 0.3,
              aes(color=island)) +
    stat_summary(fun.data = "mean_se",
               geom = "pointrange",
               color = "black",
               aes(fill = island),
               shape = 21,
               size = 0.5)

base_plot
```


## Scaling The Axes

The axes can be changed using a `scale_*_*` function. 

1st `*` = which axis to modify
2nd `*` = the type of data or scale you want it to have. 

> Replace the X's below to change the axis to run from 0 to 7000 in increments of 500

```{r}
base_plot +
  scale_y_continuous(breaks = seq(from = 0, to = 7000, by = 500),
                     labels = seq(from = 0, to = 7000, by = 500))
```

Graphs are plotted with (x,y) *cartesian* *coord*inates. Modify the limits of that coordinate system with `coord_cartesian()`

> Replace the `_` in the code below change the y-axis to run from 0-7000 and add your completed `scale_y_continuous()` code from above.

```{r}
base_plot +
  coord_cartesian(ylim = c(0,7000)) + 
  scale_y_continuous(breaks = seq(from = 0, to = 7000, by = 500),
                     labels = seq(from = 0, to = 7000, by = 500))
```


### Get Rid Of Padding

Eliminated with the `expand` argument.

> Take your code from above and add an `expand()` argument to the `scale_y_continuous` to eliminate the padding.

```{r}
base_plot +
  coord_cartesian(ylim = c(0,7000)) + 
  scale_y_continuous(breaks = seq(from = 0, to = 7000, by = 500),
                     labels = seq(from = 0, to = 7000, by = 500),
                     expand = c(0,0))
```

## Titles, Captions, and Labels, Oh My!

Uses `labs()`

> Add your code from above and replace the X's below with appropriate titles and captions

```{r}
base_plot +
  coord_cartesian(ylim = c(0,7000)) + 
  scale_y_continuous(breaks = seq(from = 0, to = 7000, by = 500),
                     labels = seq(from = 0, to = 7000, by = 500),
                     expand = c(0,0)) +
  labs(title = "How Does Penguin Weight Vary Across Islands?",
       subtitle = "Islands Contain Different Penguin Species",
       y = "Body Mass (grams)",
       x = "Island",
       tag = "Figure 1",
       caption = "Note: Error bars represent +/- 1 SEM")
```

## Themes

First, save all updates made so far to a new variable.

```{r}
modified_plot <- base_plot +
  coord_cartesian(ylim = c(0,7000)) + 
  scale_y_continuous(breaks = seq(from = 0, to = 7000, by = 500),
                     labels = seq(from = 0, to = 7000, by = 500),
                     expand = c(0,0)) +
  labs(title = "How Does Penguin Weight Vary Across Islands?",
       subtitle = "Islands Contain Different Penguin Species",
       y = "Body Mass (grams)",
       x = "Island",
       tag = "Figure 1",
       caption = "Note: Error bars represent +/- 1 SEM")
```

Most common preset themes: `theme_minimal()`, `theme_bw()`, and `theme_classic()`.

> Add each of the 3 themes listed above to `modified_plot` and observe the differences:

```{r}
modified_plot + theme_minimal()


modified_plot + theme_bw()


modified_plot + theme_classic()
```


To make manual changes to the theme's settings, you use the `theme()` function. 

`theme(item-to-modify = element_type-of-element(modification code here))`

For example:

`theme(plot.title = element_text(size = 18))`



### Titles

> Replace the X's in the code below increase font size and make text more legible for the titles and tag, specifically making the subtitle less prominent.

```{r}
modified_plot = modified_plot +
  theme_classic() +
  theme(plot.title = element_text(size = 18),
        plot.subtitle = element_text(size = 10, 
                                     color = "grey50",
                                     face = "bold"),
        plot.tag = element_text(face = "bold"))

modified_plot
```

To change the location of the text, ad*just* its *v*ertical or *h*orizontal location using `vjust` or `hjust`. 

When adjusting:
* 0 == left-aligned
* 0.5 == centered
* 1 == right-aligned

> Copy/paste your code from above and add adjustments to center the title and subtitle. When your code looks good, update `modified_plot` by saving over it.

```{r}
modified_plot = modified_plot +
  theme_classic() +
  theme(plot.title = element_text(size = 18, 
                                  hjust = 0.5, 
                                  face = "bold"),
        plot.subtitle = element_text(size = 10, 
                                     color = "grey50",
                                     hjust = 0.5,
                                     face = "bold"),
        plot.tag = element_text(face = "bold"))

modified_plot

```

### Captions

> Left align the caption and make it italicized. When it works as intended, update `modified_plot`

```{r}
modified_plot +
  theme(plot.caption = element_text(hjust = 0,
                                    face = 'italic'))
```


### Axes Titles

Change simultaneously (e.g., using `axis.title`) or individually (e.g., using `axis.title.x` and `axis.title.y`).

> Increase the axis titles size and make them bold.

```{r}
modified_plot +
  theme(axis.title.x = element_text(size = 14,
                                    face = "bold"),
        axis.title.y = element_text(size = 14,
                                    face = "bold"))
```

Lack of space causes TRouBLe. Modify the text's margins -- the area to the *t*op, *r*ight, *b*ottom, and *l*eft of it.

> Replace the X's in the code below to increase the appropriate margins to improve legibility. Once it looks good, update `modified_plot`

```{r}
modified_plot = modified_plot +
  theme(plot.subtitle = element_text(size = 10, 
                                     color = "grey50",
                                     hjust = 0.5,
                                     margin = margin(b = 0.2, 
                                                     unit = "inch")),
        axis.title.x = element_text(size = 16,
                                    face = "bold",
                                    margin = margin(t = 0.2, 
                                                    unit = "inch")),
        axis.title.y = element_text(size = 16,
                                    face = "bold",
                                    margin = margin(r = 0.2, 
                                                    unit = "inch")))

modified_plot
```


### Axes Values

> Replace the X's in the code below, try different values. Once it looks good, update `modified_plot`

```{r}
modified_plot = modified_plot +
  theme(axis.line.x = element_line(color = "gray40", size = 0.5),
        axis.ticks = element_line(color = "gray40", size = 0.5),
        axis.text = element_text(face = "bold",
                                 color = "black",
                                 size = 12))

modified_plot
```

### Setting a Default

Below is all the customization code generated thus far:

```{r}
theme(plot.title = element_text(size = 18,
                                face = "bold",
                                hjust = 0.5),
      plot.subtitle = element_text(size = 10, 
                                   color = "grey50",
                                   face = "bold",
                                   hjust = 0.5,
                                   margin = margin(b = 0.2, 
                                                   unit = "inch")),
      plot.tag = element_text(face = "bold"),
      plot.caption = element_text(hjust = 0,
                                  face = 'italic'),
      axis.title.x = element_text(size = 16,
                                  face = "bold",
                                  margin = margin(t = 0.2, 
                                                  unit = "inch")),
      axis.title.y = element_text(size = 16,
                                  face = "bold",
                                  margin = margin(r = 0.2, 
                                                  unit = "inch")),
      axis.line.x = element_line(color = "gray40", size = 0.5),
      axis.ticks = element_line(color = "gray40", size = 0.5),
      axis.text = element_text(face = "bold",
                               color = "black",
                               size = 12))
```

Use `theme_set()` to set a default applied to all visualizations you make with ggplot.

```{r}
theme_set(theme_classic() + 
            theme(plot.title = element_text(size = 18,
                                face = "bold",
                                hjust = 0.5),
      plot.subtitle = element_text(size = 10, 
                                   color = "grey50",
                                   face = "bold",
                                   hjust = 0.5,
                                   margin = margin(b = 0.2, 
                                                   unit = "inch")),
      plot.tag = element_text(face = "bold"),
      plot.caption = element_text(hjust = 0,
                                  face = 'italic'),
      axis.title.x = element_text(size = 16,
                                  face = "bold",
                                  margin = margin(t = 0.2, 
                                                  unit = "inch")),
      axis.title.y = element_text(size = 16,
                                  face = "bold",
                                  margin = margin(r = 0.2, 
                                                  unit = "inch")),
      axis.line.x = element_line(color = "gray40", size = 0.5),
      axis.ticks = element_line(color = "gray40", size = 0.5),
      axis.text = element_text(face = "bold",
                               color = "black",
                               size = 12)))
```

> Try making a new visualization to see the results:

```{r}
penguins %>%
  ggplot(aes(y = body_mass_g, x = island)) +
  geom_violin(aes(fill = island),
              alpha = 0.2) +
  geom_jitter(alpha = 0.4, width = 0.05) +
  stat_summary(fun.data = "mean_se",
               geom = "pointrange",
               aes(color = island),
               size = 0.5)
```

### Legends

To get rid of a legend altogether:

```{r}
modified_plot +
  theme(legend.position = "none")
```

Below has the relevant code for the legend:

```{r}
theme(legend.box.background = element_rect(color = "black", # Add a defined box around legend
                                           size = 2),
      legend.title = element_text(face = "bold"), # Modify the title
      legend.text = element_text(face = "bold"), # Modify text
      legend.title.align = 0.5, # Change alignment of legend title. Think of this like an hjust.
      legend.key = element_rect(fill = "white", colour = "black") # Add defined boxes around legend key graphic
) 
```

> Modify the legend from `modified_plot` using the code examples above

```{r}
penguins %>%
  drop_na() %>%
    ggplot(aes(y = body_mass_g, x = island)) +
    geom_point(size = 2, alpha = 0.3,
               shape = 21,
                aes(fill = sex),
                position = position_jitterdodge()) +
    stat_summary(fun.data = "mean_se",
                 geom = "pointrange",
                 color = "black",
                 aes(fill = sex),
                 shape = 21,
                 size = 0.5,
                 position = position_dodge(width = 0.75)) +  
  coord_cartesian(ylim = c(0,7000)) + 
  scale_y_continuous(breaks = seq(from = 0, to = 7000, by = 500),
                     labels = seq(from = 0, to = 7000, by = 500),
                     expand = c(0,0)) +
  labs(title = "How Does Penguin Weight Vary Across Islands?",
       subtitle = "Islands Contain Different Penguin Species",
       y = "Body Mass (grams)",
       x = "Island",
       tag = "Figure 1",
       caption = "Note: Error bars represent +/- 1 SEM",
        # New code starts here:
       fill = "Sex" # Change Legend label with the name of the mapped aesthetic.
       ) +
  theme(legend.box.background = element_rect(color = "black", # Add a defined box around legend
                                             size = 2),
        legend.title = element_text(face = "bold"), # Modify the title
        legend.text = element_text(face = "bold"), # Modify text
        legend.title.align = 0.5, # Change alignment of legend title. Think of this like an hjust.
        legend.key = element_rect(fill = "white", colour = "black") # Add defined boxes around legend key graphic
        ) 
```


## Combining Graphs

`patchwork` -- combine and arrange multiple graphs into a single figure

```{r}
library(patchwork)
```

Take the following 3 graphs for example:

```{r}
a = penguins %>%
  ggplot(aes(y = body_mass_g, x = island)) +
  geom_jitter(height = 0, width = 0.1, 
              size = 2, alpha = 0.3,
              aes(color=island)) +
    stat_summary(fun.data = "mean_se",
               geom = "pointrange",
               color = "black",
               aes(fill = island),
               shape = 21,
               size = 0.5)
a
b = penguins %>%
  ggplot(aes(y = body_mass_g, x = species)) +
  geom_jitter(height = 0, width = 0.1, 
              size = 2, alpha = 0.3,
              aes(color=species)) +
    stat_summary(fun.data = "mean_se",
               geom = "pointrange",
               color = "black",
               aes(fill = species),
               shape = 21,
               size = 0.5)
b
c = penguins %>%
  drop_na() %>%
    ggplot(aes(y = body_mass_g, x = sex)) +
    geom_point(size = 2, alpha = 0.3,
               shape = 21,
                aes(fill = sex),
                position = position_jitter(width = 0.1)) +
    stat_summary(fun.data = "mean_se",
                 geom = "pointrange",
                 color = "black",
                 aes(fill = sex),
                 shape = 21,
                 size = 0.5)
c
```

Patchwork combines graphs by using the `+`, `/`, and `|` operators. 

`+` combines graphs using the default layout (creating as square a grid as possible)

> Use `+` to combine plots `a` and `b`.

```{r}
a + b
```

`/` will stack graphs on top of each other

> Use `/` to arrange plot `b` on top of plot `c`

```{r}
b / c
```

`|` places graphs next to each other and can nest arrangements created with the other operators.

> Use `|` to arrange plot `c` on the left, and plot `a` over plot `b` to the right (hint: you may need to use parentheses to control the order of operations!)

```{r}
c | (a / b)
```


## Saving Graphs

use `ggsave()`

In `ggsave()`, you must specify:

* which `plot` you want to be saving
* the `filename` you want your graph to be saved with
* the `width` and `height` of the file

> Use `ggsave()` to save plot `a`

```{r}
ggsave(plot = a, 
       filename = "visualizations/test_plot.pdf",
       width = 12,
       height = 8)
```
