# Basic Wrangling

```{r}
library(tidyverse) # Load tidyverse packages
library(palmerpenguins) # Load Data
load(url("https://github.com/Psyc193L/Psyc193L.github.io/blob/main/data/mtcars2.RData?raw=true")) # Load example data
```

Data wrangling -- clean and prepare it for whatever task you have. 

Wrangling function names are all verbs.

## Arrange

`arrange()` orders the rows of a data frame by the values of selected columns.

```{r eval=FALSE}
mtcars2 %>%
  arrange(wt)
```

For descending order, wrap variable names in `desc()` within `arrange()`.

## Rename

`rename()` - renames columns.

```{r}
df %>%
  rename("new_column_name" = "old_column_name")
```

> Replace the X's to rename the abbreviated columns in `mtcars2`

```{r}
mtcars2 %>%
  rename("X" = "wt", 
         "horse_power" = "X",
         "X" = "cyl", 
         "displacement" = "X") %>%
  head()
```

### Saving Changes

> Check the changes made above

```{r}
mtcars2 %>%
  head()
```

Saving over an object is a permanent change. First verify code works, then save.

```{r}


```

If you need to use the object in its current state again or make significant changes to it, create a new object.

## Relocate

`relocate()` reorders columns in your dataframe by specifying which column(s) you want to move, and what they should come *.before* or *.after*.

> fill in the code below to move `wt` after `model`

```{r}
mtcars2 %>%
  relocate(X, .after = X)
```


Can move multiple columns

> fill in the code below to move `disp` and `wt` after `model`

```{r eval=FALSE}
mtcars2 %>%
  relocate(c(X, X), .X = X)
```


## Select

**subset** your data (cutting it to show only subsets of it).

`select()` -- selects and returns only specified columns.

`select(c(columns_of_interest))`

> Complete the code below to return only the `cyl` and `gear` columns

```{r eval=FALSE}
mtcars2 %>%
  select(c(X, X))
```


You can use `:` to return all the values in a range of *columns*

> Complete the code below to return the `cyl` column, `hp` column, and all columns in between the two

```{r eval=FALSE}
mtcars2 %>%
  select(c())
```


*get rid of columns* you do **NOT** want by negating with `!`

> Complete the code below to *get rid of* the `cyl` and `gear` columns (select *NOT* `cyl` and `gear`)

```{r eval=FALSE}
mtcars2 %>%
  select(c())
```


Select shortcut to move a variable to the front of your df:

```{r}
mtcars2 %>%
  select(wt, everything())
```

## Filter

`filter()` -- returns rows that meet specified condition(s).


> Complete the code below so that only rows where `gear` has a value of `4` are returned

```{r eval=FALSE}
mtcars2 %>%
  filter(X == X)
```


Any evaluative operator can be used in the conditions:

> Complete the code below to return only rows that have a `disp` value greater than 300

```{r eval=FALSE}
mtcars2 %>%
  filter()
```


Tests can be text strings as well

> Complete the code below so that only rows for the "Lotus Europa" `model` of car are returned

```{r eval=FALSE}
mtcars2 %>%
  filter()
```


Multiple conditions can be strung together using logical operators:

> Complete the code below to return only rows where `cyl` does NOT have a value of 4 OR `hp` is less than 100

```{r eval=FALSE}
mtcars2 %>%
  filter()
```


Be mindful about the order of operations and using parentheses to make sure the conditions are evaluated as you intended. For example:

`filter(cyl == 4 | hp < 200 & gear == 5)` would be evaluated as:

`filter(cyl == 4 | (hp < 200 & gear == 5))`

which is different than:

`filter((cyl == 4 | hp < 200) & gear == 5)`

### %in%

The `%in%` operator checks to see if the value of one variable is in a vector of possible values.

> Complete the code that would result in the illustration below

```{r eval=FALSE}
mtcars2 %>%
  filter()
```


### Pattern Matching

To filter based on whether a value *contains* a certain string, use `grepl()`:

`grepl(pattern_to_search_for, where_to_search)`

> Complete the code below to return rows where "Porsche" is contained in the value for `model`

```{r}
mtcars2 %>%
  filter(grepl("X", X))
```

## Indexing

Two functions to help index within a pipe chain

### pull()

`pull()` will extract a variable from a df (like using `$` to index)

> Use `pull()` to index the `cyl` variable from `mtcars`

```{r}

```

The result is a vector, which allows it to be piped to other functions.

> First, use select to select the `cyl` column and then pipe that to `mean()`. Below that, use `pull()` to index `cyl` and then pipe that to `mean()`

```{r}
mtcars2

mtcars2
```

### pluck()

`pluck()` allows you to index elements from an object.

After indexing the `cyl` column, like above, if you wanted to get the 4th element from that vector:

```{r}
mtcars2 %>%
  pull(cyl) %>%
  pluck(4)
```

## Unique Entries

`distinct()` -- gives the unique values of a variable

> Complete the code to return all the unique values of the `cyl` variable

```{r}
mtcars2 %>%
  X(X)
```

`n_distinct()` -- gives the *number* of unique values, takes a vector as input

> below, first `pull()` to isolate the `cyl` variable, and then pipe that to `n_distinct()` to find the *number* of unique values

```{r}

```


## Adding Variables

To add new variables to your dataframe, you use the `mutate()` function.

`mutate("new_col_name" = content_for_that_column)`

For example:

```{r wt}
mtcars2 %>%
  mutate(wt_lbs = wt * 1000)
```

1. All new variables must be the same length as the existing columns in the dataframe
2. The R expression must return a vector

Multiple new columns can be created simultaneously

> Below, create a new column `cost_per_mile` that gives the cost per mile (hint: use `price_of_gas` and the `mpg` column), and another new column called `wt_lbs` that contains the car's actual weight in lbs instead of weight in 1000 lbs.

```{r}
price_of_gas = 6.25

mtcars2 %>%
  mutate(X = X / X,
         X = X * X)
```

### Conditional Values

You may want a variable to have a value based on some different conditions. `case_when()` can be extremely useful when creating new variables!

> Fill in the blanks in the code below to create a new variable called `fuel_efficiency` which has the value of "Poor" when `mpg` is less than or equal to 19, "Average" when `mpg` is greater than or equal to 20 and less than or equal to 25, and "Great" in all other instances.

```{r}
mtcars2 %>%
  mutate(fuel_efficiency = case_when(
    mpg <= X ~ "Poor",
    X >= 20 & mpg <= X ~ "X",
    TRUE ~ "Great"
  ))
```

`ifelse()` can be used in simple instances

> Complete the code below to create a new column titled `power` that has the value "High" if `hp` is greater than or equal to 200, and "Low" otherwise.

```{r}
mtcars2 %>%
  mutate(power = ifelse(X >= X, "High", "X"))
```

### Position

You can specify what existing column you want the new column to appear `.before` or `.after`.

> Complete the code below such that mutate will create this new column `.after` `mpg`

```{r}
price_of_gas = 6.25

mtcars2 %>%
  mutate(cost_per_mile = price_of_gas / mpg, X = "X")
```

### NAs

`NA` values can cause major issues. For example:

```{r}
4 + NA + 2

mean(c(4,5,3,NA))
```

Any time you have `NA` as part of your computation, the results are `NA`. 

3 good ways to deal with this:

`na.omit()` -- will remove *all* NAs. 

`drop_na()` - will remove an entire row of data if it has an `NA` value for *specific* column(s) that you select.

```{r}
c(4, 5, 3, NA) %>%
  na.omit() %>% 
  mean()

mean(c(4,5,3,NA), na.rm = TRUE)
```

```{r}
ex_df = data.frame(A = c(NA, 1, 4), 
           B = c(1, NA, 4), 
           C = c(1,4,5))
ex_df

ex_df %>%
  na.omit()

ex_df %>%
  drop_na()

ex_df %>%
  drop_na(A)
```

## Modifying Existing Variables

`mutate()` can also be used to modify existing variables

```{r}
mtcars2 %>%
  mutate(wt = wt * 1000)
```


### Change Variable Types

You can change data type by using the `as.*` function. The one exception is that when changing something to a *factor*, you should use `factor()`

> Complete the code below to turn `mpg` into `character` data and `cyl` into a `factor`

```{r}
mtcars2 %>%
  mutate(X = as.X(mpg),
         cyl = X(X)) %>%
  glimpse()
```

### Factors

#### Factor Conversion

Consider the following:

```{r}
data.frame(test = factor(c("0", "1")))
```

Say you want to change this data from a factor to numeric:

```{r}
data.frame(test = factor(c("0", "1"))) %>% 
  mutate(test = as.numeric(test))
```


Always double check that your code is doing what you intend it to, especially when converting to and from a *factor*!

#### Reorder Levels

You may at times want to change what that order is, most often in visualizations. Consider the following:

```{r}
mtcars2 %>%
  mutate(cyl = factor(cyl)) %>%
  ggplot(aes(x = cyl, fill = cyl)) +
    geom_bar(position = "identity")
```

`fct_infreq()` -- reorders the levels of a factor **in** their **freq**uency of occurrence (with highest frequency first).

```{r}
mtcars2 %>%
  mutate(cyl = factor(cyl) %>%
           fct_infreq()) %>%
  ggplot(aes(x = cyl, fill = cyl)) +
    geom_bar(position = "identity")
```

`fct_rev()`--  for "**rev**erse **freq**uency" (lowest frequency first)

```{r}
mtcars2 %>%
  mutate(cyl = factor(cyl) %>%
           fct_infreq() %>%
           fct_rev()) %>%
  ggplot(aes(x = cyl, fill = cyl)) +
    geom_bar(position = "identity")
```

*Note: You still need to first order the bars in their frequency, then reverse.*

Most of the time you will visualize the relationship or comparison between two more more variables, like in the graph below:

```{r warning = FALSE}
mtcars2 %>%
  mutate(cyl = factor(cyl)) %>%
  ggplot(aes(y = mpg, x = cyl)) +
  stat_summary(fun.data = "mean_se", geom = "pointrange")
```

`fct_reorder()` -- order levels of a factor by their relationship with another variable
* Must specify:
  + the factor to reorder 
  + other variable you wish to reorder the levels by

```{r warning = FALSE}
mtcars2 %>%
  mutate(cyl = factor(cyl)) %>%
  ggplot(aes(y = mpg, x = fct_reorder(cyl, mpg))) +
  stat_summary(fun.data = "mean_se", geom = "pointrange")
```

## Extras

* [Factors cheatsheet](https://github.com/rstudio/cheatsheets/blob/main/factors.pdf)
