---
title: ""
author: ""
date: ""
output: html_document
---

### Set up

```{r}
library(tidyverse)
msleep2 = msleep %>%
  select(-conservation)
```

For all questions below, you will use the `msleep2` dataframe.

1. 
  A. Use `arrange()` to order the dataset by `bodywt`.

```{r}

```

  B. Modify your `arrange()` call to order the `bodywt` column from greatest to least.

```{r}

```

  C. What is the largest animal recorded in this dataset?

    *answer here*

2. Both of the weight columns in this dataset are measuring in kilograms. Use `rename()` to give those variables more informative names. **Note: Do NOT save over the `msleep2` dataset. Just run the code.**

```{r}

```

3. Use `relocate()` to...
  A. Move the `order` column to be positioned before the `vore` column.

```{r}

```

  B. Move the `sleep_total` column to be positioned after the `sleep_cycle` column.

```{r}

```

  C. Move both wt columns to be positioned after `genus`.

```{r}

```

4. Use `select()` to get...
  A. The `name` and `vore` columns.

```{r}

```

  B. The `genus` and `order` columns.

```{r}

```

  C. All the sleep related columns.

```{r}

```

5. Use `select()` to get rid of...
  A. The `awake` column.

```{r}

```

  B. All columns related to the animal's weight.

```{r}

```

6. `filter()` the data to show only the observations where...
  A. The animals are of Rodentia order.

```{r}

```

  B. The animals have a body weight of 5 or greater.

```{r}

```

  C. The animals are not herbivores.

```{r}

```


7. Use `filter()` to show only the observations where...
  A. The animals who sleep for over 14 hours total and weigh less than 3

```{r}

```

  B. The carnivores who spend over 10 hours awake, then subset only the `awake`, `vore`, and `sleep_total` columns.

```{r}

```

  C. All animals have a brain weight greater than 0.1 or spend less than 1 hour in rem, **except those who are herbivores**, then subset only the `brainwt`, `sleep_rem`, and `name` columns, and arrange those results by `brainwt` from greatest to least.

```{r}

```

8. 

  A. `filter()` the data to show animals in the "Cetacea", "Cingulata", or "Pilosa" order, who sleep for a total of anywhere between 5 and 10 hours.

```{r}

```

  B. Modify the code from above to show only the `name`, `order`, `sleep_total`, and `brainwt`.

```{r}

```

  C. Modify the code from above to arrange by `sleep_total` from least to greatest.

```{r}

```

9. Filter the data to show...
  A. All observations for seals

```{r}

```

  B. All observations for elephants

```{r}

```

10. Using a pipe chain (`%>%`)...
  A. Index the `sleep_total` variable from `msleep2`.

```{r}

```

  B. Find the mean of `sleep_total`.

```{r}

```

  C. Subset the data to only include carnivores, index the `bodywt` column, and find the average value. 
  
```{r}

```
  
  
  Now do the same for herbivores. 
  
```{r}

```
  
  Which has a higher average body weight?

    *Answer here*

11.
  A. Subset the data for primates who spend more than 13 hours awake, arrange the `awake` column from greatest to least, index the `awake` variable, and the 2nd value from the resulting vector.

```{r}

```

  B. Using a process similar to the one above, write some code that will result in the value for the 2nd lowest brain weight for omnivores who spend less than 2 hours in rem.

```{r}

```

12. 
  A. Find the unique values in the `vore` column.

```{r}

```

  B. Find the *number* of unique values in the `vore` column.

```{r}

```

13. 
  A. The sleep variables are all measured in hours. Create a new variable called `sleep_total_m` that measures total **minutes** of sleep.

```{r}

```

  B. Create a new variable that represents the proportion of total sleep spent in rem, move that column to come after `sleep_rem`, filter to show only observations with a ratio of 0.25 or greater, arrange the new column from greatest to least, and index the `bodywt` of the animal with the highest ratio.

```{r}

```

14. 
  A. Find out what the average total sleep is for all animals, then use `case_when()` to create a new column that has the value "sleepyhead" if the animal has a `sleep_total` higher than average, "wide-awake" if lower than average, and "average" if exactly average.

```{r}

```

  B. Use `ifelse()` to create a new column just indicating whether the animal had a "higher" or "lower" `sleep_total` than average.

```{r}

```

15. 
  A. Use `drop_na()` to remove all observations with an `NA`.

```{r}

```

  B. Only get rid of observations with an `NA` for `brainwt`.

```{r}

```

16. 
  A. As mentioned above, the weight columns are measured in kg. Change these columns so that they contain the weight in lbs (1kg = ~2.205 lbs). Arrange the new body weight column from least to greatest, and index the value for the lightest animal in the dataset.

```{r}

```

  B. Change the `vore` column to be a *factor* instead of *character*, and the `awake` column to be a *character* instead of *numeric*.

```{r}

```

17. Take 2 visualizations you created in the exercises from the data visualization lectures and reorder the factor levels so they are in a more sensible order.

```{r}

```


# Feedback 

Please save the appropriate number to the variables below:

1. Approximately how long (in minutes) do you think it took you to complete this assignment?

```{r}
timeEstimate = 
```

2. How difficult or challenging did you find this assignment?

Extremely easy -------------------------------------- Extremely challenging 
                                                     (impossible to complete)
    1                                                           10
    
```{r}
challenge = 
```
    
    
3. How engaging or fun did you find this assignment?
  
Extremely Boring and Dry -------------------------------------- Extremely Engaging and Fun 
          1                                                                   10

```{r}
engagement = 
```

4. If you have any other feedback about this assignment, please provide it below.




