---
title: ""
author: ""
date: ""
output: html_document
---

```{r}
library(tidyverse)
# Modify the file path in the code below to properly load the "NFLScores2011.rda" file
load("NFLScores2011.rda")
```

Do not save over the object unless you are told to *update*

Examine the `NFLScores2011` dataset

```{r}

```

1. Use `arrange()` to check `HomeScore` and `AwayScore` to find out what was the highest number of points scored by a team in a single game during this season

```{r}

```

What was the team and how many points did they score?
  - 
  
2. Use `arrange()` to check `HomeYards` and `AwayYards` to find out what was the fewest yards a team got in a single game during this season

```{r}

```

What was the team and how many yeards did they get?
  - 

3. Use `rename()` to change all the variables using camelCase to use snake_case

```{r}

```

4. Use `relocate()` to move the `Day` column after `Week`

```{r}

```

5. Move `HomeYards` and `AwayYards` before `HomeScore`

```{r}

```

Use `select()` too....

6. Return the `HomeScore` variable

```{r}

```

7. Keep only the variables relating to the Home Team

```{r}

```

8. Keep only the variables related to the game's statistics (how many points and yards there were)

```{r}

```

9. Keep all variables except `Date`, `DateStr`, and `YDM`

```{r}

```

Use `filter()` too...

10. Find only games played on a Monday

```{r}

```

11. Find only games played after Week 10

```{r}

```

12. Find the games where the home team was not "Green Bay Packers"

```{r}

```

13. Find the games played on Monday's and Thursday's (hint: consider what logical operator you need)

```{r}

```

14. Find games played on Sunday in week 7

```{r}

```

15. Find games that are either on Sunday OR have a Home Score greater than 40

```{r}

```

16. Find games played by teams in the AFC North division ("Baltimore Ravens", "Pittsburgh Steelers", "Cleveland Browns", "Cincinnati Bengals"). 

*Hint: Make sure to check for both the `HomeTeam` and the `AwayTeam` to see if either of them has a team in the list of AFCN teams*

```{r}

```

17. Find games played in week 6 and only keep columns for the teams and scores

```{r}

```

18. Use `pull()` to index the scores by the "Baltimore Ravens". There will be scores from when they are the `HomeTeam` and when they are the `AwayTeam`. Save each to a vector called `Ravens_score_home` and `Ravens_score_away`, respectively.

```{r}

```

19. Print out the two vectors from above. What was their highest point total at home? away? Use `pluck()` to pull out these values.

```{r}

```

Using `distinct()` and `n_distinct()`...

20. List the names of all the teams in the NFL

```{r}

```


21. How many teams are there total?

```{r}

```

22. How many teams scored 40 or more points as the `AwayTeam`?

```{r}

```

23. Who were those teams?

```{r}

```

Using `mutate()`...

24. Add a new column that computes the total score of a game

```{r}

```

25. Organize the dataframe by total score from greatest to least

```{r}

```

26. Add a new column after AwayYards that computes the total yards for a game

```{r}

```

27. Add a new column with the ratio of home team's score to away team's score

```{r}

```

28. Add a new column that is `TRUE` if the ratio is 3 or greater

```{r}

```

29. Keep only games before week 8 where this ratio is 3 or greater

```{r}

```

30. Only keep the Away columns, find stats only for the Houston Texans, and add a new column called "yards_rank" that contains:

"Meh" if `AwayScore` is less than 20

"Great" if `AwayScore` is greater than or equal to 30

"Decent" if `AwayScore` is anything else

```{r}

```

31. Convert the `HomeTO` and `AwayTO` variables to be factors

```{r}

```

# Feedback

Please save the appropriate number to the variables below:

1. Approximately how long (in minutes) do you think it took you to complete this assignment?

```{r}
timeEstimate = 
```

2. How difficult or challenging did you find this assignment?

Extremely easy -------------------------------------- Extremely challenging 
                                                     (impossible to complete)
    1                                                           10
    
```{r}
challenge = 
```
    
    
3. How engaging or fun did you find this assignment?
  
Extremely Boring and Dry -------------------------------------- Extremely Engaging and Fun 
          1                                                                   10

```{r}
engagement = 
```

4. If you have any other feedback about this assignment, please provide it below.




