---
title: ""
author: ""
date: ""
output: html_document
---

```{r}
library(palmerpenguins)
library(patchwork)
library(RColorBrewer)
library(colorspace)
library(viridis)
library(tidyverse)
# Modify the file path in the code below to properly load the "diamonds_sample.RData" file
load("C:/Users/Connie/Downloads/diamonds_sample.RData") 
```

They say that diamonds are a person's best friend, so why stop using the `diamonds_sample` dataset now?! 

As a reminder:

`diamonds_sample` contains the following variables: 

* `price` - price in USD
* `carat` - weight of the diamond
* `cut` - quality of the cut
* `color` - diamond color
* `clarity` - a measurement of how clear the diamond is
* `x` - length in mm
* `y` - width in mm
* `z` - depth in mm
* `depth` - total depth percentage
* `table` - width of top of diamond relative to widest point

You will be working with the code you wrote in the *Geoms Practice Problems* assignment. From that assignment, save the visualization from...

- problem 8 to `plot_bar` (first mapping the `color` variable to fill aesthetic)
- problem 15 to `plot_jitter` (first adding the width argument to `geom_jitter` and set it equal to 0.2, then mapping the `cut` variable to the color aesthetic)
- problem 23 to `plot_raster`

*NOTE: You do NOT have to use ONLY colorblind friendly color schemes/palettes for this exercise.*

Save your graphs below:

```{r}
plot_bar <- diamonds_sample %>%
  ggplot(aes(y = depth,
             x = color,
             fill = color)) + 
  stat_summary(fun = "mean", geom = "bar") + 
  stat_summary(fun.data = "mean_se", geom = "errorbar", width = 0.3)
 
plot_bar

  

plot_jitter = diamonds_sample %>%
  ggplot(aes(y = price,
             x = cut)) + 
  geom_jitter(aes(color = cut), height = 0, alpha = 0.7, width = 0.2) + 
  geom_boxplot(aes(color = cut), alpha = .3) + 
  stat_summary(fun = "mean", geom = "point", color = "black") + 
  stat_summary(fun.data = "mean_se", geom = "errorbar", width = .5, color = "black")

plot_jitter


  
plot_raster = diamonds_sample %>%
  ggplot(aes(y = carat,
             x = table,
             z = price)) + 
  stat_summary_hex(fun = "mean", geom = "tile", color = "black")

plot_raster
```


1. Using a manually specified scale (scale_*_manual/gradient)...

  A. Choose 7 colors that you think are *equally distinct* and use them for the colors in `plot_bar`
  
```{r}

  plot_bar + 
  scale_fill_manual(values = c("turquoise", "orange2", "purple", "hotpink", "darkgreen", "gold", "brown"))

```
  
  B. Choose 5 colors that you think are *in the same hue range* and use them for the colors in `plot_jitter`
  
```{r}

plot_jitter + 
  scale_color_manual(values = c("pink", "pink1", "pink2", "pink3", "pink4"))
  


```
  
  C. Create a gradient for `plot_raster` using *one hue*
  
```{r}

plot_raster + 
  scale_fill_gradient(low = "darkgreen", high = "lightgreen")

```
  
  D. Create a gradient for `plot_raster` using *two hues* that you feel are *perceptually distinct*
  
```{r}

plot_raster + 
  scale_fill_gradient(low = "yellow", high = "purple")


```
  
  E. Create a gradient for `plot_raster` using *at least 4 hues*

```{r}

plot_raster + 
  scale_fill_gradientn(colors = c("cyan", "maroon", "beige", "gold", "brown"))

```

2. Using scale_*_brewer/distiller...

  A. Set the colors of `plot_bar` to your *least* favorite and *most* favorite brewer palettes of the appropriate type (hint: for this exercise, consider `color` not to be ordered)
  

least:

```{r}
plot_bar + 
  scale_fill_brewer(palette = "Set2")
```


```{r, eval = FALSE}
#color has NO order, so use qualiative 
display.brewer.all(colorblindFriendly = TRUE, type = "qual") 

```

most:

```{r}

plot_bar + 
  scale_fill_brewer(palette = "Dark2")

```


  B. Set the colors of `plot_jitter` to your *least* favorite and *most* favorite brewer palettes of the appropriate type (hint: think about whether your data is ordered)
  
least:

```{r}
plot_jitter + 
  scale_color_brewer(palette = "PuRd")
```


```{r, eval = FALSE}
#IS ordered, use sequential
display.brewer.all(colorblindFriendly = TRUE, type = "seq")

```

most:

```{r}

plot_jitter + 
  scale_color_brewer(palette = "Blues")

```

  C. Set the colors of `plot_raster` to your NEXT *least* and *most* favorite brewer palettes of the appropriate type
  
least:

```{r}
plot_raster + 
  scale_fill_distiller(palette = "PuBu")
```


```{r, eval = FALSE}
#use sequential
display.brewer.all(colorblindFriendly = FALSE, type = "seq")

```

most:

```{r}

plot_raster + 
  scale_fill_distiller(palette = "OrRd")

```

3. Using scale_*_manual/gradientn...

  A. Set the colors of `plot_bar` to an appropriate brewer palette that you have yet to use
  
```{r}

plot_bar + 
  scale_fill_manual(values = brewer.pal(n = 7, name = 'Paired'))

```


  B. Set the colors of `plot_jitter` to an appropriate brewer palette that you have yet to use
  
```{r}

plot_jitter + 
  scale_color_manual(values = brewer.pal(n = 5, name = "PuBuGn"))


```

  C. Set the colors of `plot_raster` to an appropriate brewer palette that you have yet to use
  
```{r}

plot_raster + 
  scale_fill_gradientn(colors = brewer.pal(n = 6, name = "Greens"))

```


4. Using `plot_bar` and `plot_jitter`...

  A. Color them with the default grey scale
  
bar:  

```{r}

plot_bar + 
  scale_fill_grey()

```

jitter:

```{r}

plot_jitter + 
  scale_color_grey()

```


  B. Color them with a grey scale that is *high* luminance
  
bar:  

```{r}

plot_bar + 
  scale_fill_grey(start = .8, end = 1)

```

jitter:

```{r}

plot_jitter + 
  scale_color_grey(start = .7, end = 1)

```

  C. Color them with a grey scale that is *low* luminance

bar:  

```{r}

plot_bar + 
  scale_fill_grey(start = 0, end = .3)

```

jitter:

```{r}

plot_jitter + 
  scale_color_grey(start = .1, end = .4)

```

5. There is not a built in function to create a continuous grey scale. However, think about how you could create one of your own for `plot_raster`

```{r}

plot_raster + 
  scale_fill_gradient(low = "black", high = "white")

```

6. Use a different virids scales with scale_*_viridis to color the following graphs:

  A. `plot_bar`
  
```{r}

plot_bar + 
  scale_fill_viridis(discrete = TRUE, option = "plasma")
  

```

  B. `plot_jitter`
  
```{r}

plot_jitter + 
  scale_color_viridis(discrete = TRUE, option = "magma")

```

  C. `plot_raster`
  
```{r}

plot_raster + 
  scale_fill_viridis(option = "inferno")

```
  

# Feedback

Please save the appropriate number to the variables below:

1. Approximately how long (in minutes) do you think it took you to complete this assignment?

```{r}
timeEstimate = 150
```

2. How difficult or challenging did you find this assignment?

Extremely easy -------------------------------------- Extremely challenging 
                                                     (impossible to complete)
    1                                                           10
    
```{r}
challenge = 9.6
```
    
    
3. How engaging or fun did you find this assignment?
  
Extremely Boring and Dry -------------------------------------- Extremely Engaging and Fun 
          1                                                                   10

```{r}
engagement = 4
```

4. If you have any other feedback about this assignment, please provide it below.


**＼(°o°；）**

