---
title: ""
author: ""
date: ""
output: html_document
---

```{r}
library(tidyverse)
```


1. Define a variable called `confidence` that has *your* rating from 1-10 about how good you feel about control flow.

```{r}

confidence <- 8.2

```

2. Write an if statement that will print out the phrase "You are in good shape!" if `confidence` is greater than or equal to 6.

```{r}

if(confidence >= 6) {
  print("You are in good shape!")
}

```

3. Add an else condition to your code from above that will print "Better practice some more!" if `confidence` is less than 6.

```{r}

if(confidence >= 6) {
  print("You are in good shape!")
} else {
  print("Better practice some more!")
}

```


4. Okay, hang on. We know that when learning something new, people tend to under-weight their confidence. Let's make sure this gets accounted for. Write a new if statement that will print out the phrase "You are in great shape!" if `confidence` is greater than or equal to 8, "Good, keep at it!" if `confidence` is a value between 4 and 7, and "Better practice some more!" if `confidence` is less than 4.

```{r}

if(confidence >= 8) {
  print("You are in great shape!")
} else if ((4 < confidence) & (confidence < 7)) {
  print("Good, keep at it!") 
}  else {
    print("Better practice some more!")
}

confidence

```

5. Rewrite your code for 3 using `ifelse()`.

```{r}

ifelse(confidence >= 6,
       "You are in good shape!",
       "Better practice some more!")
```

6. Rewrite your code for 4 using nested `ifelse()` commands.

```{r}

ifelse(confidence >= 8,
       "You are in great shape!", 
       ifelse((4 < confidence) &  (confidence < 7),
       "Good, keep at it!",
       "Better practice some more!"))

```

7. Rewrite your code for 3 using `case_when()`.

```{r}

case_when(
  confidence >= 6 ~ "You are in good shape!",
  TRUE ~ "Better practice some more!"
)

```

8. Rewrite your code for 4 using `case_when()`.

```{r}


case_when(
  confidence >= 8 ~ "You are in great shape!",
  (4 < confidence) & (confidence < 7) ~ "Good, keep at it!", 
  TRUE ~ "Better practice some more!"
)

```


9. A lot of weird stuff happened during the early/lockdown portion of the COVID-19 pandemic. There were a lot of arcs and fads that happened. Some of which include:

- Dalgona coffee (Coffee)
- Making (sourdough) bread (Bread)
- Tiger King (TK)
- Animal Crossing (AC)
- Queen's Gambit (QG)
- Doing puzzles (Puzzles)
- Having anxiety/panic attacks (Anxiety)

Create a vector called `hobbies` that stores all the names (in parentheses) for each of these. 

```{r}

hobbies <- c("Dalgona coffee (Coffee)", "Making (sourdough) bread (Bread)", "Tiger King (TK)", "Animal Crossing (AC)", "Queen's Gambit (QG)", "Doing puzzles (Puzzles)", "Having anxiety/panic attacks (Anxiety)")


```


Next, use a for loop to iterate over each element of `hobbies` and print out each.

```{r}

for(i in 1:length(hobbies)) {
  print(hobbies[i])
}

```

10. 

  A. Create a vector called `rating` that contains your ratings from 1-10 on each of the  hobbies in `hobbies`. 

```{r}

rating <- c(6, 4, 2, 10, 9, 7, 10)


```

  B. Use a for loop to change those ratings to be out of 100 instead of 10 (hint: each item needs to multiplied by 10).
  
```{r}

for(i in 1:length(rating)) { 
  rating[i] = (rating[i] * 10)
  }


```
  

11. 

  A. Create a new vector called `participated` that has either a `TRUE` or `FALSE` rating for whether or not you participated in each of the hobbies in `hobbies`.
  
```{r}

participated <- c(FALSE, TRUE, TRUE, FALSE, FALSE, TRUE, TRUE)

```
  
  B. Combine `hobbies`, `rating`, and `participated` to create a dataframe called `pandemic_hobbies`. It should have three columns, titled "hobby", "rating", and "participated".
  
```{r}

pandemic_hobbies <- data.frame(hobbies, rating, participated)

pandemic_hobbies
  
```
  
  C. Use a for loop with control flow to print the name and rating of the hobbies that you participated in.
  
```{r}

pandemic_hobbies

for (i in 1:nrow(pandemic_hobbies)) {
  if(pandemic_hobbies$participated[i] == TRUE) {
    g <- pandemic_hobbies$hobbies[i]
    f <- pandemic_hobbies$rating[i]
    print(paste(g, f))
  }
}


```
  
  D. Modify your code above to do the following: 
    - If you participated in a hobby, print 1. "I participated in", 2. The hobby name, 3. "I gave it a rating of", 4. The rating.
    - If you did *not* participate in a hobby, print 1. "I did not participate in", 2. The hobby name.
    
**NOTE: it is fine to use `print()` more than once. The output does not have to be a singular string!**
    
```{r}

for (i in 1:nrow(pandemic_hobbies)) {
  h <- pandemic_hobbies$hobbies[i]
j <- pandemic_hobbies$rating[i]
  if(pandemic_hobbies$participated[i] == TRUE) {
    g <- "I participated in"
    i <- "I gave it a rating of"
    print(paste(g, h, i, j))
  }
  else {
    g <- "I did not participate in"
    print(paste(g, h))
  } 
}

```

# Feedback

Please save the appropriate number to the variables below:

1. Approximately how long (in minutes) do you think it took you to complete this assignment?

```{r}
timeEstimate = 300
```

2. How difficult or challenging did you find this assignment?

Extremely easy -------------------------------------- Extremely challenging 
                                                     (impossible to complete)
    1                                                           10
    
```{r}
challenge = 9.7
```
    
    
3. How engaging or fun did you find this assignment?
  
Extremely Boring and Dry -------------------------------------- Extremely Engaging and Fun 
          1                                                                   10

```{r}
engagement = 2.3
```

4. If you have any other feedback about this assignment, please provide it below.

**(ᇂ_ᇂ |||)**
