---
title: "Customization Practice Problem Set"
author: ""
date: ""
output: html_document
---

```{r}
library(tidyverse)
library(patchwork)
# Modify the file path in the code below to properly load the "diamonds_sample.RData" file
load("C:/Users/Connie/Downloads/diamonds_sample.RData") 
```

You are going to continue working with the `diamonds_sample` dataset.

`diamonds_sample` contains the following variables: 

* `price` - price in USD
* `carat` - weight of the diamond
* `cut` - quality of the cut
* `color` - diamond color
* `clarity` - a measurement of how clear the diamond is
* `x` - length in mm
* `y` - width in mm
* `z` - depth in mm
* `depth` - total depth percentage
* `table` - width of top of diamond relative to widest point


1. Use the `diamonds_sample` dataframe and create your own `base_graph`. Make sure to have a continuous variable on the y-axis and a categorical variable on the x-axis.

```{r}

base_graph <- diamonds_sample %>%
  ggplot(aes(y = carat,
             x = cut)) + 
  geom_boxplot(color = "black",
               alpha = 0.5) + 
  theme(legend.position = "none")

base_graph
  
```

2. Take your code from #1 and add on code that will modify your `base_graph` so the scale is more appropriate and represents the full range.

```{r}

base_graph + 
  coord_cartesian(ylim = c(0,4)) + 
  scale_y_continuous(breaks = seq(from = 0,
                                  to = 4,
                                  by = .5),
                     labels = seq(from = 0, to =  4, by = .5))

```

3. Take your code from #2 and add on code that will modify your `base_graph` so the padding is gone.

```{r}

base_graph + 
  coord_cartesian(ylim = c(0,4)) + 
  scale_y_continuous(breaks = seq(from = 0,
                                  to = 4,
                                  by = .5),
                     labels = seq(from = 0, to =  4, by = .5),
                     expand = c(0,0))
```

4. Take your code from #3 and add on code that will modify your `base_graph` so that it has more appropriate titles for the y- and x-axis. Additionally, add an appropriate title, subtitle (if needed), figure tag, and caption.

```{r}

base_graph + 
  coord_cartesian(ylim = c(0,4)) + 
  scale_y_continuous(breaks = seq(from = 0,
                                  to = 4,
                                  by = .5),
                     labels = seq(from = 0, to =  4, by = .5),
                     expand = c(0,0)) + 
  labs(title = "Does The Average Diamond Carat Vary Based On It's Quality?",
       subtitle = "Diamonds Procurred Through Diamond Markets",
       y = "Diamond Carat",
       x = "Cut Quality",
       tag = "A",
       caption = "Note: Extreme outliers have been removed from visual")

```

5. Create a new variable called `modified_graph` that takes your `base_graph` and saves all modifications you've added in questions 2:4. Then, try applying some different themes to your `modified_graph`.

```{r}

modified_graph <- base_graph + 
  coord_cartesian(ylim = c(0,4)) + 
  scale_y_continuous(breaks = seq(from = 0,
                                  to = 4,
                                  by = .5),
                     labels = seq(from = 0, to =  4, by = .5),
                     expand = c(0,0)) + 
  labs(title = "How Does Cut Quality Influence The Carat of Diamond",
       subtitle = "Diamonds Procurred Through Well-Regarded Diamond Markets",
       y = "Diamond Weight",
       x = "Cut Quality",
       tag = "A",
       caption = "Note: Extreme outliers have been removed from visual")

modified_graph + 
  theme_bw()

modified_graph + 
  theme_classic()

modified_graph + 
  theme_dark()

```

6. Add some code to `modified_graph` to modify your visualization's titles and increase their legibility.

```{r}

modified_graph +
  theme(plot.title = element_text(size = 18,
                                  hjust = 0.5),
        plot.subtitle = element_text(size = 12,
                                     hjust = 0.5),
        plot.tag = element_text(face = "bold"))

```

7. Take your code from #6 and add on code that will modify your visualization's caption and increase its legibility.

```{r}

modified_graph +
  theme(plot.title = element_text(size = 18,
                                  hjust = 0.5),
        plot.subtitle = element_text(size = 12,
                                     hjust = 0.5),
        plot.tag = element_text(face = "bold"),
        plot.caption = element_text(face = "italic",
                                    hjust = 0))

```

8. Take your code from #7 and add on code that will modify your visualization's axes titles and increase their legibility.

```{r}

modified_graph +
  theme(plot.title = element_text(size = 18,
                                  hjust = 0.5),
        plot.subtitle = element_text(size = 12,
                                     hjust = 0.5),
        plot.tag = element_text(face = "bold"),
        plot.caption = element_text(face = "italic",
                                    hjust = 0),
        axis.title.x = element_text(size = 12,
                                    face = "bold",
                                    margin = margin(t = 0.1,
                                                    unit = "inch")),
        axis.title.y = element_text(size = 12,
                                    face = "bold",
                                    margin = margin(r = 0.1,
                                                    unit = "inch")))

```

9. Take your code from #8 and add on code that will modify your visualization's axes values and increase their legibility.

```{r}

modified_graph +
  theme(plot.title = element_text(size = 18,
                                  hjust = 0.5),
        plot.subtitle = element_text(size = 12,
                                     hjust = 0.5),
        plot.tag = element_text(face = "bold"),
        plot.caption = element_text(face = "italic",
                                    hjust = 0),
        axis.title.x = element_text(size = 12,
                                    face = "bold",
                                    margin = margin(t = 0.1,
                                                    unit = "inch")),
        axis.title.y = element_text(size = 12,
                                    face = "bold",
                                    margin = margin(r = 0.1, 
                                    unit = "inch")),
        axis.text = element_text(face = "italic",
                                 color = "black",
                                 size = 10),
         axis.ticks = element_line(color = "black"))


```

10. Create a new variable called `a` that takes your `modified_graph` and saves all the new modifications you've added in questions 6:9.

```{r}

a <- modified_graph +
  theme(plot.title = element_text(size = 18,
                                  hjust = 0.5),
        plot.subtitle = element_text(size = 12,
                                     hjust = 0.5),
        plot.tag = element_text(face = "bold"),
        plot.caption = element_text(face = "italic",
                                    hjust = 0),
        axis.title.x = element_text(size = 12,
                                    face = "bold",
                                    margin = margin(t = 0.1,
                                                    unit = "inch")),
        axis.title.y = element_text(size = 12,
                                    face = "bold",
                                    margin = margin(r = 0.1, 
                                    unit = "inch")),
        axis.text = element_text(face = "italic",
                                 color = "black",
                                 size = 10),
         axis.ticks = element_line(color = "black"))

a
```


11. Take the code from questions 3, 11, 21, and 23, on your "geoms_practice" assignment, change any instances of `price` to `log10(price)`, and make any other aesthetic modifications that you think help improve the legibility or effectiveness of the graph. 

Then, repeat steps similar to those for 1:9 above to customize these visualizations. Save these new visualizations to `b`, `c`, `d`, and `e`, and call each variable to create/print the new graphs.

  B. 
  
```{r}

b <- diamonds_sample %>%
  ggplot(aes(x = log10(price))) + 
  geom_histogram(color = "black",
                 bins = 40,
                 fill = "dimgray") + 
  coord_cartesian(ylim = c(0,80)) + 
  scale_y_continuous(breaks = seq(from = 0,
                                  to = 80,
                                  by = 5),
                     labels = seq(from = 0, to = 80, by = 5),
                     expand = c(0,0)) + 
  labs(title = "The Most Common Prices of Diamonds",
       subtitle = "How Expensive Diamonds Really Are",
       y = "Frequency",
       x = "Log10 Price (USD)",
       tag = "B",
       caption = "Note: Bimodal Distribution") + 
  theme(plot.title = element_text(size = 18,
                                  hjust = 0.5),
        plot.subtitle = element_text(size = 12,
                                     hjust = 0.5),
        plot.tag = element_text(face = "bold"),
        plot.caption = element_text(face = "italic",
                                    hjust = 0),
        axis.title.x = element_text(size = 12,
                                    face = "bold",
                                    margin = margin(t = 0.1,
                                                    unit = "inch")),
        axis.title.y = element_text(size = 12,
                                    face = "bold",
                                    margin = margin(r = 0.1, 
                                    unit = "inch")),
        axis.text = element_text(face = "italic",
                                 color = "black",
                                 size = 10),
         axis.ticks = element_line(color = "black"))

b

```

  C.
  
```{r}

c <- diamonds_sample %>%
  ggplot(aes(y = depth,
             x = clarity)) + 
  geom_boxplot(color = "salmon",
               fill = "sienna",
               size = .5)  + 
  coord_cartesian(ylim = c(50,80)) + 
  scale_y_continuous(breaks = seq(from = 50,
                                  to = 80,
                                  by = 2),
                     labels = seq(from = 50, to = 80, by = 2),
                     expand = c(0,0)) + 
  labs(title = "The Relationship Between Diamond Clarity and Depth",
       subtitle = "Clearer than the Deep Blue Sea",
       y = "Diamond Depth (%)",
       x = "Diamond Clarity",
       tag = "C") + 
  theme(plot.title = element_text(size = 18,
                                  hjust = 0.5),
        plot.subtitle = element_text(size = 12,
                                     hjust = 0.5),
        plot.tag = element_text(face = "bold"),
        plot.caption = element_text(face = "italic",
                                    hjust = 0),
        axis.title.x = element_text(size = 12,
                                    face = "bold",
                                    margin = margin(t = 0.1,
                                                    unit = "inch")),
        axis.title.y = element_text(size = 12,
                                    face = "bold",
                                    margin = margin(r = 0.1, 
                                    unit = "inch")),
        axis.text = element_text(face = "italic",
                                 color = "black",
                                 size = 10),
         axis.ticks = element_line(color = "black"))

c

```

  D.

```{r}
d <- diamonds_sample %>%
  ggplot(aes(y = clarity,
             x = cut,
             z = log10(price))) + 
   stat_summary_2d(fun = "mean", geom = "tile",
                   color = "black",
                   size = .5) + 
  labs(title = "The Prices of Diamonds of Different Cuts and Clairities",
       subtitle = "Comparision of all the Different Combinations",
       y = "Diamond Clarity",
       x = "Cut Quality",
       tag = "D",
       caption =  "Note: Values are Exponents with Bases of 10",
       fill = "Log10 Price (USD)") + 
   theme(plot.title = element_text(size = 22,
                                  hjust = 0.5),
        plot.subtitle = element_text(size = 16,
                                     hjust = 0.5),
        plot.tag = element_text(face = "bold"),
        plot.caption = element_text(face = "italic",
                                    hjust = 0),
        axis.title.x = element_text(size = 12,
                                    face = "bold",
                                    margin = margin(t = 0.1,
                                                    unit = "inch")),
        axis.title.y = element_text(size = 12,
                                    face = "bold",
                                    margin = margin(r = 0.1, 
                                    unit = "inch")),
        axis.text = element_text(face = "italic",
                                 color = "black",
                                 size = 10),
         axis.ticks = element_line(color = "black")) + theme(legend.box.background = element_rect(color = "black",
                                           size = 2),
      legend.title = element_text(face = "bold"),
      legend.text = element_text(face = "bold"), 
      legend.title.align = 0.5) 

d

```

  E.

```{r}

e <- diamonds_sample %>%
  ggplot(aes(y = carat,
             x = table,
             z = log10(price))) + 
  stat_summary_hex(fun = "mean", geom = "tile", color = "black") +
  labs(title = "The Prices of Diamonds of Different Carats and Widths",
       subtitle = "Comparision of all the Different Combinations",
       y = "Diamond Carat (Weight)",
       x = "Width of Diamond Top",
       tag = "E",
       caption =  "Note: Values are Exponents with Bases of 10",
       fill = "Log10 Price (USD)") + 
   theme(plot.title = element_text(size = 22,
                                  hjust = 0.5),
        plot.subtitle = element_text(size = 16,
                                     hjust = 0.5),
        plot.tag = element_text(face = "bold"),
        plot.caption = element_text(face = "italic",
                                    hjust = 0),
        axis.title.x = element_text(size = 12,
                                    face = "bold",
                                    margin = margin(t = 0.1, 
                                                    unit = "inch")),
        axis.title.y = element_text(size = 12,
                                    face = "bold",
                                    margin = margin(r = 0.1, 
                                    unit = "inch")),
        axis.text = element_text(face = "italic",
                                 color = "black",
                                 size = 10),
         axis.ticks = element_line(color = "black")) + theme(legend.box.background = element_rect(color = "black",
                                           size = 2),
      legend.title = element_text(face = "bold"),
      legend.text = element_text(face = "bold"), 
      legend.title.align = 0.5)


e

```


12. Use `patchwork` to create plots with the following layouts:


  A. 
  
|----|
| d  |
|----|
| c  |
|----|

```{r}

d / c

```

  B. 

|----|----|
| b  |  e |
|----|----|


```{r}

b + e

```


  C. 

|----|----|
| a  |  b |
|----|----|
| c  |  d |
|----|----|

```{r}

(a / c) | (b / d)

```

  D. 

|----|----|
|    e    |
|----|----|
| c  |  d |
|----|----|

```{r}

e / (c + d)

```

  E.
  
|----|----|
| a  |    |
|----|  c |
| b  |    |
|----|----|

```{r}

(a / b) | c

```

  F. 
  
|----|----|
| e  |  a |
|----|----|
|    b    |
|----|----|

```{r}

(e + a) / b

```

  G.

|----|----|
|    |  e |
| d  |----|
|    |  b |
|----|----|

```{r}

d | (e / b)

```


# Feedback

Please save the appropriate number to the variables below:

1. Approximately how long (in minutes) do you think it took you to complete this assignment?

```{r}
timeEstimate = 200
```

2. How difficult or challenging did you find this assignment?

Extremely easy -------------------------------------- Extremely challenging 
                                                     (impossible to complete)
    1                                                           10
    
```{r}
challenge = 4
```
    
    
3. How engaging or fun did you find this assignment?
  
Extremely Boring and Dry -------------------------------------- Extremely Engaging and Fun 
          1                                                                   10

```{r}
engagement = 7.6
```

4. If you have any other feedback about this assignment, please provide it below.


