# Data Transformation

```{r}
library(tidyverse) # Load tidyverse packages
load(url("https://github.com/Psyc193L/Psyc193L.github.io/blob/main/data/bakers.RData?raw=true")) # Load example data
```

Data you get will not always be tidy, you may need to make data *not* tidy, and your data may not even all be in a singular object!

## Pivots

Two main functions to reshape data are `pivot_longer()` and `pivot_wider()`.

### pivot_longer()

`pivot_longer()` "lengthens" data, increasing the number of rows and decreasing the number of columns. Must specify:

- specific **col**umn**s** to collapse
- name for new column with **names** 
- name for new column with **values**

`pivot_longer(cols, names_to, values_to)`

```{r}
bakers_long <- bakers %>%
  pivot_longer(cinnamon_1:nutmeg_3,
               names_to = "spice",
               values_to = "correct")

bakers_long
```

`bakers` contains data from contestants on a baking show (where they had to guess a spice from a blind taste test).

Observe how `pivot_longer()` can transform this df so that each row is a unique observation:


> Use `pivot_longer()` to pivot `bakers`, have the names column called "spice" and the values column called "correct", and save to a new df called `bakers_long`

```{r}

view(bakers)

bakers_long <- bakers %>%
  pivot_longer(cinnamon_1:nutmeg_3,
               names_to = "spice",
               values_to = "correct")

bakers_long

```

### pivot_wider()

`pivot_wider()` "widens" data, increasing the number of columns and decreasing the number of rows. Must specify:

- where new column **names** are *from*
- where the **values** for those new columns are **from**

`pivot_wider(names_from, values_from)`. 


> To verify this is true, take `bakers_long` and try to recreate the original `bakers` df with `pivot_wider()`. Compare that output to `bakers`. Does it match?

```{r}

bakers_long %>%
  pivot_wider(names_from = "spice",
              values_from = "correct")

bakers
#identical cuz we just redid the pivot londer 
```


## Relational Data

Processes that involve working with data in multiple objects are referred to as **relational data**.

### `bind_rows()`

```{r}
bakers2
```

`bakers2` has data from contestants on a different episode, and has the same form as the data in `bakers`. You may want to work with all the data in one dataframe.

`bind_rows()` -- *bind* all the *rows* of the objects passed to it. 

> Complete the code below to combine `bakers` and `bakers2`

```{r}
bind_rows(bakers, bakers2)
```


If one object contains columns the other does not, those values will be filled with `NA`.

```{r}
bakers %>%
  mutate("cumin_4" = c(1,1,0,0)) %>%
  bind_rows(bakers2)
```

When individual dfs do not have identical columns you the observations from `x` to be matched to the corresponding observation in `y` (usually by the values of some ID columns appearing in both).

## Mutating Joins

Mutating Joins, like `mutate()`, add new columns to a dataframe.

### inner_join()

`inner_join()` -- returns a df containing all observations in `x` that have a matched observation in `y`, for all columns in `x` and `y`.

### left_join()

`left_join()` -- returns a df containing all observations in `x` and all columns from `x` and `y`.

### right_join()

`right_join()` -- basically the same as `left_join()` except swap `x` with `y`.

### full_join()

`full_join()` -- returns a df containing all observations (rows) from both `x` and `y` (containing all the original data from both `x` and `y`).

## Set operators

Quick and easy way to filter for different *sets* of observations.

`bakers3` contains information about the contestants on an all-star version of this baking show.

```{r}
bakers_combined <- bind_rows(bakers, bakers2)

bakers_combined

bakers3
```

### union()

`union()` -- returns a df containing all the unique observations (rows) in `x` and `y`

> Use `union()` to find all the contestants appearing in any of the 3 episodes you have data for

```{r}
union(bakers_combined, bakers3)
```

### intersect()

`intersect()` -- returns a df containing only the observations (rows) that are in **both** `x` AND `y`.

> Use `intersect()` to find what contestants from episodes 1 and 2 (`bakers_combined`) were in the all-star episode.

```{r}
bakers_combined
bakers3
intersect(bakers_combined, bakers3)

```

### setdiff()

`setdiff()` -- returns a df containing only the observations (rows) in `x` that **do NOT** appear in `y`.

> Use `setdiff()` to find the contestants in the all-star episode who were not in episodes 1 or 2.

```{r}

setdiff(bakers_combined, bakers3)

```


## Extra Resources

* [pivoting vignette](https://tidyr.tidyverse.org/articles/pivot.html)
* [tidyexplain animated illustrations](https://github.com/gadenbuie/tidyexplain)
* [r4ds relational data](https://r4ds.had.co.nz/relational-data.html#relational-data)
* [more relational data](https://rstudio-education.github.io/tidyverse-cookbook/transform-tables.html#joins)

## References