---
title: ""
author: ""
date: ""
output: html_document
---

# Set up
```{r}
library(tidyverse)
msleep2 = msleep %>%
  select(-conservation)
```

With the `msleep2` dataset...

1. Use helper functions to...
   A. Select all columns that start with "sleep".
   
```{r}
msleep2 %>%
  select(starts_with("sleep"))

view(msleep2)

```
   
   B. Select all columns that end with "wt".

```{r}

msleep2 %>%
  select(ends_with("wt"))

```

2. Select all columns that contain "re".

```{r}

msleep2 %>%
  select(contains("re"))

```

3. Use `where()` to select...
   A. All columns that are numeric.
   
```{r}

msleep2 %>%
  select(where(is.numeric))

```
   
   B. All columns that are characters.

```{r}

msleep2 %>%
  select(where(is.character))

```

4. User helper functions to select the columns that...
   A. Contain "re" and are *numeric* data.
   
```{r}

msleep2 %>%
  select(contains("re")) %>%
  select(where(is.numeric))

```
   
   B. End with "e" and do not start with "sleep".

```{r}

msleep2 %>%
  select(ends_with("e")) %>%
  select(!starts_with("sleep"))

```

5. 
   A. Filter for observations where scores in any variable that ends with "wt" are above 35.
   
```{r}

msleep2 %>%
  filter(if_any(ends_with("wt"), ~ . > 35))

```
   
   B. Filter for observations where scores in any variable that starts with "sleep" are less than 2.

```{r}

msleep2 %>%
  filter(if_any(starts_with("sleep"), ~ . < 2))

```

6. Use helper functions to...
   A. Round all the columns that are *numeric*.
   
```{r}

msleep2 %>%
  mutate(across(where(is.numeric), round))


```
   
   B. Round only the columns that are *numeric* and start with "sleep".
   
```{r}

msleep2 %>%
  select(starts_with("sleep")) %>%
  mutate(across(where(is.numeric), round))

```
   
   C. `scale()` the columns that end with "wt" and are *numeric*, then filter the results for only those where all columns that end with "wt" are greater than 0.

```{r}

msleep2 %>%
  mutate(across(where(is.numeric))) %>%
  mutate(across(ends_with("wt"), scale)) %>%
   filter(if_all(ends_with("wt"), ~ . > 0))

```


# Feedback 

Please save the appropriate number to the variables below:

1. Approximately how long (in minutes) do you think it took you to complete this assignment?

```{r}
timeEstimate = 70
```

2. How difficult or challenging did you find this assignment?

Extremely easy -------------------------------------- Extremely challenging 
                                                     (impossible to complete)
    1                                                           10
    
```{r}
challenge = 2.7
```
    
    
3. How engaging or fun did you find this assignment?
  
Extremely Boring and Dry -------------------------------------- Extremely Engaging and Fun 
          1                                                                   10

```{r}
engagement = 8.1
```

4. If you have any other feedback about this assignment, please provide it below.


**ʕง•ᴥ•ʔง   ᶘಠᴥಠᶅ**

