---
title: ""
author: ""
date: ""
output: html_document
---

### Set up

```{r}
library(tidyverse)
msleep2 = msleep %>%
  select(-conservation)
```

For all questions below, you will use the `msleep2` dataframe.

1. 
  A. Use `arrange()` to order the dataset by `bodywt`.

```{r}

msleep2 %>%
  arrange(bodywt)

```

  B. Modify your `arrange()` call to order the `bodywt` column from greatest to least.

```{r}

msleep2 %>%
  arrange(desc(bodywt))

```

  C. What is the largest animal recorded in this dataset?

    *The largest animal in the dataset is the African elephant of genus Loxodonta.*

2. Both of the weight columns in this dataset are measuring in kilograms. Use `rename()` to give those variables more informative names. **Note: Do NOT save over the `msleep2` dataset. Just run the code.**

```{r}

msleep2 %>%
  rename("Brain_Weight(kg)" = brainwt,
         "Body_Weight(kg)" = bodywt)

```

3. Use `relocate()` to...
  A. Move the `order` column to be positioned before the `vore` column.

```{r}

msleep2 %>%
  relocate(order, .before = vore)

```

  B. Move the `sleep_total` column to be positioned after the `sleep_cycle` column.

```{r}

msleep2 %>%
  relocate(sleep_total, .after = sleep_cycle)

```

  C. Move both wt columns to be positioned after `genus`.

```{r}

msleep2 %>% 
  relocate(c(bodywt, brainwt), .after = genus)

```

4. Use `select()` to get...
  A. The `name` and `vore` columns.

```{r}

msleep2 %>%
  select(c(name, vore))

```

  B. The `genus` and `order` columns.

```{r}

msleep2 %>%
  select(c(genus, order))

```

  C. All the sleep related columns.

```{r}

msleep2 %>%
  select(c(sleep_total : sleep_cycle))

```

5. Use `select()` to get rid of...
  A. The `awake` column.

```{r}

msleep2 %>% 
  select(!awake)

msleep2

```

  B. All columns related to the animal's weight.

```{r}

msleep2 %>%
  select(!c(brainwt, bodywt))

#select(ends_with("wt")) works too :D

```

6. `filter()` the data to show only the observations where...
  A. The animals are of Rodentia order.

```{r}

msleep2 %>%
  filter(order == "Rodentia")

```

  B. The animals have a body weight of 5 or greater.

```{r}

msleep2 %>%
  filter(bodywt >= 5)

```

  C. The animals are not herbivores.

```{r}

msleep2 %>%
  filter(!vore == "herbi")

```


7. Use `filter()` to show only the observations where...
  A. The animals who sleep for over 14 hours total and weigh less than 3

```{r}

msleep2 %>%
  filter((sleep_total > 14) & (bodywt < 3))

```

  B. The carnivores who spend over 10 hours awake, then subset only the `awake`, `vore`, and `sleep_total` columns.

```{r}

msleep2 %>%
  filter(awake > 10) %>%
  select(c(awake, vore, sleep_total))
  

```

  C. All animals have a brain weight greater than 0.1 or spend less than 1 hour in rem, **except those who are herbivores**, then subset only the `brainwt`, `sleep_rem`, and `name` columns, and arrange those results by `brainwt` from greatest to least.

```{r}

msleep2 %>%
  filter(((brainwt > 0.1) | (sleep_rem < 1)), !vore == "herbi") %>%
  select(c(brainwt, sleep_rem, name)) %>%
  arrange(desc(brainwt))

```

8. 

  A. `filter()` the data to show animals in the "Cetacea", "Cingulata", or "Pilosa" order, who sleep for a total of anywhere between 5 and 10 hours.

```{r}

msleep2 %>%
  filter(order %in% c("Cetacea", "Cingulata", "Pilosa")) %>%
  filter((sleep_total > 5) & (sleep_total <10))

```

  B. Modify the code from above to show only the `name`, `order`, `sleep_total`, and `brainwt`.

```{r}

msleep2 %>%
  filter(order %in% c("Cetacea", "Cingulata", "Pilosa")) %>%
  filter((sleep_total > 5) & (sleep_total <10)) %>%
  select(c(name, order, sleep_total, brainwt))

```

  C. Modify the code from above to arrange by `sleep_total` from least to greatest.

```{r}

msleep2 %>%
  filter(order %in% c("Cetacea", "Cingulata", "Pilosa")) %>%
  filter((sleep_total > 5) & (sleep_total <10)) %>%
  select(c(name, order, sleep_total, brainwt)) %>%
  arrange(sleep_total)

```

9. Filter the data to show...
  A. All observations for seals

```{r}

msleep2 %>%
  filter(grepl("seal", name))

```

  B. All observations for elephants

```{r}

msleep2 %>%
  filter(grepl("elephant", name))

```

10. Using a pipe chain (`%>%`)...
  A. Index the `sleep_total` variable from `msleep2`.

```{r}

msleep2 %>%
  pull(sleep_total)

```

  B. Find the mean of `sleep_total`.

```{r}

msleep2 %>%
  pull(sleep_total) %>%
  mean()

```

  C. Subset the data to only include carnivores, index the `bodywt` column, and find the average value. 
  
```{r}

msleep2 %>%
  filter(vore == "carni") %>%
  pull(bodywt) %>%
  mean()

```
  
  
  Now do the same for herbivores. 
  
```{r}

msleep2 %>%
  filter(vore == "herbi") %>%
  pull(bodywt) %>%
  mean()

```
  
  Which has a higher average body weight?

    *Herbivors have a higher average body weight. Herbivores have mean body weight of 366.8773, whereas carnivores have mean body weight of 90.75111.*

11.
  A. Subset the data for primates who spend more than 13 hours awake, arrange the `awake` column from greatest to least, index the `awake` variable, and the 2nd value from the resulting vector.

```{r}

msleep2 %>%
  filter(order == "Primates") %>%
  filter(awake > 13) %>%
  arrange(desc(awake)) %>%
  pull(awake) %>%
  pluck(2)

```

  B. Using a process similar to the one above, write some code that will result in the value for the 2nd lowest brain weight for omnivores who spend less than 2 hours in rem.

```{r}

msleep2 %>%
  filter(vore == "omni") %>%
  filter(sleep_rem < 2) %>%
  arrange(sleep_rem) %>%
  pull(brainwt) %>%
  pluck(2)

```

12. 
  A. Find the unique values in the `vore` column.

```{r}

msleep2 %>%
  distinct(vore)

```

  B. Find the *number* of unique values in the `vore` column.

```{r}

msleep2 %>%
  pull(vore) %>%
  n_distinct()

```

13. 
  A. The sleep variables are all measured in hours. Create a new variable called `sleep_total_m` that measures total **minutes** of sleep.

```{r}

msleep2 %>%
  mutate(sleep_total_m = sleep_total * 60)

```

  B. Create a new variable that represents the proportion of total sleep spent in rem, move that column to come after `sleep_rem`, filter to show only observations with a ratio of 0.25 or greater, arrange the new column from greatest to least, and index the `bodywt` of the animal with the highest ratio.

```{r}

msleep2 %>%
 mutate(sleep_total_rem = (sleep_total / sleep_rem)) %>%
  relocate(sleep_total_rem, .after = sleep_rem) %>%
  filter(sleep_total_rem > .25) %>%
  arrange(desc(sleep_total_rem)) %>%
  pull(bodywt) %>%
  pluck(1)

```

14. 
  A. Find out what the average total sleep is for all animals, then use `case_when()` to create a new column that has the value "sleepyhead" if the animal has a `sleep_total` higher than average, "wide-awake" if lower than average, and "average" if exactly average.

```{r}

mean_total_sleep <- msleep2 %>%
  pull(sleep_total) %>%
  mean() 
mean_total_sleep

  
msleep2 %>%
  mutate(nightnight = case_when(sleep_total >= mean_total_sleep ~ "sleepyhead",
                                sleep_total < mean_total_sleep ~ "wide-awake",
                                sleep_total == mean_total_sleep ~ "average"))

```

  B. Use `ifelse()` to create a new column just indicating whether the animal had a "higher" or "lower" `sleep_total` than average.

```{r}

msleep2 %>%
  mutate(avg_sleep_total = ifelse(sleep_total > mean_total_sleep, 
                                  "higher", "lower"))

```

15. 
  A. Use `drop_na()` to remove all observations with an `NA`.

```{r}

msleep2 %>%
  drop_na()

```

  B. Only get rid of observations with an `NA` for `brainwt`.

```{r}

msleep2 %>%
  drop_na(brainwt)

```

16. 
  A. As mentioned above, the weight columns are measured in kg. Change these columns so that they contain the weight in lbs (1kg = ~2.205 lbs). Arrange the new body weight column from least to greatest, and index the value for the lightest animal in the dataset.

```{r}

msleep2 %>%
  mutate(bodywt = bodywt * 2.205) %>%
  mutate(brainwt = brainwt * 2.205) %>%
  arrange(bodywt) %>%
  pull(bodywt) %>%
  pluck(1)

msleep2

```

  B. Change the `vore` column to be a *factor* instead of *character*, and the `awake` column to be a *character* instead of *numeric*.

```{r}

msleep2 %>%
  mutate(vore = as.factor(vore)) %>%
  mutate(awake = as.character(awake))

msleep2

```

17. Take 2 visualizations you created in the exercises from the data visualization lectures and reorder the factor levels so they are in a more sensible order.

```{r}
library(palmerpenguins) # Load penguins data


penguins %>%
    mutate(sex = factor(sex) %>%
           fct_infreq()) %>%
  drop_na() %>%
    ggplot(aes(y = body_mass_g, x = sex)) +
    geom_point(size = 2, alpha = 0.3,
               shape = 21,
                aes(fill = sex),
                position = position_jitter(width = 0.1)) +
    stat_summary(fun.data = "mean_se",
                 geom = "pointrange",
                 color = "black",
                 aes(fill = sex),
                 shape = 21,
                 size = 0.5)


```

```{r}
penguins %>%
  mutate(island = factor(island)) %>%
  ggplot(aes(y = body_mass_g, x = fct_reorder(island, body_mass_g))) +
  geom_jitter(height = 0, width = 0.1, 
              size = 2, alpha = 0.3,
              aes(color=island)) +
    stat_summary(fun.data = "mean_se",
               geom = "pointrange",
               color = "black",
               aes(fill = island),
               shape = 21,
               size = 0.5)


```


# Feedback 

Please save the appropriate number to the variables below:

1. Approximately how long (in minutes) do you think it took you to complete this assignment?

```{r}
timeEstimate = 120
```

2. How difficult or challenging did you find this assignment?

Extremely easy -------------------------------------- Extremely challenging 
                                                     (impossible to complete)
    1                                                           10
    
```{r}
challenge = 2.3
```
    
    
3. How engaging or fun did you find this assignment?
  
Extremely Boring and Dry -------------------------------------- Extremely Engaging and Fun 
          1                                                                   10

```{r}
engagement = 8.3
```

4. If you have any other feedback about this assignment, please provide it below.


**(っ´ω｀c)**

