---
title: ""
author: ""
date: ""
output: html_document
---


1. Use each of the following operators in a new expression:

"+"

```{r}

oneA <- (387 + 35)
oneA

```

"-"

```{r}

oneB <- (9689 - 343)
oneB

```

"*"

```{r}

oneC <- (398 * 3)
oneC

```

"/"

```{r}

oneD <- (23 / 2.453)
oneD

```

"^"

```{r}

oneE <- (5 ^ sin(24))
oneE

```

"%%"

```{r}

oneF <- (70 %% 4.20)
oneF

```


2. Use each of the following operators in a new expression:

"<"

```{r}

Margarine <- 20.4
Margarine 

Butter <- 66.1
Butter

Margarine < Butter
```

">"

```{r}

PorkThiamin <- 16
BeefThiamin <- 276

PorkThiamin > BeefThiamin
```

"<="

```{r}

Bulking <- (12 / 34) %% PorkThiamin
Cutting <- BeefThiamin ^ 8

Bulking <= Cutting

```

">="

```{r}

WalletA <- (100 + .097)
WalletB <- (255 + 2)

WalletB >= WalletA


```

"=="

```{r}

SisterHeight <- 170
BrotherHeight <- 158
MyHeight <- 182.88 

Comparison <- ((SisterHeight + BrotherHeight) - 145.12) == MyHeight
print(Comparison)

```

"!="

```{r}

GenZ <- 17.34
BabyBoomers <- 76.97

GenZ != BabyBoomers

```

3. 
  A. Use each of the operators below in a new expression. 

"&"

```{r}

Elementary <- 5 
MiddleSchool  <- 4 

(Elementary > 4) & (MiddleSchool < 4)

```

"|"

```{r}

philo <- c(TRUE, FALSE) 
(philo > 1) | (philo < 1)

```

"!"

```{r}

x = 34
y = 1
z = 3.3

!(x + !z)

```

B. Use *each* operator (`&`, `!`, and `|`) combined with at least one operator from exercise 1 or 2 as well.

```{r}

and_operator <- 56
and_operator > (5 * 1) & (and_operator < 57)

not_operator <- (29 / 34)
!not_operator >= .8529

#does this count as using at least one operator? does using an operator when defining the variable count? 


or_operator <- c(2.34, 234, 2340)
(or_operator > 234) | (or_operator < 34)


```


C. Now, use *each* operator (`&`, `!`, and `|`) combined with at least one *other* operator (logical or comparison operators).

```{r}

papertowel <- 10
handtowel <- 1000
(papertowel != handtowel) & (papertowel < handtowel)



gambling_disorder <- c(1.5, 2.0)
(gambling_disorder == 2.0) | (gambling_disorder != "money")



not_today = c("sky", "cloudy", "overcast")
!not_today >= 0

```


4. Define variables of each of the following types and use `typeof()` to verify their type.

A. number

```{r}

number <- .00000000000012
typeof(number)

```

B. character

```{r}

character <- "Mary had a little lamb"
typeof(character)

```


C. logical

```{r}

logical <- TRUE | FALSE
typeof(logical)

```

5. Create 3 vectors that each contain a different type of data (number, character, and logical). See which operations can be applied to each vector.

  A. number

```{r}
numberVector <- c(19, 18, 16, 10)
```


```{r, eval = FALSE}
mean(numberVector) #yes
numberVector ^ 3 #yes
numberVector / 23.54 #yes
numberVector - numberVector #yes
numberVector %% .12345 #yes
numberVector * 2 #yes
numberVector + 1 #yes

!numberVector #yes
numberVector != numberVector #yes 

numberVector & numberVector #yes

```

  B. character

```{r}
characterVector <- c('Connie', 'Benny', 'Nicole', 'Jefferson')
```


```{r, eval = FALSE}
mean(characterVector) #no

characterVector ^ 3 #no
characterVector / 23.54 #no
characterVector - characterVector #no
characterVector %% .12345 #no
characterVector * 2 #no
characterVector + 1 #no

characterVector & characterVector #no
!characterVector #no 
characterVector | characterVector #no 

characterVector > characterVector #yes
characterVector == characterVector #yes

#NOTE: added eval = FALSE because I was unable to knit properly. 


```

  C. logical

```{r}
logicalVector <- c(TRUE, TRUE, TRUE, FALSE)
```


```{r, eval = FALSE}
mean(logicalVector) #yes 
logicalVector ^ 3 #yes
logicalVector / 23.54 #yes
logicalVector - characterVector #yes
logicalVector %% .12345 #no
logicalVector * 2 #yes
logicalVector + 1 #yes


!logicalVector #yes
logicalVector & logicalVector #yes

logicalVector == logicalVector #yes
logicalVector != logicalVector #yes


```

6.

  A. Index the 1st and 2nd element from the vector in 5A

```{r}

numberVector[1:2]

```

  B. Index the 2nd and 3rd element from the vector in 5B.
  
```{r}

characterVector[2:3]

```
  
  C. Save the first element from your first vector to a variable called `first_first`.
  
```{r}

first_first <- numberVector[1]
first_first

```

  D. Save the last element from your last vector to one called `last_last`.
  
```{r}

last_last <- logicalVector[length(logicalVector)]
last_last

```
  

7. Create a dataframe called `my_df` that has information about your top 3 favorite animals. It should contain 3 columns: 1. One that has the words, "first", "second", and "third". 2. Another that has the animals names. 3. A third having a rating, on a scale of 1-10, of how likely you think it is you could beat that animal in a fight to the death.

```{r exercise 7}

my_df <- data.frame("Rank" = c('first', 'second', 'third'),
                     "Names" = c('Artic Fox', 'Jellyfish', 'Snake'),
                     "Probability of Self Winning in a Fight" = c(4, 9.5, 6)) 

my_df
  
```

8. Index the second row of your dataframe and save it to a variable called `df_second_row`. Index the name of your second favorite animal and save it to a variable called `second_fave`. Index the battle likelihood rating for your third favorite animal and save it to a variable called `third_rating`.

```{r exercise 8}

df_second_row <- my_df[2,]
df_second_row

second_fave <- my_df[2,2]
second_fave

third_rating <- my_df[3,3]
third_rating

```

9. Rewrite the following code as properly formatted pipe chains.

```{r, eval = FALSE}
park(drive(start_car(find("keys")), to = "campus"))

"keys" %>%
  find() %>%
  start_car() %>%
  drive(to = "campus") %>%
  park() 


brush(tooth_paste(running_water(tooth_brush)), teeth)

tooth_brush() %>%
  running_water() %>%
  tooth_paste() %>%
  brush(teeth)


```


# Feedback 

Please save the appropriate number to the variables below:

1. Approximately how long (in minutes) do you think it took you to complete this assignment?

```{r}
timeEstimate = 190
```

2. How difficult or challenging did you find this assignment?

Extremely easy -------------------------------------- Extremely challenging 
                                                     (impossible to complete)
    1                                                           10
    
```{r}
challenge = 8.3
```
    
    
3. How engaging or fun did you find this assignment?
  
Extremely Boring and Dry -------------------------------------- Extremely Engaging and Fun 
          1                                                                   10

```{r}
engagement = 6.8
```

4. If you have any other feedback about this assignment, please provide it below.


<!-- # I would like a little bit more explanation for what is expected of us, but it was fun to mess around with made up data points! --> -->

