---
title: ""
author: ""
date: ""
output: html_document
---
```{r}
library(tidyverse)
```

You will use the built in `iris` dataset in this assignment.

Select all that columns that.. 

1. start with "Sepal"

```{r}
view(iris)

iris %>%
  select(starts_with("Sepal"))

```

2. start with "Petal"

```{r}

iris %>%
  select(starts_with("Petal"))

```

3. end with "Length"

```{r}

iris %>%
  select(ends_with("Length"))

```

4. end with "Width"

```{r}

iris %>%
  select(ends_with("Width"))

```

5. have a period in their name

```{r}

iris %>%
  select(contains("."))

```

6. have punctuation in their name

```{r}

iris %>%
  select(matches("[[:punct:]]"))

```

7. is the last one in the df

```{r}

iris %>%
  select(last_col())

```

8. contain numeric data

```{r}

iris %>%
  select(where(is.numeric))

```

9. contain factor data

```{r}

iris %>%
  select(where(is.factor))

```

10. contain data that is not numeric

```{r}

iris %>%
  select(!where(is.numeric))

```

Filter to return the observations that have a value...

11. Starting with "Sepal" and are greater than 4

```{r}

iris %>%
 filter(if_any(starts_with("Sepal"), ~ . > 4))

```

12. Ending with "width" and lower than 0.5

```{r}

iris %>%
  filter(if_any(ends_with("width"), ~ . < 0.5))

```

13. Starting with "Sepal" or ending with "Length" and are less than 2

```{r}

iris %>%
  filter(if_any(starts_with("Sepal") | (ends_with("Length")), ~ . < 2))

```

14. Containing numeric data, starting with "Petal", and are greater than or equal to 6

```{r}

iris %>%
  filter(if_any(where(is.numeric))) %>%
  filter(if_any(starts_with("Petal"), ~ . >= 6))

```

Across the variables...

15. Log transform those that end with "Length"

```{r}

iris %>%
  mutate(across(ends_with("Length"), log))

```

16. Round those that are numeric

```{r}

iris %>%
  mutate(across(where(is.numeric), round))

```

17. Scale those that start with "Petal" and are numeric

```{r}

iris %>%
  mutate(across((starts_with("Petal")) & where(is.numeric), scale))

```

18. Take your code from 17 but modify it to return only the observations with values less than -1.4

```{r}

iris %>%
  mutate(across((starts_with("Petal")) & where(is.numeric), scale)) %>%
  filter(if_all(starts_with("Petal"), ~ . < (-1.4)))

```

# Feedback

Please save the appropriate number to the variables below:

1. Approximately how long (in minutes) do you think it took you to complete this assignment?

```{r}
timeEstimate = 80
```

2. How difficult or challenging did you find this assignment?

Extremely easy -------------------------------------- Extremely challenging 
                                                     (impossible to complete)
    1                                                           10
    
```{r}
challenge = 3.4
```
    
    
3. How engaging or fun did you find this assignment?
  
Extremely Boring and Dry -------------------------------------- Extremely Engaging and Fun 
          1                                                                   10

```{r}
engagement = 8.3
```

4. If you have any other feedback about this assignment, please provide it below.


**d(･∀･○)**

