---
title: "Geoms Practice Problem Set"
author: ""
date: ""
output: html_document
---

```{r}
library(tidyverse)
# Modify the file path in the code below to properly load the "diamonds_sample.RData" file
load("diamonds_sample.RData") 
```

# Intro

You are going to work with a subset of data in the df `diamonds_sample`. All questions below will be in reference to `diamonds_sample`.

* `price` - price in USD
* `carat` - weight of the diamond
* `cut` - quality of the cut
* `color` - diamond color
* `clarity` - a measurement of how clear the diamond is
* `x` - length in mm
* `y` - width in mm
* `z` - depth in mm
* `depth` - total depth percentage
* `table` - width of top of diamond relative to widest point

Below, you are going to practice making several different kinds of graphs, thinking about what type of questions that graph would allow you to answer, what your prediction is, and then summarize what you actually observe. These are to help you with both creating the graphs with R code, but also graph comprehension in general. The latter is a critical skill, without which you will not know what the best graph to make is, even if you have the R skills to make several!

There will be some questions marked below where before running the code to create your graph, you will...
A. Write down *question* that this graph is exploring.
B. Write a brief sentence making a *prediction* of what you expect the relationship or pattern to be. 

Then, after observing the visualization, you will... 
A. Write a brief *summary* describing what that relationship or pattern actually is, and explain what evidence you have for this (e.g., "all the brown colored dots that correspond to 'Ideal' cut diamonds are higher on the y-axis, which here is 'price'. So I can see that 'Ideal' cut diamonds tend to be the most expensive.")

These are clearly marked in the questions that expect them. When a question has a spot that says something like "*Question here*", please delete that text and replace it with your answer.

*NOTE: For some of these visualizations, it may be hard to discern any actual patterns or relationships. Just try your best to describe what you see. If it is too hard to determine anything, state that and explain why!*


1. Use `geom_bar()` to create a bar graph for `clarity`.

```{r}
diamonds %>%
  ggplot(aes(x = clarity)) + 
  geom_bar(color = "white",
           fill = "skyblue")
```

2. Use `geom_bar()` to create a bar graph for `color`. Make the bars themselves be filled with violet and have a blue outline. 

```{r}
diamonds %>%
  ggplot(aes(x = color)) + 
  geom_bar(color = "blue",
           fill = "violet")
```

3. Use `geom_histogram()` to create a histogram for `price`.

```{r}
diamonds %>%
  ggplot(aes(x = price)) + 
  geom_histogram(color = "white",
           fill = "skyblue")
```

4. Use `geom_histogram()` to create a histogram for `carat`. Make the bars themselves be filled with cyan with a turquoise outline. Add a vertical bar at where you think the average might be.

```{r}
diamonds %>%
  ggplot(aes(x = carat)) + 
  geom_histogram(color = "turquoise",
           fill = "cyan") + 
  geom_vline(xintercept = 0.8, color = "violet")
```

5. Use `geom_point()` to create a scatter plot for `carat` and `depth`. Add the line of best fit, and make any aesthetic modifications that you think help improve the legibility or effectiveness of the graph.

Question:
  Does diamond weight increase with an increase in diamond depth?

Prediction:
  I predict that there is an increase in diamond weight with an increase in diamond depth.

```{r}
diamonds %>%
  ggplot(aes(y = depth, x = carat)) + 
  geom_point(size = 0.5, 
             alpha = 0.2, color = "turquoise") + 
  geom_smooth(color = "violet")
```

Summary:
 Most of the data points seem to cluster at a depth of 55 to 70, which corresponds to 0.2 to 2.5 carats, but there are a few outliers that bring the trendline upwards, suggesting there is a very slight correlation (if at all) with an increase in carats and an increase in depth.


6. Create 2D histogram (regular or hexbin) for `y` and `table`.

```{r}
diamonds %>%
  ggplot(aes(y = y, x = table)) + 
  geom_bin_2d(color = "white") + 
  geom_smooth()
```
Summary:
  Most of the data seems to cluster around 48 to 71 in table measurements, which corresponds to a width of about 0.2 to 11 mm. The line of best fit is also mostly horizontal, suggesting a lack of positive or negative correlation between diamond table and width.


7. Take your visualizations from questions 5 and 6 and add information about the individual distributions to the margins (whichever way you prefer).

```{r}

```

Do you think one of these two is better/more effective than the other? If so, which and why? If not, why not?

I think the scatterplot was a better and more easily readable visualization because of its clarity--you can see each data point and its position on the graph, allowing for more accurate analysis.


8. Use `stat_summary()` to show the mean `depth` for `color`. Represent the mean with a bar (note: *not* a vline), and include standard error *bars*. Make any aesthetic modifications that you think help improve the legibility or effectiveness of the graph.

Question:
  Is there a correlation between mean depth and mean color?

Prediction:
  I predict there is a positive correlation between mean depth and mean color.

```{r}
diamonds %>%
  ggplot(aes(y = depth, x = color)) +  
  stat_summary(fun = mean, 
               geom = "bar") + 
  stat_summary(fun.data = mean_se,
               geom = "errorbar",
               width = 0.2,
               color = "black")
```

Summary:
  All the bars are the same height, suggesting there is no correlation between mean depth and mean color. If there was a correlation, the bars would increase in height from left to right.


9. Use `stat_summary()` to show the mean `price` for `cut`. Represent the mean with a point, and include standard error *lines*. Make any aesthetic modifications that you think help improve the legibility or effectiveness of the graph.

```{r}
diamonds %>%
  ggplot(aes(y = price, x = cut)) +
  stat_summary(fun = "mean", geom = "bar") +
  stat_summary(fun.data = "mean_se", geom = "errorbar", width = 0.3) + 
  stat_summary(fun = "mean", geom = "point", color = "turquoise")
```

Summary:
  The mean price for cut is the highest with a premium cut, and the lowest with an ideal cut.


10. Take your code from question 9 and modify it so that there is a longdash line connecting each of the points.

```{r}
diamonds %>%
  ggplot(aes(y = price, x = cut)) +
  stat_summary(fun = "mean", geom = "bar") +
  stat_summary(fun.data = "mean_se", geom = "errorbar", width = 0.3) + 
  stat_summary(fun = "mean", geom = "point", color = "turquoise") + 
  geom_line()
#idk how to do the connecting line T-T
```

11. `geom_boxplot()` to create a boxplot for `depth` and `clarity`. Make the boxplots sienna with a salmon outline. Make any other aesthetic modifications that you think help improve the legibility or effectiveness of the graph.

```{r}
diamonds %>%
  ggplot(aes(y = depth, x = clarity)) + 
  geom_boxplot(color = "salmon", 
               fill = "sienna")
```

What more can you say from this visualization than the one you made in question 8?

There appears to be more of a correlation between clarity and depth than color and depth, as the boxplots seem to decrease in height from left to right.


12. `geom_boxplot()` to create a boxplot for `price` and `cut`. Make the boxplots' color and outline (the *fill* and *color* arguments) depend on their `cut`. Make any other aesthetic modifications that you think help improve the legibility or effectiveness of the graph (make sure the median line is visible).

```{r}
diamonds %>%
  ggplot(aes(y = price, x = cut)) + 
  geom_boxplot(aes(color = cut, fill = cut), color = "black")
```

What more can you say from this visualization than the one you made in question 9?

Most of the diamonds in the data set are premium or very good cuts, as those boxplots are the largest.


13. Use `geom_violin()` to create a violin plot for `carat` and `clarity`. Include a boxplot inside the violin. Make any other aesthetic modifications that you think help improve the legibility or effectiveness of the graph.

```{r}
diamonds %>%
  ggplot(aes(y = carat, x = clarity)) + 
  geom_violin(aes(color = clarity)) + 
  geom_boxplot(size = 0.3, width = 0.2, alpha = 0)
```

Summary:
 Carat and clarity appear to be generally negatively correlated, as the violin plots and mean points slope downward from left to right.


14. Use `geom_violin()` to create a violin plot for `carat` and `color`. Include a point for the mean, and error bars around the mean. Make any other aesthetic modifications that you think help improve the legibility or effectiveness of the graph.

```{r}
diamonds %>%
  ggplot(aes(y = carat, x = clarity)) + 
  geom_violin(aes(color = clarity)) + 
  stat_summary(fun = "mean", geom = "point", color = "red") +
  stat_summary(fun.data = "mean_se", geom = "errorbar", width = 0.5)
```

15. Use `geom_jitter()` to create a jitter plot for `price` and `cut`. Include a point for the mean and error lines around the mean. Make any other aesthetic modifications that you think help improve the legibility or effectiveness of the graph.

Question:
 Is there a correlation between price and cut?

Prediction:
  I predict there is a positive correlation between price and cut.


```{r}
diamonds %>%
  ggplot(aes(y = price, x = cut)) + 
  geom_jitter(aes(color = cut)) + 
  stat_summary(fun = "mean", geom = "point", color = "red") +
  stat_summary(fun.data = "mean_se", geom = "errorbar", width = 0.5)
```

Summary:
  There appears to be a slight positive correlation between price and cut mostly for diamonds with the good, very good, and premium cut types, as their mean points trend upward.

16. Take your visualization from question 14 and add on jittered points to show the whole distribution of data on top of the violins. Make any other aesthetic modifications that you think help improve the legibility or effectiveness of the graph.

```{r}
diamonds %>%
  ggplot(aes(y = carat, x = clarity)) + 
  geom_jitter(alpha = 0.1) +
  geom_violin(aes(color = clarity)) + 
  stat_summary(fun = "mean", geom = "point", color = "red") +
  stat_summary(fun.data = "mean_se", geom = "errorbar", width = 0.5)
```

17. Use `geom_jitter()` to create a strip chart for `z` and `clarity`. Make any other aesthetic modifications that you think help improve the legibility or effectiveness of the graph.

```{r}
diamonds %>%
  ggplot(aes(y = z, x = clarity)) + 
  geom_jitter(height = 25,
              color = "darkmagenta",
              alpha = .5) + 
  stat_summary(fun = "mean", 
               geom = "crossbar", 
               width = 0.8)
```

18. Use `geom_jitter()` to create a jitter plot for `price` and `color`. Include a point for the mean and error lines around the mean. Map the color of the points to `cut`. Make any other aesthetic modifications that you think help improve the legibility or effectiveness of the graph.

```{r}
diamonds %>%
  ggplot(aes(y = price, x = color)) + 
  geom_jitter(aes(color = cut)) + 
  stat_summary(fun = "mean", geom = "point", color = "red") +
  stat_summary(fun.data = "mean_se", geom = "errorbar", width = 0.6)
```

19. Use `geom_jitter()` to create a jitter plot for `price` and `color`. Include a point for the mean and error lines around the mean. Facet this graph by `cut`. Make any other aesthetic modifications that you think help improve the legibility or effectiveness of the graph.

```{r}
diamonds %>%
  ggplot(aes(y = price, x = color)) + 
  geom_jitter(aes(color = cut)) + 
  facet_grid(cols = vars(cut)) + 
  stat_summary(fun = "mean", geom = "point", color = "red") +
  stat_summary(fun.data = "mean_se", geom = "errorbar", width = 0.6)
```

20. Do you think that the graph created in 18 or 19 is more effective? Explain why.

Graph 19 is more effective in my opinion because it is categorized by cut, which adds more information to the graph and makes the data much more legible.

21. Use `stat_summary_2d()` to make a raster plot for `clarity` (y), `cut` (x), and `price` (z). Make any other aesthetic modifications that you think help improve the legibility or effectiveness of the graph.


```{r}
diamonds %>%
  ggplot(aes(x = cut,
             y = clarity,
             z = price)) +
  stat_summary_2d(fun = "mean", geom = "tile")
```



22. Create a scatter plot for `price` and `carat`. Add a line of best fit. Facet by `cut`. Make any other aesthetic modifications that you think help improve the legibility or effectiveness of the graph.

```{r}
diamonds %>%
  ggplot(aes(y = price, x = carat)) + 
  geom_point(aes(color = cut)) +
  facet_grid(cols = vars(cut)) + 
  geom_smooth()
```



23. Use `stat_summary_hex()` or `stat_summary_2d()` to create a raster plot for `carat` (y), `table` (x), and `price` (z). Make any other aesthetic modifications that you think help improve the legibility or effectiveness of the graph.


```{r}
diamonds %>%
  ggplot(aes(x = table,
             y = carat,
             z = price)) +
  stat_summary_2d(fun = "mean", geom = "tile")
```




# Feedback

Please save the appropriate number to the variables below:

1. Approximately how long (in minutes) do you think it took you to complete this assignment?

```{r}
timeEstimate = 
```

2. How difficult or challenging did you find this assignment?

Extremely easy -------------------------------------- Extremely challenging 
                                                     (impossible to complete)
    1                                                           10
    
```{r}
challenge = 
```
    
    
3. How engaging or fun did you find this assignment?
  
Extremely Boring and Dry -------------------------------------- Extremely Engaging and Fun 
          1                                                                   10

```{r}
engagement = 
```

4. If you have any other feedback about this assignment, please provide it below.




