# Different Geoms and When To Use Them

Run all code in the chunk below first!

```{r}
library(tidyverse) # Load tidyverse
library(palmerpenguins) # Load penguins data
mtcars2 = mtcars %>%
  mutate(gear = factor(gear),
         cyl = factor(cyl))
```


## One Categorical

Graphing one categorical variable is used to show counts or proportions.

### Bar

One good way of visualizing a single categorical variable is with a bar chart.

Think about the following question:

-- "How many penguin observations do we have from each island?"

> Create a visualization that has a bar for each island, and that bar's height corresponds to the number of penguins recorded on that island. Use `geom_bar()` to do so, where all you need to specify is an x-axis variable.

```{r}
penguins %>%
  ggplot(aes(x = island)) + 
  geom_bar()
```

The bars could also represent the *proportion* of all observations that came from each island instead of the raw counts.

$$\frac{nObservationsFromIslandX}{sumOfObservationsFromAllIslands}$$

If the **count**'s were on the y-axis before, then you would just want each `..count..` (numerator above) divided by the sum of all the `..count..`s (denominator above).

```{r}
penguins %>%
  ggplot(aes(x = island)) + 
  geom_bar(aes(y = (..count..)/sum(..count..)))
```

**Note: Proportions must sum to 1! If your bars ever do not sum to one, there is an issue!**

### Pie

Code included here so you have a template if absolutely needed.

```{r}
penguins %>%
  ggplot(aes(x = 1,
             fill = species)) +
  geom_bar() +
  coord_polar("y", start = 0)
```

## One Continuous

**Looking at distributions**

Being able to understand and characterize distributions is an integral part of the Social/Data Scientists toolbox. 

### Histogram

In a histogram, values of the variable of interest are separated into different bins on the x-axis.

The y-axis represents the *frequency* or *count* of some value or range of values in the distribution.

> Using `geom_histogram()`, create a histogram to investigate the distribution of `flipper_length_mm`

```{r}
penguins %>%
  ggplot(aes(x = flipper_length_mm)) + 
  geom_histogram()
```

Outline the bars with the color aesthetic.

> Add a black outline to the bars from the visualization above.

```{r}
penguins %>%
  ggplot(aes(x = flipper_length_mm)) + 
  geom_histogram(color = "black")
```

#### Bins

**bins** = number of bins (bars) in your histogram
**binwidth** = width of each bin (bar)

> Take the code above and compare the difference between using 5 bins and 15 bins.
  
```{r}
penguins %>%
  ggplot(aes(x = flipper_length_mm)) + 
  geom_histogram(color = "black", 
                 bins = 5)
penguins %>%
  ggplot(aes(x = flipper_length_mm)) + 
  geom_histogram(color = "black", 
                 bins = 15)
```


### Density

**density plots**, in short, are a smoothed histogram. 

> Use `geom_density()` to create a density plot showing the distribution of `flipper_length_mm`

```{r}
penguins %>%
  ggplot(aes(x = flipper_length_mm)) + 
  geom_density()
```

### vlines

You can add *vertical lines* to sections of a graph with `geom_vline()`, specifying where on the x-axis (intercept) that line should cross. Since you are doing something to the axis, you must make the specification in an `aes()` call.

> Replace the X's in the code below to add black lines marking the range of scores between 180-200:

```{r}
penguins %>%
  ggplot(aes(x = flipper_length_mm)) +
  geom_histogram(color = 'black',
                 bins = 15) +  
  geom_vline(aes(xintercept = 180), color = "black", size = 1) +
  geom_vline(aes(xintercept = 200), color = "black", size = 1)

```

## Continuous ~ Continuous

**Relationships**

### Scatter plot

`geom_point()` is used for scatter plots -- where each point on the visualization represents an observation in your data.

> Replace the X's below to investigate the relationship between `body_mass_g` and `bill_depth_mm` with a scatter plot

```{r}
penguins %>%
  ggplot(aes(y = body_mass_g, x = bill_depth_mm)) +
  geom_point()
```

Use scatter plots for datasets with **lower n’s only**.


### 2d Histogram

For datasets with a **large n**, you can use a 2d histogram with `geom_bin2d()`.

> Investigate the relationship between `body_mass_g` and `bill_depth_mm` with a 2d histogram

```{r}
penguins %>%
  ggplot(aes(y = body_mass_g, x = bill_depth_mm)) +
  geom_bin2d()
```

A hexbin plot using `geom_hex()` is essentially the same thing but uses hexagons.

> Investigate the relationship between `body_mass_g` and `bill_depth_mm` with a hexbin plot
  
```{r}
penguins %>%
  ggplot(aes(y = body_mass_g, x = bill_depth_mm)) +
  geom_hex()
```


### Adding Conditional Means

You can add a line of best fit to show the trend of your data with `geom_smooth()`. 

Two main arguments:

- `method=` - always gets set to "lm"
- `se=` - refers to whether or not to show error bars on the line (`TRUE` / `FALSE`).

> Investigate the relationship between `body_mass_g` and `bill_depth_mm` with a scatter plot and add the line of best fit without error bars

```{r}
penguins %>%
  ggplot(aes(y = body_mass_g, x = bill_depth_mm)) +
  geom_point() +
  geom_smooth(method = lm, se = FALSE)
```


### Rugs and Margins

Including a "rug" to your scatter plots with `geom_rug()` adds some information about each individual distribution.

> Investigate the relationship between `body_mass_g` and `bill_depth_mm` with a scatter plot and add a rug to the graph

```{r}
penguins %>%
  ggplot(aes(y = body_mass_g, x = bill_depth_mm)) +
  geom_point() +
  geom_rug()
```

> Tweak some of the aesthetic settings in the rug (e.g., alpha, size)

```{r}
penguins %>%
  ggplot(aes(y = body_mass_g, x = bill_depth_mm)) +
  geom_point() +
  geom_rug(alpha = 0.5, size = 0.8)
```

Another way to do so is using `ggMarginal()` from the `ggExtra` package (`ggExtra::ggMarginal()`).

> Run the code below to see:

```{r}
(penguins %>%
  ggplot(aes(y = body_mass_g, x = bill_depth_mm)) +
  geom_point()) %>%
ggExtra::ggMarginal(type = "histogram")
```


## Continuous ~ Categorical

**Comparisons**

For example: 

"How does the average weight (`body_mass_g`) of the penguins compare across islands (`island`)?"

Helpful to first examine how the values of the continuous variable vary to begin with.

> Above, you learned about how to investigate a distribution. Use one of those methods to investigate `body_mass_g`.

```{r}
penguins %>%
  ggplot(aes(x = body_mass_g)) +
  geom_histogram(color = 'black')

```
^ This variability is what is trying to be explained (e.g., perhaps by `island`)

### `stat_summary()`

`stat_summary()` - versatile function used to create visualizations summarizing the y values for each unique x value. 

2 main arguments:

- `fun =` what type of summary to visualize for the y values. 
- `geom =` how to visualize those summaries.

You will most often use "mean" for the `fun`.

#### Bar

Use "bar" for `geom=`.

Formal predictions should be made before running the graph code and short summaries should be written after observing them.

> Replac the X's below to use `stat_summary()` and compare the mean `body_mass_g` (represented with bars) across `island`

Prediction:
--
“If it is the case that the differences in penguin weight could be explained by what island they live on (e.g., penguins on some islands are heavier on average than penguins on other islands), then some bars should be higher or lower than the others. If it is not the case that the differences in penguin weight could be explained by what island they live on, the bars should all have roughly equivalent heights.”
--

```{r}
penguins %>%
  ggplot(aes(y = body_mass_g, x = island)) + 
  stat_summary(fun = "mean", geom = "bar")
```

Summary:
--
"In the visualization you can see that, generally speaking, penguins on Biscoe island seem to be the heaviest and heavier on average than penguins on either Dream or Torgersen island. The penguins on Dream and Torgensen island seem to have similar weight. You can see this pattern by noticing that the bar representing Biscoe island is higher than the bars for Dream and Torgersen islands (which are both about the same height)."
--

#### Point

> Use `stat_summary()` to compare the mean `body_mass_g` (represented with a point) across `island`

```{r}
penguins %>%
  ggplot(aes(y = body_mass_g, x = island)) +
  stat_summary(fun = "mean", geom = "point")

```


Summary (compare to when the means were represented with bars)
--
"Compared to when the means were represented with bars, the difference between the average weight of penguins on Biscoe island to the other two islands looks much more drastic."
--

#### Line

> Use `stat_summary()` to compare the mean `body_mass_g` (represented with a line) across `island`

```{r}
penguins %>%
  ggplot(aes(y = body_mass_g, x = island)) +
  stat_summary(fun = "mean", geom = "line")
```


> add `group = 1` to the code from above.

```{r}
penguins %>%
  ggplot(aes(y = body_mass_g, x = island, group = 1)) +
  stat_summary(fun = "mean", geom = "line")

```

> Change the linetype from the visualization above

```{r}
penguins %>%
  ggplot(aes(y = body_mass_g, x = island, group = 1)) +
  stat_summary(fun = "mean", geom = "line", linetype = "dashed")
```

> Use `stat_summary()` to compare the mean `body_mass_g` (represented with a point AND a line) across `island`

```{r}
penguins %>%
  ggplot(aes(y = body_mass_g, x = island, group = 1)) +
  stat_summary(fun = "mean", geom = "point") +
  stat_summary(fun = "mean", geom = "line")

```


### Error bars

You will use the SEM in this course.

You want the *s*tandard *e*rror of your *mean* ("mean_se"), and want that represented by error bars ("errorbar").

> Replace the X's in the code below to add error bars to the means represented by a bar.

```{r}
penguins %>%
  ggplot(aes(y = body_mass_g, x = island)) +
  stat_summary(fun = "mean", geom = "bar") +
  stat_summary(fun.data = "mean_se", geom = "errorbar")
```


Note you have to use `fun.data = ` instead of `fun = `. 

> Add a `width` aesthetic to the errorbar in the code above and find a value you think looks good.

```{r}
penguins %>%
  ggplot(aes(y = body_mass_g, x = island)) +
  stat_summary(fun = "mean", geom = "bar") +
  stat_summary(fun.data = "mean_se", geom = "errorbar",
               width = 0.3)
```

> Use `stat_summary()` to compare the mean `body_mass_g` (represented with a point) across `island` and add errorbars to the means.

```{r}
penguins %>%
  ggplot(aes(y = body_mass_g, x = island)) +
  stat_summary(fun = "mean", geom = "point") +
  stat_summary(fun.data = "mean_se", geom = "errorbar", width = 0.2)
```

> Take your code from above and use "linerange" as the geom instead of "errorbar"

```{r}
penguins %>%
  ggplot(aes(y = body_mass_g, x = island)) +
  stat_summary(fun = "mean", geom = "point") +
  stat_summary(fun.data = "mean_se", geom = "linerange")
```

> Take your code from above, use "pointrange" as the geom, and get rid of the other `stat_summary()` call.

```{r}
penguins %>%
  ggplot(aes(y = body_mass_g, x = island)) +
  stat_summary(fun.data = "mean_se", geom = "pointrange")
```

### Boxplots

> Use `geom_boxplot()` to compare the mean `body_mass_g` across `island`

```{r}
penguins %>%
  ggplot(aes(y = body_mass_g, x = island)) +
  geom_boxplot()
```

### Problem With Summary Stats

Including nothing but summary statistics in your graphs is not much better than only reporting the summary statistics as numbers.

It is recommended to visualize the actual distribution of your data! 

### Violin Plots

Best when your dataset has a large n.

> Use `geom_violin()` to create a violin plot comparing the mean `body_mass_g` across `island`

```{r}
penguins %>%
  ggplot(aes(y = body_mass_g, x = island)) +
  geom_violin()

```

> Use **both** a violin and boxplot to compare the mean `body_mass_g` across `island`

```{r}
penguins %>%
  ggplot(aes(y = body_mass_g, x = island)) +
  geom_violin() +
  geom_boxplot(width = 0.2)

```

Since ggplot is an additive/layered system, you can combine different geoms.

### Jitter Plots

Since the x-axis is a categorical variable, all the data points will have the same value:

> Run code below

```{r}
penguins %>%
  ggplot(aes(y = body_mass_g, x = island)) +
  geom_point()
```

Jitter plots are best for small n’s.

> Use `geom_jitter()` to create a jitter plot comparing the `body_mass_g` scores across `island`

```{r}
penguins %>%
  ggplot(aes(y = body_mass_g, x = island)) +
  geom_jitter()

```

jitter plots pair well with other geoms.

> Use **both** a boxplot and jitter plot to compare the `body_mass_g` across `island`

```{r}
penguins %>%
  ggplot(aes(y = body_mass_g, x = island)) +
  geom_boxplot(width = 0.6) +
  geom_jitter(height = 0, width = 0.1,
              alpha = 0.5, color = "seagreen")
```

> Use **both** a violin and jitter plot to compare the `body_mass_g` across `island`. Include a point indicating the mean as well.

```{r}
penguins %>%
  ggplot(aes(y = body_mass_g, x = island)) +
  geom_violin() +
  geom_jitter(alpha = 0.4, width = 0.05) +
  stat_summary(fun = "mean",
               geom = "point",
               color = "red")

```


#### Limits

1. Adding noise changes the data being visualized. Only jitter along a categorical variable. 

> Add the appropriate argument (`height` or `width`) to the code below so it does not jitter along a continuous variable.

```{r}
penguins %>%
  ggplot(aes(y = body_mass_g, x = island)) +
  geom_jitter(height = 0)
```

2. Jitter is randomly generated each time the code is executed.

3. May see this message:

*Warning messages: 1: Removed `X` rows containing non-finite values (stat_smooth). 2: Removed `X` rows containing missing values (geom_point).*

**X** data points are being removed from the dataset when generating the graph.

### Variations on Jitter

#### Strip Chart

> Create a strip chart plot by taking your jitter plot from above and adding `stat_summary()` to represent the mean using a "crossbar". Use aesthetics to clean up.

```{r}
penguins %>%
  ggplot(aes(y = body_mass_g, x = island)) + 
  geom_jitter(height = 0, width = .1, 
              color = "darkmagenta",
              alpha = .5) + 
  stat_summary(fun = "mean", 
               geom = "crossbar", 
               width = 0.3)
```

#### Beeswarm/Dot Plot

> Run code below

```{r}
penguins %>%
  ggplot(aes(y = body_mass_g, x = island)) +   
  geom_dotplot(stackdir = "center", 
               binaxis = "y", 
               binwidth = 80,
               stackratio = 1,
               fill = "cyan3", 
               colour = "cyan3")
```

The settings can be quite temperamental, and you have to play around with the binwidth, stackratio, and dotsize, but once dialed in they can make some nice looking visualizations. 

> Run code below

```{r}
penguins %>%
  ggplot(aes(y = body_mass_g, x = island)) +  
  geom_boxplot() + 
  geom_dotplot(binaxis = 'y', 
               stackdir = 'center', 
               stackratio = 1, 
               binwidth = 80,
               binpositions = "all",
               dotsize = 1,
               alpha = .45, 
               fill = "cyan3", 
               colour = "cyan3")
```

### Ridgeline Plot

Requires the continuous variable to be on the x-axis and the categorical variable to be on the y-axis. 

`geom_density_ridges()` from `ggridges`. The `scale` argument adds space between each distribution.

> Create a ridgeline plot to compare the distributions of `body_mass_g` across `island`. Play with the `scale` to find the value you think makes the best looking graph.

```{r}
penguins %>%
  ggplot(aes(x = body_mass_g, y = island)) +
  ggridges::geom_density_ridges(scale = 0.9)
```

raincloud plot:

> Replace the X's in the code below by adding the `jittered_points` argument set to `TRUE` and `position` argument set to "raincloud" to the geom_density_rides() call.

```{r}
penguins %>%
  ggplot(aes(x = body_mass_g, y = island)) +  
  ggridges::geom_density_ridges(jittered_points = TRUE, 
                      position = "raincloud",
                      scale = 0.4)
```


## New Arguments and Functions

### Faceting

faceting -- separate subsets of data into entirely different graphs. 

Done using `facet_grid()` -- specifying what *var*iable(*s*) you want to facet by, and whether you want those graphs spread across different *col*umn*s* or *rows*

> In the code below, replace the Xs to first facet `island` across columns, then across rows.

```{r}
# By columns
penguins %>%
  ggplot(aes(y = body_mass_g, x = bill_depth_mm)) +
  geom_point() + 
  facet_grid(cols = vars(island))

# By rows
penguins %>%
  ggplot(aes(y = body_mass_g, x = bill_depth_mm)) +
  geom_point() +
  facet_grid(rows = vars(island))
```

> Modify the code below to facet `island` across rows and `species` across columns:

```{r}
penguins %>%
    ggplot(aes(y = body_mass_g, x = bill_depth_mm)) +
    geom_point() + 
    facet_grid(rows = vars(island),
               cols = vars(species))
```

### Groups

Grouping is another way you can plot subsets of data.

> Replace the X's in the code below to look at how `wt` changes across `gear` for cars with different `cyl`inders by grouping by `cyl`.

```{r}
mtcars2 %>%
  ggplot(aes(y = wt, x = factor(gear), 
               group = factor(cyl), color = factor(cyl))) +
    stat_summary(fun = "mean", geom = "line")
```

### Positions

position/adjustment arguments usually take the form: 

`position = position_*()`

Instead of `geom_jitter()`, could use `geom_point()` and setting a position argument. e.g.,

`geom_point(position=position_jitter())`

#### Identity

`position_identity()` overlaps the elements

> Set position below to "identity":

```{r}
penguins %>%
 ggplot(aes(x = island, fill = species)) +
  geom_bar(position = "identity")
```

#### Dodging

`“position_dodge()”` places overlapping objects directly beside one another

> Replace the X's in the code below to set the position to dodge

```{r}
penguins %>%
  ggplot(aes(x = island, fill = species)) +
  geom_bar(position = posiiton_dodge())
```

> Add code below to dodge the points, specifying a specific `width` argument.

```{r}
penguins %>%
 ggplot(aes(y = body_mass_g, x = island, fill = species)) +
     geom_point(shape = 21, position = position_dodge(width = .75))
```

Observe the following. By default, they are often come out looking funky:

```{r}
data.frame(
  x = c("a","a","b","b"),
  y = 2:5,
  g = rep(1:2, 2)
) %>%
  ggplot(aes(x, y, group = g)) +
  geom_col(position = "dodge", fill = "grey50", colour = "black")+
  geom_errorbar(
  aes(ymin = y - 1, ymax = y + 1),
  width = 0.2
)
```

Adding some position adjustments corrects this!

```{r}
data.frame(
  x = c("a","a","b","b"),
  y = 2:5,
  g = rep(1:2, 2)
) %>%
  ggplot(aes(x, y, group = g)) +
  geom_col(position = "dodge", fill = "grey50", colour = "black")+
  geom_errorbar(
    aes(ymin = y - 1, ymax = y + 1),
    width = 0.2,
    position = position_dodge(width = 0.9)
)
```

Simultaneously dodge and jitter with `position_jitterdodge()`.

> Add code below to jitter and dodge the points, specifying a specific `width` argument.

```{r}
penguins %>%
ggplot(aes(x = island, y = body_mass_g, fill = species)) +
    geom_boxplot(outlier.size = 0) +
    geom_point(shape = 21, 
               position = position_jitterdodge(jitter.width = 0.3))
```

#### Stacking

`position_fill()` -- each set of stacked bars is uniform in height.

> Replace the X below to use the fill positional argument

```{r}
penguins %>%
ggplot(aes(x = island, fill = species)) +
  geom_bar(position = position_fill())
```

## Categorical ~ Categorical

> Replace the X's in the code below to map `species` to fill.

```{r}
# Counts
penguins %>%
  ggplot(aes(x = island, fill = species)) + 
  geom_bar(stat = "count")

# Proportions
penguins %>%
  ggplot(aes(x = island, fill = species)) + 
    geom_bar(position = position_fill())
```

### Cont ~ Cat + Cat

Add another aesthetic to any Cont ~ Cat

> Replace the X's in the code below so that `species` is mapped to fill

```{r}
penguins %>%
  ggplot(aes(y = body_mass_g, x = island)) +
  geom_jitter(aes(fill = species),
              size = 1, alpha = 0.7,
              shape = 21,
              position = position_jitterdodge()) +
  stat_summary(aes(fill = species),
               fun.data = "mean_se",
               geom = "pointrange",
               color = "black",
               shape = 21,
               size = 0.5,
               position = position_dodge(width = 0.7))
```

or facet

> Add code below to facet `species` across columns

```{r}
penguins %>%
  ggplot(aes(y = body_mass_g, x = island)) +
  geom_jitter(height = 0, width = 0.2, 
              size = 2, alpha = 0.4,
              pch = 21,
              aes(shape = island,
                   fill = island)) +
    stat_summary(fun.data = "mean_se",
               geom = "linerange",
               color = "black",
               size = 2) +
      stat_summary(fun = "mean",
               geom = "point",
               color = "black",
               shape = 21,
               size = 2.5,
               aes(fill=island)) + 
  facet_grid(cols = vars(species))
```

#### Raster

> Replace the X's in the code below to show how the different levels of `species` and `island` combinations have different average values of `body_mass_g`

```{r}
penguins %>%
  ggplot(aes(x = island,
             y = species,
             z = body_mass_g)) +
  stat_summary_2d(fun = "mean", geom = "tile")
```

### Cont ~ Cont + Cat

Just facet a scatter plot

> Add code below to facet `species` across columns

```{r}
penguins %>%
  ggplot(aes(y = body_mass_g, x = bill_depth_mm)) +
  geom_point() +
  facet_grid(cols = vars(species))
```



### Cont ~ Cont + Cont

z-axis shows values on a continuous variable

```{r}
penguins %>%
  ggplot(aes(y = body_mass_g,
             x = bill_depth_mm,
             z = flipper_length_mm)) +
  stat_summary_2d(color = "black")

penguins %>%
  ggplot(aes(y = body_mass_g,
             x = bill_depth_mm,
             z = flipper_length_mm)) +
  stat_summary_hex(color = "black")
```

## Custom geoms

Other geoms can be loaded from packages or other sources. Code is included here to create 2 geoms that can be used to make 2 visualizations that are currently pretty popular.

### Split Violin Plot

A split violin plot allows you to easily compare two groups (and across the levels of another variable). 

```{r}
source(url("https://raw.githubusercontent.com/Psyc193L/Psyc193L.github.io/main/geom_split_violin.R"))
```

> Run the code below, make some step-wise tweaks (one at a time) to the different arguments to see if you can understand what each is doing.

```{r}
penguins %>%
ggplot(aes(x = island, y = body_mass_g, fill = species)) +
  geom_split_violin(trim = FALSE, alpha = .4)+
  geom_boxplot(width = .2, alpha = .6, 
               fatten = NULL, show.legend = FALSE) +
  stat_summary(fun.data = "mean_se", geom = "pointrange", 
               show.legend = F, 
               position = position_dodge(.175))
```

### Raincloud

```{r}
#source(here::here("geom_flat_violin.R"))
source(url("https://raw.githubusercontent.com/Psyc193L/Psyc193L.github.io/main/geom_flat_violin.R"))
```

Do not worry about understanding all parts of the code below.

```{r}
rain_height <- .1

penguins %>%
ggplot(aes(x = "", y = body_mass_g, fill = species)) +
  # clouds  
  geom_flat_violin(position = position_nudge(x = rain_height+.05),
                   alpha = 0.4, trim = FALSE) + 
  # rain
  geom_point(aes(colour = species), size = 2, 
             alpha = .5, show.legend = FALSE, 
              position = position_jitter(width = 0.05, height = 0)) +
  # boxplots
  geom_boxplot(width = 0.05, alpha = 0.4, 
               show.legend = FALSE, outlier.shape = NA,
               position = position_nudge(x = -rain_height*2)) +
  # mean and SE point in the cloud
  stat_summary(fun.data = "mean_cl_normal", mapping = aes(color = species), 
               show.legend = FALSE,
               position = position_nudge(x = rain_height * 3)) +
  # adjust layout
  scale_x_discrete(name = "", expand = c(rain_height*3, 0, 0, 0.7)) +
  scale_y_continuous(limits = c(2000, 7000)) +
  coord_flip()
```

## Best Practices:

Below are some guidelines and best practices that should be considered when designing your visualizations.

* Graphs should be EASILY readable. 
  + Label everything intuitively.
  + Follow conventions: y = response variable, x = predictor, be mindful of variable types, etc.

* Graphs should be purposeful
  + What is the specific relationship or trend in your data that you are trying to communicate with this visualization?

* Graphs should facilitate quantitative interpretation and comparison, and allow for inferential statistics by eye.
  + Represent variability.
  + Show relationship trends, means, etc.

* Cool =/= best.
  + Just because you CAN do something does not always mean you SHOULD. Keep things simple and clean.
    
* Make your visualization aesthetically pleasing but not at the cost of wasting ink.

## Extra Resources

* [ggplot2 reference](https://ggplot2.tidyverse.org/reference/)
* [R graphics cookbook](http://www.cookbook-r.com/Graphs/) 
* [ggplot2 book](https://ggplot2-book.org/) 
* [ggplot2 cheat sheet](https://rstudio.com/wp-content/uploads/2016/11/ggplot2-cheatsheet-2.1.pdf)
* [Help understand different types of graphs](https://datavizcatalogue.com/index.html)
* [Recommendations on best graphs for visualizing particular relationships](https://www.data-to-viz.com/)
* [r-specific information on how to construct graphs](https://www.r-graph-gallery.com/index.html)
* [More r-specific stuff. Top 50 ggplot geoms](http://r-statistics.co/Top50-Ggplot2-Visualizations-MasterList-R-Code.html)
* [Info on plotly](https://plotly-r.com/overview.html)
* [ggplot2 extensions](https://exts.ggplot2.tidyverse.org/gallery/)
* [Fundamentals of Data Visualization](https://serialmentor.com/dataviz/)

## Citations

As always, most illustrations by [@allison_horst](https://twitter.com/allison_horst)

Custom violin plots modified from source code [here](https://psyteachr.github.io/introdataviz/advanced-plots.html)
